### 2016-08-08 main.tex
Add the template from Elsevier

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Medical Image Analysis}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
\author{Elsevier\fnref{myfootnote}}
\address{Radarweg 29, Amsterdam}
\fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
\ead[url]{www.elsevier.com}

\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{support@elsevier.com}

\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
\address[mysecondaryaddress]{360 Park Avenue South, New York}

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

\begin{keyword}
\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
\MSC[2010] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}

\linenumbers

\section{The Elsevier article class}

\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript. Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal. It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.

\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class. In addition, it features commands and options to format the
\begin{itemize}
\item document style
\item baselineskip
\item front matter
\item keywords and MSC codes
\item theorems, definitions and proofs
\item lables of enumerations
\item citation style and labeling.
\end{itemize}

\section{Front matter}

The author names and affiliations could be formatted in two ways:
\begin{enumerate}[(1)]
\item Group the authors per affiliation.
\item Use footnotes to indicate the affiliations.
\end{enumerate}
See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.

\section{Bibliography styles}

There are various bibliography styles available. You can select the style of your choice in the preamble of this document. These styles are Elsevier styles based on standard styles like Harvard and Vancouver. Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.

Here are two sample references: \cite{Feynman1963118,Dirac1953888}.

\section*{References}

\bibliography{literature}

\end{document}

### 2016-08-08 01_introduction/introduction.tex
Add the outline and the frontmatter

\section{Introduction}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2016-08-08 main.tex
Add the outline and the frontmatter

@@
 \modulolinenumbers[5]
+
+% Use the acro package to handle the acronym
+\usepackage{acro}
+\input{00_files_system/acro_def.tex}
 
@@
 %% Numbered
-%\bibliographystyle{model1-num-names}
+%\bibliographystyle{00_files_system/model1-num-names}
 
 %% Numbered without titles
-%\bibliographystyle{model1a-num-names}
+%\bibliographystyle{00_files_system/model1a-num-names}
 
 %% Harvard
-\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+\bibliographystyle{00_files_system/model2-names}\biboptions{authoryear}
 
 %% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+%\usepackage{numcompress}\bibliographystyle{00_files_system/model3-num-names}
 
 %% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+%\usepackage{numcompress}\bibliographystyle{00_files_system/model4-names}\biboptions{authoryear}
 
 %% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
+%\bibliographystyle{00_files_system/model5-names}\biboptions{authoryear}
 
 %% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+%\usepackage{numcompress}\bibliographystyle{00_files_system/model6-num-names}
 
@@
 
-\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
+\title{Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization}
 
-%% Group authors per affiliation:
-\author{Elsevier\fnref{myfootnote}}
-\address{Radarweg 29, Amsterdam}
-\fntext[myfootnote]{Since 1880.}
+% Add authors and the different addresses
+\author[label1,label3]{Guillaume~Lema\^itre\corref{cor1}}
+\ead{g.lemaitre58@gmail.com}
+\author[label3]{Robert~Mart\'i}
+%\ead{marly@eia.udg.edu}
+\author[label3]{Jordi~Freixenet}
+%\ead{jordif@eia.udg.edu}
+\author[label5]{Anke Meyer-Baese}
+%\ead{ameyerbaese@fsu.edu}
+\author[label4]{Joan~C.~Vilanova}
+%\ead{kvilanova@comg.cat}
+\author[label2]{Paul~M.~Walker}
+%\ead{pwalker@u-bourgogne.fr}
+\author[label1,label6]{Fabrice~Meriaudeau}
+%\ead{fabrice.meriaudeau@u-bourgogne.fr}
+\address[label1]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, 12 rue de la Fonderie, 71200 Le Creusot, France}
+\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
+\address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
+\address[label4]{\scriptsize Department of Magnetic Resonance, Cl\'inica Girona, Lorenzana 36, 17002 Girona, Spain}
+\address[label5]{\scriptsize Department of Scientific Computing, 400 Dirac Science Library, Florida State University, Tallahassee, FL 32306, United States}
+\address[label6]{\scriptsize CISIR, Electrical \& Electronic Engineering Department, Universiti Teknologi Petronas, 32610 Seri Iskandar, Perak, Malaysia}
+\cortext[cor1]{Corresponding author.}
 
-%% or include affiliations in footnotes:
-\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
-\ead[url]{www.elsevier.com}
-
-\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-\ead{support@elsevier.com}
-
-\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
-\address[mysecondaryaddress]{360 Park Avenue South, New York}
-
+% Start the abstract
 \begin{abstract}
@@
 
+% Give the different keywords
 \begin{keyword}
-\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
-\MSC[2010] 00-01\sep  99-00
+\acs*{dce}-\acs*{mri}\sep prostate cancer\sep normalization\sep classification\sep quantification
 \end{keyword}
@@
 
+% Reset all the acronyms
+\acresetall
 \linenumbers
+% Include now the different files
+\input{01_introduction/introduction}
+\input{02_methods/methods}
+\input{03_experiments/experiments}
+\input{04_discussions/discussions}
+\input{05_conclusions/conclusions}
 
-\section{The Elsevier article class}
-
-\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.
-
-\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript.
-Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal.
-It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.
-
-\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class.
-In addition, it features commands and options to format the
-\begin{itemize}
-\item document style
-\item baselineskip
-\item front matter
-\item keywords and MSC codes
-\item theorems, definitions and proofs
-\item lables of enumerations
-\item citation style and labeling.
-\end{itemize}
-
-\section{Front matter}
-
-The author names and affiliations could be formatted in two ways:
-\begin{enumerate}[(1)]
-\item Group the authors per affiliation.
-\item Use footnotes to indicate the affiliations.
-\end{enumerate}
-See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.
-
-\section{Bibliography styles}
-
-There are various bibliography styles available.
-You can select the style of your choice in the preamble of this document.
-These styles are Elsevier styles based on standard styles like Harvard and Vancouver.
-Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.
-
-Here are two sample references: \cite{Feynman1963118,Dirac1953888}.
-
+% Include the bibliography
 \section*{References}
 
-\bibliography{literature}
+\bibliography{00_files_system/literature}
 

### 2016-08-09 01_introduction/introduction.tex
Add quantitative methods

@@
 \section{Introduction}
+
+\Ac{cap} is the second most frequently diagnosed men cancer, accounting for 899,000 cases leading to 258,100 deaths~\citep{ferlay2010estimates}.
+As highlighted by the PI-RADS Steering Committee, the two main challenges to be addressed are~\citep{weinreb2016pi}:
+(i) the improvement of detecting clinically significant \ac{cap} and
+(ii) an increase of the confidence in benign or dormant cases, avoiding unnecessary invasive medical exams.
+In this regard, \ac{mpmri} is frequently used to build robust \ac{cad} systems to detect, localize, and grade \ac{cap}.
+In general, \ac{cad} systems are based on \ac{mpmri} which combines several of the following modalities~\citep{lemaitre2015computer}: \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri}, \ac{adc} maps, and \ac{mrsi}.
+
+In \ac{dce}-\ac{mri}, a contrast media is injected intravenously and a set of images is acquired over time.
+Consequently, each voxel in the image is a dynamic signal which is related to the vascular properties of the tissue.
+In fact, these properties are automatically extracted using quantitative or semi-quantitative approaches~\citep{lemaitre2015computer}.
+
+The former group of approaches uses pharmacokinetic modelling based on a bicompartment model, namely Brix~\citep{brix1991pharmacokinetic} and Tofts~\citep{tofts1995quantitative} models.
+The parameters of the Brix model are found assuming a linear relationship between the media concentration and \ac{mri} signal intensity.
+This assumption has shown, however, to lead to inaccurate parameter calculation~\citep{heilmann2006determination}.
+In the contrary, Tofts model only requires a conversion from \ac{mri} signal intensity to concentration, which can become a non-linear relationship using specific equation of \ac{mri} sequences (e.g., FLASH sequence).
+Tofts modelling suffers, however, from an higher complexity~\citep{gliozzi2011phenomenological}.
+The conversion using the non-linear approach requires to acquire a T$_1$ map which is not always possible during clinical examination.
+Furthermore, the parameter calculation require the \ac{aif} which is challenging to measure and can also lead to inaccurate estimation of the parameters.
+
+The latter group of approaches are rather mathematical than pharmacokinetic modelling.
 

### 2016-08-09 01_introduction/introduction.tex
Finish the introduction

@@
 
-The latter group of approaches are rather mathematical than pharmacokinetic modelling.
+The latter group of approaches are rather mathematical than pharmacokinetic modelling~\citep{huisman2001accurate,gliozzi2011phenomenological}.
+These methods offer the advantages to not require any knowledge about the \ac{mri} sequence nor any conversion from signal intensity to concentration.
+However, the heuristic approach propose by \citeauthor{huisman2001accurate} requires an estimate regarding the noise standard deviation of the signal as well as manual tuning.
+
+Nevertheless, all presented methods suffer from two major drawbacks:
+(i) the inter-patient variability of the data lead to a variation of the parameters estimated and to poor classification performance while designing \ac{cad} systems, and
+(ii) only few parameters are used to characterize the dynamic signal implying that some information are discarded.
+
+In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduce the inter-patient variability of the data.
+Furthermore, we show that using the full normalized signal lead to the best classification performance.
+
+The paper is organized as follows: Section~\ref{sec:methods} outlines our normalization strategy (Section~\ref{sec:norm}) as well as specificity regarding the state-of-the-art methods used for comparison (Section~\ref{sec:stateart}).
+The dataset, experiments, and results are reported in Section~\ref{sec:experiments} while discussed in Section~\ref{sec:discussions} followed by a concluding section.
 

### 2016-08-09 main.tex
Add quantitative methods
Finish the introduction

@@
 %% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{00_files_system/model3-num-names}
+%\usepackage{00_files_system/numcompress}\bibliographystyle{00_files_system/model3-num-names}
 
@@
 %\ead{marly@eia.udg.edu}
-\author[label3]{Jordi~Freixenet}
+%\author[label3]{Jordi~Freixenet}
 %\ead{jordif@eia.udg.edu}
-\author[label5]{Anke Meyer-Baese}
+%\author[label5]{Anke Meyer-Baese}
 %\ead{ameyerbaese@fsu.edu}
-\author[label4]{Joan~C.~Vilanova}
+%\author[label4]{Joan~C.~Vilanova}
 %\ead{kvilanova@comg.cat}
-\author[label2]{Paul~M.~Walker}
+%\author[label2]{Paul~M.~Walker}
 %\ead{pwalker@u-bourgogne.fr}
@@
 \address[label1]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, 12 rue de la Fonderie, 71200 Le Creusot, France}
-\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
+%\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
 \address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
-\address[label4]{\scriptsize Department of Magnetic Resonance, Cl\'inica Girona, Lorenzana 36, 17002 Girona, Spain}
-\address[label5]{\scriptsize Department of Scientific Computing, 400 Dirac Science Library, Florida State University, Tallahassee, FL 32306, United States}
+%\address[label4]{\scriptsize Department of Magnetic Resonance, Cl\'inica Girona, Lorenzana 36, 17002 Girona, Spain}
+%\address[label5]{\scriptsize Department of Scientific Computing, 400 Dirac Science Library, Florida State University, Tallahassee, FL 32306, United States}
 \address[label6]{\scriptsize CISIR, Electrical \& Electronic Engineering Department, Universiti Teknologi Petronas, 32610 Seri Iskandar, Perak, Malaysia}

### 2016-08-10 02_methods/methods.tex
Add the outline and the frontmatter
Add the section with the different models
Finish the introduction
Advance in the methods section

--- 2016-08-08 01_introduction/introduction.tex
@@
-\section{Introduction}
+\section{Methods}\label{sec:methods}
+
+\subsection{Normalization of \ac{dce}-\ac{mri} images}\label{sec:norm}
+
+\subsection{Quantification of \ac{dce}-\ac{mri}}\label{sec:stateart}
+
+\subsubsection{Brix and Hoffmann models}
+
+In the Brix model~\citep{brix1991pharmacokinetic}, the \ac{mri} signal intensity is assumed to be proportional to the media concentration.
+Therefore, the model is expressed as in Eq.\,\eqref{eq:brix}:
+
+\begin{equation}
+  s_n(t) = 1 + A \left[ \frac{\exp(k_{el} t') - 1}{k_{ep}(k_{ep} - k_{el})} \exp(- k_{el} t) - \frac{\exp(k_{ep} t') - 1}{k_{el}(k_{ep} - k_{el})} \exp(- k_{ep} t) \right],
+  \label{eq:brix}
+\end{equation}
+
+\noindent with
+
+\begin{equation}
+  s_n(t) = \frac{s(t)}{S_0},
+  \label{eq:enh}
+\end{equation}
+
+\noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at time $t$ and the average pre-contrast \ac{mri} signal intensity, respectively; $A$, $k_{el}$, and $k_{ep}$ are a constant proportional to the transfer constant, the diffusion rate constant, and the rate constant, respectively.
+Additionally, during the injection time $0 \leq t \leq \tau$, $t' = t$ and afterwards while $t > \tau$, $t' = \tau$.
+
+Following this model, \citeauthor{hoffmann1995pharmacokinetic} propose the following similar model as expressed in Eq.\,\eqref{eq:hoffmann}:
+
+\begin{equation}
+  s_n(t) = 1 + \frac{A}{\tau} \left[ \frac{k_{ep} \left( \exp(k_{el} t') - 1 \right)}{k_{el}(k_{ep} - k_{el})} \exp(- k_{el} t) - \frac{\exp(k_{ep} t') - 1}{(k_{ep} - k_{el})} \exp(- k_{ep} t) \right].
+  \label{eq:hoffmann}
+\end{equation}
+
+\subsubsection{Tofts model}
+
+The extended Tofts model is formulated as in Eq.\,\eqref{eq:exttofts}:
+
+\begin{equation}
+  C_t(t) = K_{trans} C_p(t) \Conv \exp(-k_{ep}t) + v_p C_p(t),
+  \label{eq:exttofts}
+\end{equation}
+
+\begin{description}
+  \item[Conversion of \ac{mri} signal intensity to concentration]
+
+  \item[Estimation of patient-based \ac{aif} signal \textit{vs.} population-based \ac{aif} signal]
+\end{description}
+
+\subsubsection{\acs*{pun} model}
+
+\citeauthor{gliozzi2011phenomenological} show that \ac{pun} approach can be used for \ac{dce}-\ac{mri} analysis~\citep{gliozzi2011phenomenological}.
+The model has been successfully used in a \ac{cad} system proposed by~\cite{giannini2015fully}.
+This model can be expressed as in Eq.\,\eqref{eq:pun}:
+
+\begin{equation}
+  s_n(t) = \exp\left[rt + \frac{1}{\beta} \left( a_0 - r \right) \left( \exp(\beta t) - 1 \right) \right],
+  \label{eq:pun}
+\end{equation}
+
+\noindent with
+
+\begin{equation}
+  s_n(t) = \frac{s(t) - S_0}{S_0},
+  \label{eq:enh}
+\end{equation}
+
+\noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at time $t$ and the average pre-contrast \ac{mri} signal intensity, respectively; $r$, $a_0$, and $\beta$ are the free parameters of the model.
+
+\subsubsection{}
 

### 2016-08-10 02_methods/methods.tex
advance tofts

@@
 
+\noindent where $\Conv$ is the convolution operator; $C_t(t)$ and $C_p(t)$ is the concentration of contrast agent in the tissue and in the plasma, respectively; $K_{trans}$, $k_{ep}$, and $v_p$ are the volume transfer constant, the diffusion rate constant, and the plasma volume fraction, respectively.
+
+Therefore, Tofts model requires to:
+(i) estimate an \ac{aif} signal to later compute $C_p(t)$, and
+(ii) convert the \ac{mri} signal intensity into a concentration.
+
 \begin{description}
+  \item[Estimation of \ac{aif} signal] Two different strategies can be used to get an \ac{aif} signal:
+    (i) compute a population-based \ac{aif} signal or
+    (ii) estimate a patient-based \ac{aif} signal from the \ac{dce}-\ac{mri} data.
+
+    The former approach
   \item[Conversion of \ac{mri} signal intensity to concentration]
-
-  \item[Estimation of patient-based \ac{aif} signal \textit{vs.} population-based \ac{aif} signal]
 \end{description}

### 2016-08-11 02_methods/methods.tex
Add the segmentation of the aif

--- 2016-08-10 02_methods/methods.tex
@@
 
+\noindent where $\Conv$ is the convolution operator; $C_t(t)$ and $C_p(t)$ is the concentration of contrast agent in the tissue and in the plasma, respectively; $K_{trans}$, $k_{ep}$, and $v_p$ are the volume transfer constant, the diffusion rate constant, and the plasma volume fraction, respectively.
+
+Therefore, Tofts model requires to:
+(i) detect candidate voxels from the femoral or iliac arteries and estimate a patient-based \ac{aif} signal,
+(ii) convert the \ac{mri} signal intensity (i.e., \ac{aif} and dynamic signal) to a concentration, and
+(iii) in the case of a population-based \ac{aif}, estimate an \ac{aif} signal.
+
 \begin{description}
+  \item[Segmentation of artery voxels and patient-based \ac{aif} estimation] The \ac{aif} signal from \ac{dce}-\ac{mri} can be manually estimated by selecting the most-enhanced voxels from the femoral or iliac arteries~\citep{meng2010comparison}.
+    Few methods have been proposed to address the automated extraction of \ac{aif} signal.
+    \citeauthor{chen2008automatic} filter successively the possible candidates~\citep{chen2008automatic}:
+    (i) dynamic signals with small peak are rejecting by thresholding,
+    (ii) voxels with a small wash-in are rejected by thresholding,
+    (iii) a blob detector is used and large enough regions are kept, and
+    (iv) circular and cylindricality are used to reject the last false positive.
+    \citeauthor{zhu2011automated} propose an iterative method selecting voxels which best fit a gamma variate function~\citep{zhu2011automated}.
+    However, it requires to compute first and second derivatives as well as maximum curvature points.
+    \citeauthor{shanbhag2012generalized} propose a 4-steps algorithm~\citep{shanbhag2012generalized,fennessy2015quantitative}:
+    (i) remove slices with artefacts and find the best slices based on intrinsic anatomic landmarks and enhancement characteristics,
+    (ii) find the voxel candidates using the maximum enhanced voxels and a multi-label maximum entropy based thresholding algorithm,
+    (iii) excluding region next to the endorectal coil, and
+    (iv) selecting the best 5 candidates which meet enhancement characteristics and that are correlated.
+
+    All the above methods are rather complex and thus we propose a method which is based on the following simple assumptions:
+    (i) all possible \ac{aif} signal candidates should have a similar shape,
+    (ii) an high enhancement, and
+    (iii) the arteries should be almost round and within a size range.
+    Therefore, each slice is clustered into regions using K-means clustering with $k=6$.
+    The cluster with the highest enhancement\textemdash i.e.
+corresponding to the 90\textsuperscript{th} percentile of the maximum of each dynamic signal\textemdash contain the arteries and is selected.
+    Finally, regions with an eccentricity smaller than $0.5$ and an area in the range of $[100, 400]$ voxels are kept.
+    Additionally, to remove voxels contaminated by partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\citep{schabel2008uncertainty}.
+    An example of artery segmentation is shown in Fig.\,\ref{fig:aifseg}.
     \item[Conversion of \ac{mri} signal intensity to concentration]    
-
-  \item[Estimation of patient-based \ac{aif} signal \textit{vs.} population-based \ac{aif} signal]
 \end{description}

### 2016-08-12 02_methods/methods.tex
Added the demonstration to make the conversion
Finish to present the sub steps of Tofts

@@
     Finally, regions with an eccentricity smaller than $0.5$ and an area in the range of $[100, 400]$ voxels are kept.
-    Additionally, to remove voxels contaminated by partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\citep{schabel2008uncertainty}.
-    An example of artery segmentation is shown in Fig.\,\ref{fig:aifseg}.
-    \item[Conversion of \ac{mri} signal intensity to concentration]    
+    Additionally, to remove voxels contaminated by partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\citep{schabel2008uncertainty} and the average signal is computed.
+    A summary of the different segmentation steps is presented in Fig.\,\ref{fig:aifseg}.
+    \item[Conversion of \ac{mri} signal intensity to concentration] To estimate the free parameters of the Tofts model (see Eq.\,\eqref{eq:exttofts}), the concentration $C_t(t)$ and $C_p(t)$ need to be computed from the \ac{mri} signal intensity and the \ac{aif} signal, respectively.
+      This conversion is based on the equation of the FLASH sequence\textemdash see~\ref{app:signaltoconc} for details\textemdash and is formulated as in Eq.\,\eqref{eq:conv}:
+      \begin{equation}
+        C(t) = \frac{1}{TR \cdot r_1} \ln\left( \frac{1 - \cos \alpha \cdot S^{*}\frac{S(t)}{S_0}}{1 - S^{*}\frac{S(t)}{S_0}} \right) - \frac{R_{10}}{r_1} ,
+        \label{eq:conv}
+      \end{equation}
+      \noindent with,
+      \begin{equation}
+        S^{*} = \frac{1 - \exp(- TR \cdot R_{10})}{1 - \cos \alpha \cdot \exp(- TR \cdot R_{10})} ,
+        \label{eq:sstarconv}
+      \end{equation}
+      \noindent where $S(t)$ is the \ac{mri} signal, $S_0$ is the \ac{mri} signal prior to the injection of the contrast media, $\alpha$ is the flip angle, $TR$ is the \acf{tr}, $R_{10}$ is the pre-contrast tissue relaxation time also equal to $\frac{1}{T_{10}}$, $r_1$ is the relaxitivity coefficient of the contrast agent.
+
+      $T_{10}$ can be estimated from the acquisition of a T$_1$ map.
+      However, this modality was not part of the clinical trial in this research and the value of $T_{10}$ was fixed to \SI{1600}{\ms} for both blood and prostate as stated in the literature~\citep{fennessy2015quantitative,de2004mr,carr2011magnetic}.
+      \item[Estimation of population-based \ac{aif}] While estimating the pharmacokinetic parameters from Tofts model, the \ac{aif} concentration $C_p(t)$ can be computed either from the patient or a population.
+        We presented in the two previous sections the algorithms which allows to estimate the patient-based \ac{aif} concentration.
+        To compare with the previous approach, we also computed a population-based \ac{aif} which will be also later used to compare the performance of both approaches.
+        In that regard, the population-based \ac{aif} was estimated as in~\citep{meng2010comparison} by fitting the average patient-based \ac{aif}s to the model of~\cite{parker2006experimentally} which is formulated as in Eq.\,\eqref{eq:parker}:
+        \begin{equation}
+          C_p(t) = \sum_{n=1}^{2} \frac{A_n}{\sigma_n \sqrt{2 \pi}} \exp\left(\frac{- (t- T_n)^2}{2\sigma_{n}^{2}}\right) + \frac{\alpha \exp(-\beta t)}{1 + \exp{-s (t - \tau)}} ,
+          \label{eq:parker}
+        \end{equation}
+        \noindent where $A_n$, $T_n$, and $\sigma_n$ are the scaling constants, centers, and widths of the n\textsuperscript{th} Gaussian, $\alpha$ and $\beta$ are the amplitude and decay constant of the exponential; and $s$ and $\tau$ are the width and center of the sigmoid function, respectively.
 \end{description}

### 2016-08-13 02_methods/methods.tex
Finish the state-of-the-art draft

@@
 
-\subsubsection{Brix and Hoffmann models}
+\subsubsection{Brix and Hoffmann models}\label{sec:brixhoffmann}
 
@@
 
-\subsubsection{Tofts model}
+The parameters are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
+
+\subsubsection{Tofts model}\label{sec:tofts}
 
@@
       \begin{equation}
-        C(t) = \frac{1}{TR \cdot r_1} \ln\left( \frac{1 - \cos \alpha \cdot S^{*}\frac{S(t)}{S_0}}{1 - S^{*}\frac{S(t)}{S_0}} \right) - \frac{R_{10}}{r_1} ,
+        c(t) = \frac{1}{TR \cdot r_1} \ln\left( \frac{1 - \cos \alpha \cdot S^{*}\frac{s(t)}{S_0}}{1 - S^{*}\frac{s(t)}{S_0}} \right) - \frac{R_{10}}{r_1} ,
         \label{eq:conv}
@@
       \end{equation}
-      \noindent where $S(t)$ is the \ac{mri} signal, $S_0$ is the \ac{mri} signal prior to the injection of the contrast media, $\alpha$ is the flip angle, $TR$ is the \acf{tr}, $R_{10}$ is the pre-contrast tissue relaxation time also equal to $\frac{1}{T_{10}}$, $r_1$ is the relaxitivity coefficient of the contrast agent.
+      \noindent where $s(t)$ is the \ac{mri} signal, $S_0$ is the \ac{mri} signal prior to the injection of the contrast media, $\alpha$ is the flip angle, $TR$ is the \acf{tr}, $R_{10}$ is the pre-contrast tissue relaxation time also equal to $\frac{1}{T_{10}}$, $r_1$ is the relaxitivity coefficient of the contrast agent.
 
@@
 
-\subsubsection{\acs*{pun} model}
+The parameters are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
+
+\subsubsection{\acs*{pun} model}\label{sec:pun}
 
@@
 
-\subsubsection{}
+The parameters are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
+
+\subsubsection{Semi-quantitative analysis}\label{sec:semi}
+
+The semi-quantitative analysis of the \ac{dce}-\ac{mri} is equivalent to extract curve characteristics directly from the signal without a strict theoretical pharmacokinetic meaning.
+In this work, we use the model presented by~\cite{huisman2001accurate} which formulate the \ac{mri} signal as in Eq.\,\eqref{eq:huisman}:
+
+\begin{equation}
+  s(t) = \begin{cases}
+    S_0 & 0 \leq t \leq t_0 \\
+    S_M - (S_M - S_0) \exp\left( \frac{-(t - t_0)}{\tau} \right) & t_0 < t \leq t_0 + 2 \tau \\
+    S_M - (S_M - S_0) \exp\left( \frac{-(t - t_0)}{\tau} \right) + w(t - t_0 + 2 \tau) & t > t_0 + 2 \tau
+  \end{cases}
+  \label{eq:huisman}
+\end{equation}
+
+\noindent where $s(t)$ is the \ac{mri} signal intensity, $S_0$ is the pre-contrast signal intensity, $t_0$ is the time corresponding to the start of enhancement, $S_M$ and $\tau$ is the maximum of the signal and the exponential time constant, and $w$ is the slope of the linear part.
+
+\citeauthor{huisman2001accurate} argue that curve fitting via least-squares minimization using Nelder-Mead algorithm leads to inaccurate estimation of the free parameters: mainly the issue come from an incorrect estimation of the start of enhancement $t_0$ leading to incorrect estimation of the other parameters.
+Therefore, they propose to:
+(i) estimate robustly $t_0$,
+(ii) estimate $S_0$ by averaging the samples between $0$ and $t_0$
+(ii) estimate $w$ depending if the slope is significant or not,
+(iii) estimate $S_M$ which should be the point at the intersection of the most probable slope line and the plateau.
+
+Instead of these successive estimations, we propose a unified optimization in which $t_0$ is fixed since that this is a key parameter.
+Therefore, $t_0$ is robustly estimated from the \ac{aif} signal since that this is the most enhanced signal in which the start of enhancement is easily identifiable.
+The \ac{aif} signal is computed as in Section~\ref{sec:tofts}.
+$t_0$ is estimated by finding the maximum in the beginning of the first derivative of the \ac{mri} signal.
+Then, the function in Eq.\,\eqref{eq:huisman} is fitted using non-linear least squares with Trust Region Reflective algorithm.
+Furthermore, the parameters $\tau$ and $S_M$ are bounded during the optimization to ensure robust estimations.
+
+From Eq.\,\eqref{eq:huisman}, the following features are extracted:
+(i) the wash-in corresponding to the slope between $t_0$ and $t_0 + 2 \tau$,
+(ii) the wash-out corresponding to the parameter $w$,
+(iii) the area under the curve between $t_0$ and the end of the signal,
+(iv) the exponential time constant $\tau$, and
+(v) the relative enhancement $S_M - S_0$.
 

### 2016-08-14 03_experiments/experiments.tex
Add the outline and the frontmatter
Finish the introduction
add the first results

--- 2016-08-08 01_introduction/introduction.tex
@@
-\section{Introduction}
+\section{Experiments and results}\label{sec:experiments}
+
+\begin{table}
+  \caption{\acs*{auc} of the individual features for each method.}
+  \centering
+  \begin{tabular}{l c c}
+    \toprule
+    \textbf{Features} & Un-normalized data & Normalized data \\
+    \midrule
+    \textbf{Brix model} & & \\
+    \quad $A$         & & \\
+    \quad $k_{el}$    & & \\
+    \quad $k_{ep}$    & & \\
+    \textbf{Hoffmann model} & & \\
+    \quad $A$         & & \\
+    \quad $k_{el}$    & & \\
+    \quad $k_{ep}$    & & \\
+    \textbf{Tofts model with population \ac{aif}} & & \\
+    \quad $K_{trans}$ & & \\
+    \quad $v_{p}$     & & \\
+    \quad $k_{ep}$    & & \\
+    \textbf{Tofts model with patient \ac{aif}} & & \\
+    \quad $K_{trans}$ & & \\
+    \quad $v_{p}$     & & \\
+    \quad $k_{ep}$    & & \\
+    \textbf{\ac{pun} model} & & \\
+    \quad $a_0$       & & \\
+    \quad $r$         & & \\
+    \quad $\beta$     & & \\
+    \textbf{Semi-quantitative analysis} & & \\
+    \quad wash-in     & & \\
+    \quad wash-out    & & \\
+    \quad IAUC        & & \\
+    \quad $\tau$      & & \\
+    \quad $S_M - S_0$ & & \\
+    \bottomrule
+  \end{tabular}
+  \label{tab:resfeats}
+\end{table}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/unormalized/rf.pdf}
+  \caption{\acs*{roc} analysis using a \acs*{rf} classifier for the different quantification methods without data normalization.}
+  \label{fig:rfunorm}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/unormalized/nb.pdf}
+  \caption{\acs*{roc} analysis using a \acs*{nb} classifier for the different quantification methods without data normalization.}
+  \label{fig:rfunorm}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/normalized/rf.pdf}
+  \caption{\acs*{roc} analysis using a \acs*{rf} classifier for the different quantification methods with data normalization.}
+  \label{fig:rfunorm}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/normalized/nb.pdf}
+  \caption{\acs*{roc} analysis using a \acs*{nb} classifier for the different quantification methods with data normalization.}
+  \label{fig:rfunorm}
+\end{figure}
 

### 2016-08-17 03_experiments/experiments.tex
Add all the results

@@
   \centering
-  \begin{tabular}{l c c}
+  \begin{tabular}{l c c c c}
     \toprule
-    \textbf{Features} & Un-normalized data & Normalized data \\
+    \textbf{Features} & \multicolumn{2}{c}{Un-normalized data} & \multicolumn{2}{c}{Normalized data} \\
+    & \acs*{rf} & \acs*{nb} & \acs*{rf} & \acs*{nb} \\
     \midrule
-    \textbf{Brix model} & & \\
-    \quad $A$         & & \\
-    \quad $k_{el}$    & & \\
-    \quad $k_{ep}$    & & \\
-    \textbf{Hoffmann model} & & \\
-    \quad $A$         & & \\
-    \quad $k_{el}$    & & \\
-    \quad $k_{ep}$    & & \\
-    \textbf{Tofts model with population \ac{aif}} & & \\
-    \quad $K_{trans}$ & & \\
-    \quad $v_{p}$     & & \\
-    \quad $k_{ep}$    & & \\
-    \textbf{Tofts model with patient \ac{aif}} & & \\
-    \quad $K_{trans}$ & & \\
-    \quad $v_{p}$     & & \\
-    \quad $k_{ep}$    & & \\
-    \textbf{\ac{pun} model} & & \\
-    \quad $a_0$       & & \\
-    \quad $r$         & & \\
-    \quad $\beta$     & & \\
-    \textbf{Semi-quantitative analysis} & & \\
-    \quad wash-in     & & \\
-    \quad wash-out    & & \\
-    \quad IAUC        & & \\
-    \quad $\tau$      & & \\
-    \quad $S_M - S_0$ & & \\
+    \textbf{Brix model} & & & & \\
+    \quad $A$         & 0.54 & 0.62 & 0.58 & 0.67 \\
+    \quad $k_{el}$    & 0.55 & 0.52 & 0.54 & 0.61 \\
+    \quad $k_{ep}$    & 0.51 & 0.52 & 0.51 & 0.58 \\
+    \textbf{Hoffmann model} & & & & \\
+    \quad $A$         & 0.52 & 0.50 & 0.51 & 0.56 \\
+    \quad $k_{el}$    & 0.55 & 0.53 & 0.54 & 0.64 \\
+    \quad $k_{ep}$    & 0.55 & 0.50 & 0.53 & 0.66 \\
+    \textbf{Tofts model with population \ac{aif}} & & & & \\
+    \quad $K_{trans}$ & 0.56 & 0.62 & 0.56 & 0.65 \\
+    \quad $v_{e}$     & 0.51 & 0.50 & 0.50 & 0.52 \\
+    \quad $v_{p}$     & 0.53 & 0.63 & 0.55 & 0.53 \\
+    \textbf{Tofts model with patient \ac{aif}} & & & & \\
+    \quad $K_{trans}$ & 0.57 & 0.66 & 0.56 & 0.65 \\
+    \quad $v_{e}$     & 0.49 & 0.50 & 0.51 & 0.52 \\
+    \quad $v_{p}$     & 0.53 & 0.37 & 0.57 & 0.65 \\
+    \textbf{\ac{pun} model} & & & & \\
+    \quad $a_0$       & 0.52 & 0.53 & 0.53 & 0.51  \\
+    \quad $r$         & 0.53 & 0.59 & 0.55 & 0.55 \\
+    \quad $\beta$     & 0.55 & 0.56 & 0.53 & 0.44 \\
+    \textbf{Semi-quantitative analysis} & & & & \\
+    \quad wash-in     & 0.59 & 0.64 & 0.55 & 0.51 \\
+    \quad wash-out    & 0.52 & 0.50 & 0.56 & 0.66 \\
+    \quad IAUC        & 0.51 & 0.61 & 0.52 & 0.64 \\
+    \quad $\tau$      & 0.57 & 0.57 & 0.56 & 0.61 \\
+    \quad $S_M - S_0$ & 0.56 & 0.63 & 0.53 & 0.64 \\
     \bottomrule
@@
 \end{table}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/rf.pdf}
+  \caption{\acs*{roc} analysis using a \acs*{rf} classifier using the \ac{dce} signal with and without normalization.}
+  \label{fig:rfunorm}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/nb.pdf}
+  \caption{\acs*{roc} analysis using a \acs*{nb} classifier using the \ac{dce} signal with and without normalization.}
+  \label{fig:rfunorm}
+\end{figure}
 

### 2016-08-18 03_experiments/experiments.tex
Add a description about the data

@@
 \section{Experiments and results}\label{sec:experiments}
+
+\subsection{Data}\label{sec:data}
+
+The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
+The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
+Aside of the \ac{mri} examination, these patients also have underwent a guided-biopsy.
+The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
+Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
+An experienced radiologist has segmented the prostate organ --- on \ac{t2w}- and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
+
+The \ac{dce}-\ac{mri} sequence consists in a kinetic study composed of 40 samples over time with a time resolution of \SI{6.5}{\second}.
+These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w} \ac{mri} sequence with dimensions of $448 \times 360 \times 64$ and voxel spacing of $0.68 \times 0.68 \times 1.25 $ mm\textsuperscript{3}.
+A linear interpolation is used to compute missing data during the up-sampling.
+The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
+Furthermore, a non-rigid registration is performed between the \ac{t2w}- and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
+The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
+
+\subsection{Results}
 

### 2016-08-18 02_methods/methods.tex
start with the normalization

@@
 \subsection{Normalization of \ac{dce}-\ac{mri} images}\label{sec:norm}
+
+\begin{figure}
+  \centering
+  \hspace*{\fill}
+  \subfigure[Patient 1]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1.pdf}} \hfill
+  \subfigure[Patient 2]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}}
+  \hspace*{\fill}
+  \caption{Illustration of the variations of the intensity \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
+  \label{fig:heatmap}
+\end{figure}
+
+In this work, we proposed a method to normalized \ac{dce}-\ac{mri} prostate data.
+However, it can be note that this method can be used for any \ac{dce}-\ac{mri} sequences.
+The aim of the method is to reduce the intra-patient variation that can occur during the acquisition.
+These variations can be highlighted by observing the evolution of the intensity \ac{pdf} of the \ac{dce}-\ac{mri} over time, as shown in Fig.\,\ref{fig:heatmap}.
+These variations are:
+(i) an offset of the peak value before pre-contrast,
+(ii) a time offset depending of the contrast injection, and
+(iii) a scale factor related to the enhancement.
+Therefore, our normalization method should attenuate all these variations
+
+\subsubsection{Baseline alignment of each \ac{dce}-\ac{mri} serie}
+
+Short-path using graph minimization.
+
+\subsubsection{Estimate the dispersion of the voxel intensities}
+
+MSE.
+
+\subsubsection{Parametric curve alignment}
+
+Model using 1 translation and one scale.
 

### 2016-08-18 03_experiments/experiments.tex
start with the normalization

@@
 The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
+
+\subsection{Implementation}
+
+The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
+The data used for this work are also publicly available\footnote{\url{http://some-url.com}}.
 

### 2016-08-19 02_methods/methods.tex
Finish to explain the graph based approach

--- 2016-08-13 02_methods/methods.tex
@@
 \subsection{Normalization of \ac{dce}-\ac{mri} images}\label{sec:norm}
+
+\begin{figure}
+  \centering
+  \hspace*{\fill}
+  \subfigure[Patient 1]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1.pdf}} \hfill
+  \subfigure[Patient 2]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}}
+  \hspace*{\fill}
+  \caption{Illustration of the variations of the intensity \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
+  \label{fig:heatmap}
+\end{figure}
+
+In this work, we proposed a method to normalized \ac{dce}-\ac{mri} prostate data, although it can be ported to any \ac{dce}-\ac{mri} sequences.
+The aim of the method is to reduce the intra-patient variations that can occur during acquisition.
+In \ac{t2w}-\ac{mri} prostate image, an offset and a scale factor are the two factors driving the intra-patient variation.
+Therefore, these variations are corrected using a $z$-score approach assuming that the data follow a Rician distribution~\citep{lemaitre2016normalization}.
+In \ac{dce}-\ac{mri}, there is additional factors characterizing such variations.
+These variations can be highlighted by observing the evolution of the intensity \ac{pdf} of the \ac{dce}-\ac{mri} over time, as shown in the heatmap in Fig.\,\ref{fig:heatmap}.
+These variations are:
+(i) an offset of the peak value before pre-contrast,
+(ii) a time offset depending of the contrast injection, and
+(iii) a global scale factor related to the enhancement.
+Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.
+
+\subsubsection{Graph-based offset correction for each \ac{dce}-\ac{mri} sequence}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{02_methods/figures/estimator.pdf}
+  \caption{Illustration of the estimator found using the shortest-path through the graph.}
+  \label{fig:estimator}
+\end{figure}
+
+Before to standardize each sequence, the first step of the normalization is to cancel the intensity shift which is specific for each patient.
+The intensity \ac{pdf} do not follow either a Rician or Gaussian distribution over time.
+Therefore, the mean cannot be used as a potential estimate for the offset.
+Additionally, this offset should be characterized by a smooth transition over time.
+This problem can be solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{fig:heatmap}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
+Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar of the heatmap as a node and connecting each pair of bars by an edge.
+The edge weight $w_{ij}$ between two nodes $i$ and $j$ corresponding to two pixels at position $(x_i, y_i)$ and $(x_j, y_j)$, respectively, is defined as in Eq.\,\eqref{eq:weight}:
+
+\begin{equation}
+  w_{ij} = \begin{cases}
+    \alpha \exp(1 - \frac{H(i)}{\max(H)})       & \text{if } x_j = x_i + 1 \text{ and } y_j = y_i \\
+    (1 - \alpha) \exp(1 - \frac{H(i)}{\max(H)}) & \text{if } x_j = x_i \text{ and } y_j = y_i + 1 \\
+    0                                           & \text{otherwise}
+  \end{cases} ,
+  \label{eq:weight}
+\end{equation}
+
+\noindent where $H$ is the heatmap, $\alpha$ is a smoothing parameter controlling the partitioning.
+
+Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra algorithm.
+The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
+To ensure a robust estimation of the offset, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
+The procedure is stopped once that the offset found do not change.
+In general, this process is not repeated more than 3 iterations.
+An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.
+
+\subsubsection{Estimate the dispersion of the voxel intensities}
+
+MSE.
+
+\subsubsection{Parametric curve alignment}
+
+Model using 1 translation and one scale.
 

### 2016-08-19 02_methods/methods.tex
Finish the draft for the normalization

@@
 An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.
+Finally, each sequence is shifted using this offset.
 
-\subsubsection{Estimate the dispersion of the voxel intensities}
+\subsubsection{Time offset and data dispersion correction}
 
-MSE.
+\begin{figure}
+  \centering
+  \hspace*{\fill}
+  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse.pdf}} \hfill
+  \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
+  \hspace*{\fill}
+  \caption{Illustration of the correction of the time offset and the data dispersion.}
+  \label{fig:curveal}
+\end{figure}
 
-\subsubsection{Parametric curve alignment}
+The next variations to correct are the time offset and the data dispersion.
+By computing the \ac{rmse} for each \ac{dce}-\ac{mri}, one can observed these two variations as shown in Fig.\,\ref{fig:rmse}.
+Therefore, to correct these variations, we propose to register each patient \ac{rmse} to a mean model which corresponds to the mean of all patients \ac{rmse}.
+The parametric model to perform the registration is formulated as in Eq.\,\eqref{eq:model}:
 
-Model using 1 translation and one scale.
+\begin{equation}
+  T(\alpha, \tau, f(t)) = \alpha f(t - \tau) ,
+  \label{eq:model}
+\end{equation}
+
+\noindent where $\alpha$ and $\tau$ are the two parameters handling the time offset and global scale, respectively, $f(\cdot)$ is the \ac{rmse} function.
+
+Therefore the registration problem is equivalent to:
+
+\begin{equation}
+  \argmin_{\alpha, \tau} = \sum_{t=0}^{N} \left[ T\left(\alpha, \tau, f(t)\right) - \mu(t) \right]^{2} ,
+  \label{eq:cost}
+\end{equation}
+
+\noindent where $\mu(\cdot)$ is the mean model, $N$ is the number of \ac{dce}-\ac{mri} serie.
+
+Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
+Once all these parameters have been inferred, the data can be shifted as well as scale.
 

### 2016-08-20 03_experiments/experiments.tex
Change the results selecting the important facts

@@
 
+% \begin{table}
+%   \caption{\acs*{auc} of the individual features for each method.}
+%   \centering
+%   \begin{tabular}{l c c c c}
+%     \toprule
+%     \textbf{Features} & \multicolumn{2}{c}{Un-normalized data} & \multicolumn{2}{c}{Normalized data} \\
+%     & \acs*{rf} & \acs*{nb} & \acs*{rf} & \acs*{nb} \\
+%     \midrule
+%     \textbf{Brix model} & & & & \\
+%     \quad $A$         & 0.54 & 0.62 & 0.58 & 0.67 \\
+%     \quad $k_{el}$    & 0.55 & 0.52 & 0.54 & 0.61 \\
+%     \quad $k_{ep}$    & 0.51 & 0.52 & 0.51 & 0.58 \\
+%     \textbf{Hoffmann model} & & & & \\
+%     \quad $A$         & 0.52 & 0.50 & 0.51 & 0.56 \\
+%     \quad $k_{el}$    & 0.55 & 0.53 & 0.54 & 0.64 \\
+%     \quad $k_{ep}$    & 0.55 & 0.50 & 0.53 & 0.66 \\
+%     \textbf{Tofts model with population \ac{aif}} & & & & \\
+%     \quad $K_{trans}$ & 0.56 & 0.62 & 0.56 & 0.65 \\
+%     \quad $v_{e}$     & 0.51 & 0.50 & 0.50 & 0.52 \\
+%     \quad $v_{p}$     & 0.53 & 0.63 & 0.55 & 0.53 \\
+%     \textbf{Tofts model with patient \ac{aif}} & & & & \\
+%     \quad $K_{trans}$ & 0.57 & 0.66 & 0.56 & 0.65 \\
+%     \quad $v_{e}$     & 0.49 & 0.50 & 0.51 & 0.52 \\
+%     \quad $v_{p}$     & 0.53 & 0.37 & 0.57 & 0.65 \\
+%     \textbf{\ac{pun} model} & & & & \\
+%     \quad $a_0$       & 0.52 & 0.53 & 0.53 & 0.51  \\
+%     \quad $r$         & 0.53 & 0.59 & 0.55 & 0.55 \\
+%     \quad $\beta$     & 0.55 & 0.56 & 0.53 & 0.44 \\
+%     \textbf{Semi-quantitative analysis} & & & & \\
+%     \quad wash-in     & 0.59 & 0.64 & 0.55 & 0.51 \\
+%     \quad wash-out    & 0.52 & 0.50 & 0.56 & 0.66 \\
+%     \quad IAUC        & 0.51 & 0.61 & 0.52 & 0.64 \\
+%     \quad $\tau$      & 0.57 & 0.57 & 0.56 & 0.61 \\
+%     \quad $S_M - S_0$ & 0.56 & 0.63 & 0.53 & 0.64 \\
+%     \bottomrule
+%   \end{tabular}
+%   \label{tab:resfeats}
+% \end{table}
+
 \begin{table}
-  \caption{\acs*{auc} of the individual features for each method.}
+  \caption{\acs*{auc} for each individual pharmacokinetic parameter using a \acs*{nb} classifier.}
   \centering
-  \begin{tabular}{l c c c c}
+  \begin{tabular}{l c c}
     \toprule
-    \textbf{Features} & \multicolumn{2}{c}{Un-normalized data} & \multicolumn{2}{c}{Normalized data} \\
-    & \acs*{rf} & \acs*{nb} & \acs*{rf} & \acs*{nb} \\
+    \textbf{Features} & Un-normalized data & Normalized data \\
     \midrule
-    \textbf{Brix model} & & & & \\
-    \quad $A$         & 0.54 & 0.62 & 0.58 & 0.67 \\
-    \quad $k_{el}$    & 0.55 & 0.52 & 0.54 & 0.61 \\
-    \quad $k_{ep}$    & 0.51 & 0.52 & 0.51 & 0.58 \\
-    \textbf{Hoffmann model} & & & & \\
-    \quad $A$         & 0.52 & 0.50 & 0.51 & 0.56 \\
-    \quad $k_{el}$    & 0.55 & 0.53 & 0.54 & 0.64 \\
-    \quad $k_{ep}$    & 0.55 & 0.50 & 0.53 & 0.66 \\
-    \textbf{Tofts model with population \ac{aif}} & & & & \\
-    \quad $K_{trans}$ & 0.56 & 0.62 & 0.56 & 0.65 \\
-    \quad $v_{e}$     & 0.51 & 0.50 & 0.50 & 0.52 \\
-    \quad $v_{p}$     & 0.53 & 0.63 & 0.55 & 0.53 \\
-    \textbf{Tofts model with patient \ac{aif}} & & & & \\
-    \quad $K_{trans}$ & 0.57 & 0.66 & 0.56 & 0.65 \\
-    \quad $v_{e}$     & 0.49 & 0.50 & 0.51 & 0.52 \\
-    \quad $v_{p}$     & 0.53 & 0.37 & 0.57 & 0.65 \\
-    \textbf{\ac{pun} model} & & & & \\
-    \quad $a_0$       & 0.52 & 0.53 & 0.53 & 0.51  \\
-    \quad $r$         & 0.53 & 0.59 & 0.55 & 0.55 \\
-    \quad $\beta$     & 0.55 & 0.56 & 0.53 & 0.44 \\
-    \textbf{Semi-quantitative analysis} & & & & \\
-    \quad wash-in     & 0.59 & 0.64 & 0.55 & 0.51 \\
-    \quad wash-out    & 0.52 & 0.50 & 0.56 & 0.66 \\
-    \quad IAUC        & 0.51 & 0.61 & 0.52 & 0.64 \\
-    \quad $\tau$      & 0.57 & 0.57 & 0.56 & 0.61 \\
-    \quad $S_M - S_0$ & 0.56 & 0.63 & 0.53 & 0.64 \\
+    \textbf{Brix model} & & \\
+    \quad $A$         & 0.62 & 0.67 \\
+    \quad $k_{el}$    & 0.52 & 0.61 \\
+    \quad $k_{ep}$    & 0.52 & 0.58 \\
+    \textbf{Hoffmann model} & & \\
+    \quad $A$         & 0.50 & 0.56 \\
+    \quad $k_{el}$    & 0.53 & 0.64 \\
+    \quad $k_{ep}$    & 0.50 & 0.66 \\
+    \textbf{Tofts model with population \ac{aif}} & & \\
+    \quad $K_{trans}$ & 0.62 & 0.65 \\
+    \quad $v_{e}$     & 0.50 & 0.52 \\
+    \quad $v_{p}$     & 0.63 & 0.53 \\
+    \textbf{Tofts model with patient \ac{aif}} & & \\
+    \quad $K_{trans}$ & 0.66 & 0.65 \\
+    \quad $v_{e}$     & 0.50 & 0.52 \\
+    \quad $v_{p}$     & 0.37 & 0.65 \\
+    \textbf{\ac{pun} model} & & \\
+    \quad $a_0$       & 0.53 & 0.51  \\
+    \quad $r$         & 0.59 & 0.55 \\
+    \quad $\beta$     & 0.56 & 0.44 \\
+    \textbf{Semi-quantitative analysis} & & \\
+    \quad wash-in     & 0.64 & 0.51 \\
+    \quad wash-out    & 0.50 & 0.66 \\
+    \quad IAUC        & 0.61 & 0.64 \\
+    \quad $\tau$      & 0.57 & 0.61 \\
+    \quad $S_M - S_0$ & 0.63 & 0.64 \\
     \bottomrule
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/rf.pdf}
-  \caption{\acs*{roc} analysis using a \acs*{rf} classifier using the \ac{dce} signal with and without normalization.}
-  \label{fig:rfunorm}
+  \hspace*{\fill}
+  \subfigure[Without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/rf.pdf}} \hfill
+  \subfigure[With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/rf.pdf}}
+  \hspace*{\fill}
+  \caption{\acs*{roc} analysis using a \acs*{rf} classifier with and without normalization \ac{dce}-\ac{mri} data for different pharmacokinetic models.}
+  \label{fig:normpharmarf}
 \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \hspace*{\fill}
+%   \subfigure[Without normalization.]{\label{fig:nbpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/nb.pdf}} \hfill
+%   \subfigure[With normalization.]{\label{fig:nbpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/nb.pdf}}
+%   \hspace*{\fill}
+%   \caption{\acs*{roc} analysis using a \acs*{nb} classifier with and without normalization \ac{dce}-\ac{mri} data for different pharmacokinetic models.}
+%   \label{fig:normpharmanb}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \hspace*{\fill}
+%   \subfigure[\acs*{rf} classifier.]{\label{fig:rfunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/rf.pdf}} \hfill
+%   \subfigure[\acs*{nb} classifier.]{\label{fig:nbunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/nb.pdf}}
+%   \hspace*{\fill}
+%   \caption{\acs*{roc} analysis using the entire \ac{dce}-\ac{mri} signal with and without normalization.}
+%   \label{fig:unormdcesignal}
+% \end{figure}
 
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/nb.pdf}
-  \caption{\acs*{roc} analysis using a \acs*{nb} classifier using the \ac{dce} signal with and without normalization.}
-  \label{fig:rfunorm}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/unormalized/rf.pdf}
-  \caption{\acs*{roc} analysis using a \acs*{rf} classifier for the different quantification methods without data normalization.}
-  \label{fig:rfunorm}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/unormalized/nb.pdf}
-  \caption{\acs*{roc} analysis using a \acs*{nb} classifier for the different quantification methods without data normalization.}
-  \label{fig:rfunorm}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/normalized/rf.pdf}
-  \caption{\acs*{roc} analysis using a \acs*{rf} classifier for the different quantification methods with data normalization.}
-  \label{fig:rfunorm}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/normalized/nb.pdf}
-  \caption{\acs*{roc} analysis using a \acs*{nb} classifier for the different quantification methods with data normalization.}
-  \label{fig:rfunorm}
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/rf.pdf}
+  \caption{\acs*{roc} analysis using the entire \ac{dce}-\ac{mri} signal with and without normalization in conjunction with a \acs*{rf} classifier.}
+  \label{fig:rfnormdcesignal}
 \end{figure}

### 2016-08-20 02_methods/methods.tex
Added the semgnetation of the AIF images

@@
 
+\begin{figure}
+  \centering
+  \hspace*{\fill}
+  \subfigure[Original image.]{\label{fig:org}\includegraphics[width=.3\textwidth]{02_methods/figures/original.pdf}} \hfill
+  \subfigure[Candidates region after clustering.]{\label{fig:cand}\includegraphics[width=.3\textwidth]{02_methods/figures/candidate.pdf}} \hfill
+  \subfigure[Regions selected after applying the different criteria.]{\label{fig:final}\includegraphics[width=.3\textwidth]{02_methods/figures/aif.pdf}}
+  \hspace*{\fill}
+  \caption{Illustration of the segmentation of the area used to determine the \acs*{aif}.}
+  \label{fig:aif}
+\end{figure}
+
 \begin{description}
@@
     Additionally, to remove voxels contaminated by partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\citep{schabel2008uncertainty} and the average signal is computed.
-    A summary of the different segmentation steps is presented in Fig.\,\ref{fig:aifseg}.
+    A summary of the different segmentation steps is presented in Fig.\,\ref{fig:aif}.
     \item[Conversion of \ac{mri} signal intensity to concentration] To estimate the free parameters of the Tofts model (see Eq.\,\eqref{eq:exttofts}), the concentration $C_t(t)$ and $C_p(t)$ need to be computed from the \ac{mri} signal intensity and the \ac{aif} signal, respectively.

### 2016-08-22 02_methods/methods.tex
Comment the results

@@
-\section{Methods}\label{sec:methods}
+\section{Materials and methods}\label{sec:methods}
+
+\subsection{Data}\label{sec:data}
+
+The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
+The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
+Aside of the \ac{mri} examination, these patients also have underwent a guided-biopsy.
+The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
+Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
+An experienced radiologist has segmented the prostate organ --- on \ac{t2w}- and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
+
+The \ac{dce}-\ac{mri} sequence consists in a kinetic study composed of 40 samples over time with a time resolution of \SI{6.5}{\second}.
+These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w} \ac{mri} sequence with dimensions of $448 \times 360 \times 64$ and voxel spacing of $0.68 \times 0.68 \times 1.25 $ mm\textsuperscript{3}.
+A linear interpolation is used to compute missing data during the up-sampling.
+The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
+Furthermore, a non-rigid registration is performed between the \ac{t2w}- and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
+The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
+
+\subsection{Implementation}
+
+The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
+The data used for this work are also publicly available\footnote{\url{http://kaggle.com}}.
 

### 2016-08-22 03_experiments/experiments.tex
Comment the results

@@
 
-\subsection{Data}\label{sec:data}
-
-The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
-The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
-Aside of the \ac{mri} examination, these patients also have underwent a guided-biopsy.
-The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
-Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
-An experienced radiologist has segmented the prostate organ --- on \ac{t2w}- and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
-
-The \ac{dce}-\ac{mri} sequence consists in a kinetic study composed of 40 samples over time with a time resolution of \SI{6.5}{\second}.
-These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w} \ac{mri} sequence with dimensions of $448 \times 360 \times 64$ and voxel spacing of $0.68 \times 0.68 \times 1.25 $ mm\textsuperscript{3}.
-A linear interpolation is used to compute missing data during the up-sampling.
-The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
-Furthermore, a non-rigid registration is performed between the \ac{t2w}- and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
-The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
-
-\subsection{Implementation}
-
-The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
-The data used for this work are also publicly available\footnote{\url{http://some-url.com}}.
-
-\subsection{Results}
+\subsection{Classification of individual parameter for each model}
 
@@
 
+The first experiment consists in comparing the classification performance using each individual parameter for the different models, to assess the potential benefit of the normalization method.
+Therefore, each feature is individually classified using a Gaussian \ac{nb} classifier in a \ac{lopo} fashion.
+{\color{red}\ac{nb} is used due to its simplicity and it enables to check the fitted parameters for interpretation.}
+The results are summarized in Table~\ref{tab:resfeats}.
+It can be noted that in the majority of the cases, normalizing the data improve the classification performance in terms of \ac{auc}.
+Only the \ac{pun} model does not follow this tendency {\color{red} which might due to the fact that the function do not fit the data as good as the other model - WE WILL NEED SOME RMSE FOR EACH FITTING IF WE SAY SO.}.
+
+{\color{red}It could be interesting to check the value of the mean and std of the \ac{nb}. We could compute a ratio which refer to the class separability.}
+
 \begin{table}
@@
 
+\subsection{Classification by combining the parameters for each model}
+
+Usually, the parameters are combined to form a multi-dimensional prior to classify the data.
+Therefore, for each model, all parameters are combined and classified using a \ac{rf} classifier in a \ac{lopo} fashion.
+The use of \ac{rf} is motivated since that it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer}.
+The results are summarized by making \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
+It can be noted that in all the cases the normalization of the data improve the classification performance.
+
 \begin{figure}
@@
 
+\subsection{Classification of the entire enhanced \acs*{dce}-\acs*{mri} signal}
+
+The quantification methods are extracting a minimal set of parameters which should characterized the enhancement \ac{dce}-\ac{mri} curves.
+However, this extraction could discard some information of the signal.
+This experiment attends to use the whole \ac{dce}-\ac{mri} signal to perform the classification.
+Therefore, the enhanced signal is classified using a \ac{rf} classifier in a \ac{lopo} fashion.
+The \ac{roc} analysis and \ac{auc} are reported in Fig.\,\ref{fig:rfnormdcesignal}.
+It can be note that the worst performance are achieved while data without normalization.
+However, normalizing the data, this classification strategy lead the best classification performance, outperforming any quantification method, showing the importance of our normalization algorithm.
+
 \begin{figure}

### 2016-08-22 04_discussions/discussions.tex
Add the outline and the frontmatter
Finish the introduction
Add some draft discussion and conclusion

--- 2016-08-08 01_introduction/introduction.tex
@@
-\section{Introduction}
+\section{Discussions}\label{sec:discussions}
+
+\begin{itemize}
+  \item Discuss about the T1 parameters in Tofts and say that we can do better probably.
+  \item Compare the two approach for the AIF.
+  \item Make a discussion about the detailed interpretation of individual feature classification.
+There is something to discuss about the semi-quantitative from wash-in to wash-out reversed performance.
+Something also about the PUN model.
+  \item Explain the drawbacks of the whole signal classification (time).
+\end{itemize}
 

### 2016-08-22 05_conclusions/conclusions.tex
Add the outline and the frontmatter
Finish the introduction
Add some draft discussion and conclusion

--- 2016-08-08 01_introduction/introduction.tex
@@
-\section{Introduction}
+\section{Conclusions and future works}\label{sec:conclusions}
+
+In this work, we presented a new method for normalizing/standardizing \ac{dce}-\ac{mri} data.
+Through different experiments, we show the benefit of such normalization.
+Furthermore, we show that using the whole \ac{dce}-\ac{mri} signal instead extracting parameters lead to the best classification performance.
+
+As avenues for future research, this normalization has to be part of a \ac{mpmri} \ac{cad} system, mixing \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri}, \ac{dw}-\ac{mri}, and \ac{mrsi}.
 

### 2016-08-23 01_introduction/introduction.tex
Review the introduction and data

@@
 In this regard, \ac{mpmri} is frequently used to build robust \ac{cad} systems to detect, localize, and grade \ac{cap}.
-In general, \ac{cad} systems are based on \ac{mpmri} which combines several of the following modalities~\citep{lemaitre2015computer}: \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri}, \ac{adc} maps, and \ac{mrsi}.
+In general, \ac{cad} systems are based on \ac{mpmri} which potentially combines several of the following modalities~\citep{lemaitre2015computer}: \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri}, \ac{adc} maps, and \ac{mrsi}.
 
 In \ac{dce}-\ac{mri}, a contrast media is injected intravenously and a set of images is acquired over time.
-Consequently, each voxel in the image is a dynamic signal which is related to the vascular properties of the tissue.
+Consequently, each voxel in an image corresponds to a dynamic signal is related to the vascular properties of the tissue.
 In fact, these properties are automatically extracted using quantitative or semi-quantitative approaches~\citep{lemaitre2015computer}.
@@
 The former group of approaches uses pharmacokinetic modelling based on a bicompartment model, namely Brix~\citep{brix1991pharmacokinetic} and Tofts~\citep{tofts1995quantitative} models.
-The parameters of the Brix model are found assuming a linear relationship between the media concentration and \ac{mri} signal intensity.
-This assumption has shown, however, to lead to inaccurate parameter calculation~\citep{heilmann2006determination}.
-In the contrary, Tofts model only requires a conversion from \ac{mri} signal intensity to concentration, which can become a non-linear relationship using specific equation of \ac{mri} sequences (e.g., FLASH sequence).
+The parameters of the Brix model are inferred assuming a linear relationship between the media concentration and the \ac{mri} signal intensity.
+This assumption has shown, however, to lead to inaccurately estimate the pharmacokinetic parameters~\citep{heilmann2006determination}.
+In the contrary, Tofts model requires a conversion from \ac{mri} signal intensity to concentration, which become a non-linear relationship using specific equation of \ac{mri} sequences (e.g., FLASH sequence).
 Tofts modelling suffers, however, from an higher complexity~\citep{gliozzi2011phenomenological}.
-The conversion using the non-linear approach requires to acquire a T$_1$ map which is not always possible during clinical examination.
-Furthermore, the parameter calculation require the \ac{aif} which is challenging to measure and can also lead to inaccurate estimation of the parameters.
+Indeed, the conversion using the non-linear approach requires to acquire a T$_1$ map which is not always possible during clinical examination.
+Additionally, the parameter calculation requires the \ac{aif} which is challenging to measure and can also lead to inaccurate estimation.
 
@@
 Nevertheless, all presented methods suffer from two major drawbacks:
-(i) the inter-patient variability of the data lead to a variation of the parameters estimated and to poor classification performance while designing \ac{cad} systems, and
+(i) the inter-patient variability of the data lead to a variation of the parameters estimated and subsequently to poor classification performance while designing \ac{cad} systems, and
 (ii) only few parameters are used to characterize the dynamic signal implying that some information are discarded.
@@
 In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduce the inter-patient variability of the data.
-Furthermore, we show that using the full normalized signal lead to the best classification performance.
+Furthermore, we show that using the full normalized \ac{dce}-\ac{mri} signal lead to the best classification performance.
 

### 2016-08-23 02_methods/methods.tex
Review the introduction and data

@@
 Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
-An experienced radiologist has segmented the prostate organ --- on \ac{t2w}- and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
+An experienced radiologist has segmented the prostate organ --- on \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
 
-The \ac{dce}-\ac{mri} sequence consists in a kinetic study composed of 40 samples over time with a time resolution of \SI{6.5}{\second}.
-These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w} \ac{mri} sequence with dimensions of $448 \times 360 \times 64$ and voxel spacing of $0.68 \times 0.68 \times 1.25 $ mm\textsuperscript{3}.
-A linear interpolation is used to compute missing data during the up-sampling.
+A \SI{3}{\mm} slice fat-suppressed \ac{t2w} fast spin-echo sequence (\ac{tr}/\ac{te}/\ac{etl}: \SI{3400}{\ms}/\SI{85}{\ms}/13) is used to acquire images in sagittal and oblique coronal planes, the latter planes being orientated perpendicular or parallel to the prostate \ac{pz} – rectal wall axis.
+Three-dimensional \ac{t2w} fast spin-echo (\ac{tr}/\ac{te}/\ac{etl}: \SI{3600}{\ms}/\SI{143}{\ms}/109, slice thickness: \SI{1.25}{\mm}) images are then acquired in an oblique axial plane.
+The nominal matrix and \ac{fov} of the 3D \ac{t2w} fast spin-echo images are $320 \times 256$ and $280 \times 240$ mm\textsuperscript{2}, respectively, thereby affording sub-millimetric pixel resolution within the imaging plane.
+
+\ac{dce}-\ac{mri} are performed using a fat suppressed 3D T1 VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
+A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
+
+These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using linear interpolation.
 The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
-Furthermore, a non-rigid registration is performed between the \ac{t2w}- and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
+Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
 The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
@@
 
-In this work, we proposed a method to normalized \ac{dce}-\ac{mri} prostate data, although it can be ported to any \ac{dce}-\ac{mri} sequences.
-The aim of the method is to reduce the intra-patient variations that can occur during acquisition.
-In \ac{t2w}-\ac{mri} prostate image, an offset and a scale factor are the two factors driving the intra-patient variation.
-Therefore, these variations are corrected using a $z$-score approach assuming that the data follow a Rician distribution~\citep{lemaitre2016normalization}.
-In \ac{dce}-\ac{mri}, there is additional factors characterizing such variations.
+In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data, although it can be applied to any \ac{dce}-\ac{mri} sequences.
+The aim of the method is to reduce the intra-patient variations, occuring during the acquisition process.
+In \ac{t2w}-\ac{mri}, these variations imply that the intensity \ac{pdf} of the prostate region is shifted as well as wider or narrower, from a patient to another.
+Therefore, these variations can be corrected using a $z$-score approach, assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
+
+In \ac{dce}-\ac{mri}, the inter-patient variations are more complex due to the over time acquisition.
 These variations can be highlighted by observing the evolution of the intensity \ac{pdf} of the \ac{dce}-\ac{mri} over time, as shown in the heatmap in Fig.\,\ref{fig:heatmap}.
-These variations are:
+Therefore, these variations are:
 (i) an offset of the peak value before pre-contrast,

### 2016-08-23 02_methods/methods.tex
Update the normalization roughly

@@
 
-Before to standardize each sequence, the first step of the normalization is to cancel the intensity shift which is specific for each patient.
-The intensity \ac{pdf} do not follow either a Rician or Gaussian distribution over time.
-Therefore, the mean cannot be used as a potential estimate for the offset.
-Additionally, this offset should be characterized by a smooth transition over time.
-This problem can be solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{fig:heatmap}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
+Before to standardize each sequence, the first step of the normalization is to cancel the intensity specific at each patient, occurring due to the media injection.
+In \ac{dce}-\ac{mri}, the intensity \ac{pdf} do not always follow either a Rician or a Gaussian distribution over time.
+Therefore, the mean of these distributions cannot be used as a potential estimate for this offset.
+Additionally, this offset should be characterized by a smooth transition between series over time.
+Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{fig:heatmap}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
 Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar of the heatmap as a node and connecting each pair of bars by an edge.
@@
   w_{ij} = \begin{cases}
-    \alpha \exp(1 - \frac{H(i)}{\max(H)})       & \text{if } x_j = x_i + 1 \text{ and } y_j = y_i \\
-    (1 - \alpha) \exp(1 - \frac{H(i)}{\max(H)}) & \text{if } x_j = x_i \text{ and } y_j = y_i + 1 \\
-    0                                           & \text{otherwise}
-  \end{cases} ,
+    \alpha \exp(1 - \frac{H(i)}{\max(H)})       & \text{if } x_j = x_i + 1 \text{ and } y_j = y_i, \\
+    (1 - \alpha) \exp(1 - \frac{H(i)}{\max(H)}) & \text{if } x_j = x_i \text{ and } y_j = y_i + 1, \\
+    0                                           & \text{otherwise},
+  \end{cases}
   \label{eq:weight}
@@
 
-Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra algorithm.
+Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra's algorithm.
 The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
@@
 An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.
-Finally, each sequence is shifted using this offset.
+Finally, for each \ac{dce}-\ac{mri} serie, the intensities are shifted by this offset.
 
@@
 The next variations to correct are the time offset and the data dispersion.
-By computing the \ac{rmse} for each \ac{dce}-\ac{mri}, one can observed these two variations as shown in Fig.\,\ref{fig:rmse}.
+By computing the \ac{rmse} of the intensities for each \ac{dce}-\ac{mri} serie, one can observed these two variations as shown in Fig.\,\ref{fig:rmse}.
 Therefore, to correct these variations, we propose to register each patient \ac{rmse} to a mean model which corresponds to the mean of all patients \ac{rmse}.
@@
 Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
-Once all these parameters have been inferred, the data can be shifted as well as scale.
+Once all these parameters have been inferred, the data can be shifted as well as scaled.
 

### 2016-08-24 01_introduction/introduction.tex
Update the introduction

@@
 In \ac{dce}-\ac{mri}, a contrast media is injected intravenously and a set of images is acquired over time.
-Consequently, each voxel in an image corresponds to a dynamic signal is related to the vascular properties of the tissue.
+Consequently, each voxel in an image corresponds to a dynamic signal which is related to both contrast agent concentration and the vascular properties of the tissue.
+Therefore, changes of the enhanced signal allows to discriminate healthy from \ac{cap} tissues.
 In fact, these properties are automatically extracted using quantitative or semi-quantitative approaches~\citep{lemaitre2015computer}.
 
-The former group of approaches uses pharmacokinetic modelling based on a bicompartment model, namely Brix~\citep{brix1991pharmacokinetic} and Tofts~\citep{tofts1995quantitative} models.
+\emph{Quantitative} approaches uses pharmacokinetic modelling based on a bicompartment model, namely Brix~\citep{brix1991pharmacokinetic} and Tofts~\citep{tofts1995quantitative} models.
 The parameters of the Brix model are inferred assuming a linear relationship between the media concentration and the \ac{mri} signal intensity.
@@
 
-The latter group of approaches are rather mathematical than pharmacokinetic modelling~\citep{huisman2001accurate,gliozzi2011phenomenological}.
+\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling~\citep{huisman2001accurate,gliozzi2011phenomenological}.
 These methods offer the advantages to not require any knowledge about the \ac{mri} sequence nor any conversion from signal intensity to concentration.
@@
 Nevertheless, all presented methods suffer from two major drawbacks:
-(i) the inter-patient variability of the data lead to a variation of the parameters estimated and subsequently to poor classification performance while designing \ac{cad} systems, and
-(ii) only few parameters are used to characterize the dynamic signal implying that some information are discarded.
+(i) inter-patient variability and (ii) loss of information.
+The inter-patient variability is mainly due to the acquisition process and consequently lead to generalization issue while applying machine learning algorithm.
+All previous methods extract few discriminative parameters to describe the \ac{dce}-\ac{mri} signal which might lead to a loss of information.
+%(i) the inter-patient variability of the data lead to a variation of the parameters estimated and subsequently to poor classification performance while designing \ac{cad} systems, and
+%(ii) only few parameters are used to characterize the dynamic signal implying that some information are discarded.
 
 In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduce the inter-patient variability of the data.
-Furthermore, we show that using the full normalized \ac{dce}-\ac{mri} signal lead to the best classification performance.
+The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
+Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.
 
-The paper is organized as follows: Section~\ref{sec:methods} outlines our normalization strategy (Section~\ref{sec:norm}) as well as specificity regarding the state-of-the-art methods used for comparison (Section~\ref{sec:stateart}).
-The dataset, experiments, and results are reported in Section~\ref{sec:experiments} while discussed in Section~\ref{sec:discussions} followed by a concluding section.
+{\color{red}
+The paper is organized as follows:
+Section~\ref{sec:norm} presents into details our normalization strategy for \ac{dce}-\ac{mri} data.
+Quantitative and semi-quantitative methods are summarized in Sect.\,\ref{sec:stateart} with insights about their implementations.
+Section~\ref{sec:materials} gives information about the dataset used and provided source code.
+Experiments and results to answer the previous stated challenges are reported in Sect.\,\ref{sec:experiments} while discussed in Sect.\,\ref{sec:discussions}, followed by a concluding section.
+%Section~\ref{sec:methods} outlines our normalization strategy (Section~\ref{sec:norm}) as well as specificity regarding the state-of-the-art methods used for comparison (Section~\ref{sec:stateart}).
+%The dataset, experiments, and results are reported in Section~\ref{sec:experiments} while discussed in Section~\ref{sec:discussions} followed by a concluding section.
+}
 

### 2016-08-24 02_methods/methods.tex
Update the introduction

@@
-\section{Materials and methods}\label{sec:methods}
-
-\subsection{Data}\label{sec:data}
-
-The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
-The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
-Aside of the \ac{mri} examination, these patients also have underwent a guided-biopsy.
-The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
-Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
-An experienced radiologist has segmented the prostate organ --- on \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
-
-A \SI{3}{\mm} slice fat-suppressed \ac{t2w} fast spin-echo sequence (\ac{tr}/\ac{te}/\ac{etl}: \SI{3400}{\ms}/\SI{85}{\ms}/13) is used to acquire images in sagittal and oblique coronal planes, the latter planes being orientated perpendicular or parallel to the prostate \ac{pz} – rectal wall axis.
-Three-dimensional \ac{t2w} fast spin-echo (\ac{tr}/\ac{te}/\ac{etl}: \SI{3600}{\ms}/\SI{143}{\ms}/109, slice thickness: \SI{1.25}{\mm}) images are then acquired in an oblique axial plane.
-The nominal matrix and \ac{fov} of the 3D \ac{t2w} fast spin-echo images are $320 \times 256$ and $280 \times 240$ mm\textsuperscript{2}, respectively, thereby affording sub-millimetric pixel resolution within the imaging plane.
-
-\ac{dce}-\ac{mri} are performed using a fat suppressed 3D T1 VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
-A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
-
-These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using linear interpolation.
-The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
-Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
-The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
-
-\subsection{Implementation}
-
-The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
-The data used for this work are also publicly available\footnote{\url{http://kaggle.com}}.
+\section{Methods}\label{sec:method}
 
@@
 In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data, although it can be applied to any \ac{dce}-\ac{mri} sequences.
-The aim of the method is to reduce the intra-patient variations, occuring during the acquisition process.
+The aim of the method is to reduce the intra-patient variations, occurring during the acquisition process.
 In \ac{t2w}-\ac{mri}, these variations imply that the intensity \ac{pdf} of the prostate region is shifted as well as wider or narrower, from a patient to another.
@@
 Therefore, these variations are:
-(i) an offset of the peak value before pre-contrast,
-(ii) a time offset depending of the contrast injection, and
-(iii) a global scale factor related to the enhancement.
+(i) an intensity offset of the \ac{pdf} peak at pre-contrast,
+(ii) a time offset depending of the contrast agent arrival, and
+(iii) a change of scale related to the signal enhancement.
 Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.

### 2016-08-24 03_experiments/experiments.tex
Update the introduction

@@
+\section{Materials}\label{sec:materials}
+
+\subsection{Data}\label{sec:data}
+
+The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
+The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
+Aside of the \ac{mri} examination, these patients also have underwent a guided-biopsy.
+The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
+Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
+An experienced radiologist has segmented the prostate organ --- on \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
+
+A \SI{3}{\mm} slice fat-suppressed \ac{t2w} fast spin-echo sequence (\ac{tr}/\ac{te}/\ac{etl}: \SI{3400}{\ms}/\SI{85}{\ms}/13) is used to acquire images in sagittal and oblique coronal planes, the latter planes being orientated perpendicular or parallel to the prostate \ac{pz} – rectal wall axis.
+Three-dimensional \ac{t2w} fast spin-echo (\ac{tr}/\ac{te}/\ac{etl}: \SI{3600}{\ms}/\SI{143}{\ms}/109, slice thickness: \SI{1.25}{\mm}) images are then acquired in an oblique axial plane.
+The nominal matrix and \ac{fov} of the 3D \ac{t2w} fast spin-echo images are $320 \times 256$ and $280 \times 240$ mm\textsuperscript{2}, respectively, thereby affording sub-millimetric pixel resolution within the imaging plane.
+
+\ac{dce}-\ac{mri} are performed using a fat suppressed 3D T$_1$ VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
+A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
+
+These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using linear interpolation.
+The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
+Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
+The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
+
+\subsection{Implementation}
+
+The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
+The data used for this work are also publicly available\footnote{\url{http://kaggle.com}}.
+
 \section{Experiments and results}\label{sec:experiments}

### 2016-08-24 02_methods/methods.tex
Finish to describe the results

@@
   \centering
+  \includegraphics[width=0.7\linewidth]{02_methods/figures/t2w.pdf}
+  \caption{Illustration of the inter-patient variations in 17 different patients, using the \acs*{pdf} representation.}
+  \label{fig:t2w}
+\end{figure}
+
+In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data to reduce intra-patient variations, although it can be applied to any \ac{dce}-\ac{mri} sequences.
+In \ac{t2w}-\ac{mri}, these variations are characterized by a shift and a scaling of the intensities as illustrated by the intensity \ac{pdf} in Fig.\,\ref{fig:t2w}.
+Therefore, these variations can be corrected using a $z$-score approach, assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
+
+\begin{figure}
+  \centering
   \hspace*{\fill}
-  \subfigure[Patient 1]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1.pdf}} \hfill
-  \subfigure[Patient 2]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}}
+  \subfigure[]{\label{subfig:pathist}\includegraphics[width=.35\textwidth]{02_methods/figures/IMG_20160824_122328.jpg}} \hfill
+  \subfigure[]{\label{subfig:heatmaprep}\includegraphics[width=.5\textwidth]{02_methods/figures/pat2.pdf}}
+  \hspace*{\fill}
+  \\
+  \hspace*{\fill}
+  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat1.pdf}} \hfill
+  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}} \hfill
+  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}}
   \hspace*{\fill}
@@
 
-In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data, although it can be applied to any \ac{dce}-\ac{mri} sequences.
-The aim of the method is to reduce the intra-patient variations, occurring during the acquisition process.
-In \ac{t2w}-\ac{mri}, these variations imply that the intensity \ac{pdf} of the prostate region is shifted as well as wider or narrower, from a patient to another.
-Therefore, these variations can be corrected using a $z$-score approach, assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
-
-In \ac{dce}-\ac{mri}, the inter-patient variations are more complex due to the over time acquisition.
-These variations can be highlighted by observing the evolution of the intensity \ac{pdf} of the \ac{dce}-\ac{mri} over time, as shown in the heatmap in Fig.\,\ref{fig:heatmap}.
-Therefore, these variations are:
-(i) an intensity offset of the \ac{pdf} peak at pre-contrast,
-(ii) a time offset depending of the contrast agent arrival, and
-(iii) a change of scale related to the signal enhancement.
+In \ac{dce}-\ac{mri}, the intensity \ac{pdf} does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathist}.
+Indeed, the inter-patient variations are more complex due to the temporal acquisition.
+A better representation to observed these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time (see Fig.\,\ref{subfig:pathist}) using a heatmap representation as shown in Fig.\,\ref{subfig:heatmaprep}.
+Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
+(i) an intensity offset $\Delta_i$ of the \ac{pdf} peak at pre-contrast,
+(ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
+(iii) a change of scale $\sigma_i$ related to the signal enhancement.
 Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.
@@
 Before to standardize each sequence, the first step of the normalization is to cancel the intensity specific at each patient, occurring due to the media injection.
-In \ac{dce}-\ac{mri}, the intensity \ac{pdf} do not always follow either a Rician or a Gaussian distribution over time.
+As previously mentioned, the intensity \ac{pdf} do not always follow either a Rician or a Gaussian distribution over time, in \ac{dce}-\ac{mri}.
 Therefore, the mean of these distributions cannot be used as a potential estimate for this offset.
 Additionally, this offset should be characterized by a smooth transition between series over time.
-Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{fig:heatmap}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
+Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{subfig:heatmaprep}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
 Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar of the heatmap as a node and connecting each pair of bars by an edge.
@@
 
+As stated in the introduction, one of our main challenge is to demonstrate the benefit of using our normalization method prior to extract parameters using quantitative and semi-quantitative methods.
+In this section, we summarize the different methods which have been used for the quantification of \ac{dce}-\ac{mri} for \ac{cap} detection~\citep{lemaitre2015computer}.
+Furthermore, we would like to emphasize the following additional contributions: (i) a novel automatic \ac{aif} estimation algorithm based on clustering and (ii) a simplified semi-quantitative method using constrained optimization.
+
 \subsubsection{Brix and Hoffmann models}\label{sec:brixhoffmann}
@@
 \noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at time $t$ and the average pre-contrast \ac{mri} signal intensity, respectively; $A$, $k_{el}$, and $k_{ep}$ are a constant proportional to the transfer constant, the diffusion rate constant, and the rate constant, respectively.
-Additionally, during the injection time $0 \leq t \leq \tau$, $t' = t$ and afterwards while $t > \tau$, $t' = \tau$.
+Additionally, $t'$ is set such that $0 \leq t \leq \tau$, $t' = t$ and afterwards while $t > \tau$, $t' = \tau$.
 
-Following this model, \citeauthor{hoffmann1995pharmacokinetic} propose the following similar model as expressed in Eq.\,\eqref{eq:hoffmann}:
+\citeauthor{hoffmann1995pharmacokinetic} propose a similar model as expressed in Eq.\,\eqref{eq:hoffmann}, which derive from the Brix model:
 
 \begin{equation}
+  \small
   s_n(t) = 1 + \frac{A}{\tau} \left[ \frac{k_{ep} \left( \exp(k_{el} t') - 1 \right)}{k_{el}(k_{ep} - k_{el})} \exp(- k_{el} t) - \frac{\exp(k_{ep} t') - 1}{(k_{ep} - k_{el})} \exp(- k_{ep} t) \right].
@@
 
-The parameters are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
+The parameters $A$, $k_{el}$, and $k_{ep}$ are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
 
@@
     (iii) a blob detector is used and large enough regions are kept, and
-    (iv) circular and cylindricality are used to reject the last false positive.
+    (iv) circular and cylindricality criteria are used to reject the last false positive.
     \citeauthor{zhu2011automated} propose an iterative method selecting voxels which best fit a gamma variate function~\citep{zhu2011automated}.
@@
       $T_{10}$ can be estimated from the acquisition of a T$_1$ map.
-      However, this modality was not part of the clinical trial in this research and the value of $T_{10}$ was fixed to \SI{1600}{\ms} for both blood and prostate as stated in the literature~\citep{fennessy2015quantitative,de2004mr,carr2011magnetic}.
+      However, this modality is not part of the clinical trial in this research and the value of $T_{10}$ is fixed to \SI{1600}{\ms} for both blood and prostate, in accordance with the values found in the literature~\citep{fennessy2015quantitative,de2004mr,carr2011magnetic}.
       \item[Estimation of population-based \ac{aif}] While estimating the pharmacokinetic parameters from Tofts model, the \ac{aif} concentration $C_p(t)$ can be computed either from the patient or a population.

### 2016-08-24 03_experiments/experiments.tex
Finish to describe the results

@@
 
-\ac{dce}-\ac{mri} are performed using a fat suppressed 3D T$_1$ VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
+\ac{dce}-\ac{mri} is performed using a fat suppressed 3D T$_1$ VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
 A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
 
-These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using linear interpolation.
+These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using a linear interpolation.
 The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
@@
 
-The first experiment consists in comparing the classification performance using each individual parameter for the different models, to assess the potential benefit of the normalization method.
-Therefore, each feature is individually classified using a Gaussian \ac{nb} classifier in a \ac{lopo} fashion.
-{\color{red}\ac{nb} is used due to its simplicity and it enables to check the fitted parameters for interpretation.}
-The results are summarized in Table~\ref{tab:resfeats}.
-It can be noted that in the majority of the cases, normalizing the data improve the classification performance in terms of \ac{auc}.
-Only the \ac{pun} model does not follow this tendency {\color{red} which might due to the fact that the function do not fit the data as good as the other model - WE WILL NEED SOME RMSE FOR EACH FITTING IF WE SAY SO.}.
-
-{\color{red}It could be interesting to check the value of the mean and std of the \ac{nb}. We could compute a ratio which refer to the class separability.}
-
 \begin{table}
@@
 
+This experiment consists in assessing the benefit of normalizing the \ac{dce}-\ac{mri}, prior to classify each individual parameter for each model.
+Therefore, a Gaussian \ac{nb} classifier is used in conjunction with a \ac{lopo}.
+The results are summarized in Table~\ref{tab:resfeats}.
+In general, data normalization leads to better classification performance while extracting pharmacokinetic related parameters.
+Only the \ac{pun} model does not follow this tendency.
+{\color{red} Find out why!!!}
+
 \subsection{Classification by combining the parameters for each model}
-
-Usually, the parameters are combined to form a multi-dimensional prior to classify the data.
-Therefore, for each model, all parameters are combined and classified using a \ac{rf} classifier in a \ac{lopo} fashion.
-The use of \ac{rf} is motivated since that it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer}.
-The results are summarized by making \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
-It can be noted that in all the cases the normalization of the data improve the classification performance.
 
@@
 \end{figure}
+
+In previous proposed \ac{cad} systems, the pharmacokinetic of a single model are combined.
+Therefore, for each model, all parameters are combined and classified using a \ac{rf} classifier in a \ac{lopo} fashion.
+The use of \ac{rf} is motivated since that it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer}.
+Results are summarized by performing a \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
+Independently to the quantification model, the data normalization improves the\ac{auc} and classification performance.
 
@@
 
-The quantification methods are extracting a minimal set of parameters which should characterized the enhancement \ac{dce}-\ac{mri} curves.
-However, this extraction could discard some information of the signal.
-This experiment attends to use the whole \ac{dce}-\ac{mri} signal to perform the classification.
-Therefore, the enhanced signal is classified using a \ac{rf} classifier in a \ac{lopo} fashion.
-The \ac{roc} analysis and \ac{auc} are reported in Fig.\,\ref{fig:rfnormdcesignal}.
-It can be note that the worst performance are achieved while data without normalization.
-However, normalizing the data, this classification strategy lead the best classification performance, outperforming any quantification method, showing the importance of our normalization algorithm.
-
 \begin{figure}
@@
 
+As stated in the introduction, the quantification methods are extracting a set of parameters characterizing the enhancement \ac{dce}-\ac{mri} signal.
+However, this extraction could lead to a loss of information.
+This experiment is performed to assess if making use of the whole \ac{dce}-\ac{mri} signal instead of the just the pharmacokinetic parameters can improve the classification performance.
+Therefore, each enhanced \ac{dce}-\ac{mri} signal, normalized and un-normalized, is classified using a \ac{rf} classifier in a \ac{lopo} fashion.
+The \ac{roc} analysis and \ac{auc} are reported in Fig.\,\ref{fig:rfnormdcesignal}.
+It can be noted that the worst performance are achieved while classifying raw data without normalization.
+However, data normalization in conjunction with the use of the whole \ac{dce}-\ac{mri} signal is the strategy which outperforms all others.
+
 %%% Local Variables: 

### 2016-08-24 03_experiments/experiments.tex
Finish the first draft

@@
 
-\begin{table}
+\begin{table*}
   \caption{\acs*{auc} for each individual pharmacokinetic parameter using a \acs*{nb} classifier.}
   \centering
-  \begin{tabular}{l c c}
+  \begin{tabular}{l c c c}
     \toprule
-    \textbf{Features} & Un-normalized data & Normalized data \\
+    \textbf{Features} & Un-normalized data & Normalized data & Gain/Loss \\
     \midrule
-    \textbf{Brix model} & & \\
-    \quad $A$         & 0.62 & 0.67 \\
-    \quad $k_{el}$    & 0.52 & 0.61 \\
-    \quad $k_{ep}$    & 0.52 & 0.58 \\
-    \textbf{Hoffmann model} & & \\
-    \quad $A$         & 0.50 & 0.56 \\
-    \quad $k_{el}$    & 0.53 & 0.64 \\
-    \quad $k_{ep}$    & 0.50 & 0.66 \\
-    \textbf{Tofts model with population \ac{aif}} & & \\
-    \quad $K_{trans}$ & 0.62 & 0.65 \\
-    \quad $v_{e}$     & 0.50 & 0.52 \\
-    \quad $v_{p}$     & 0.63 & 0.53 \\
-    \textbf{Tofts model with patient \ac{aif}} & & \\
-    \quad $K_{trans}$ & 0.66 & 0.65 \\
-    \quad $v_{e}$     & 0.50 & 0.52 \\
-    \quad $v_{p}$     & 0.37 & 0.65 \\
-    \textbf{\ac{pun} model} & & \\
-    \quad $a_0$       & 0.53 & 0.51 \\
-    \quad $r$         & 0.59 & 0.55 \\
-    \quad $\beta$     & 0.56 & 0.44 \\
-    \textbf{Semi-quantitative analysis} & & \\
-    \quad wash-in     & 0.64 & 0.51 \\
-    \quad wash-out    & 0.50 & 0.66 \\
-    \quad IAUC        & 0.61 & 0.64 \\
-    \quad $\tau$      & 0.57 & 0.61 \\
-    \quad $S_M - S_0$ & 0.63 & 0.64 \\
+    \textbf{Brix model} & & & \\
+    \quad $A$         & 0.62 & 0.67 & + 0.05 \\
+    \quad $k_{el}$    & 0.52 & 0.61 & + 0.09 \\
+    \quad $k_{ep}$    & 0.52 & 0.58 & + 0.06 \\
+    \textbf{Hoffmann model} & & & \\
+    \quad $A$         & 0.50 & 0.56 & + 0.06 \\
+    \quad $k_{el}$    & 0.53 & 0.64 & + 0.11 \\
+    \quad $k_{ep}$    & 0.50 & 0.66 & + 0.16 \\
+    \textbf{Tofts model with population \ac{aif}} & & & \\
+    \quad $K_{trans}$ & 0.62 & 0.65 & + 0.03 \\
+    \quad $v_{e}$     & 0.50 & 0.52 & + 0.02 \\
+    \quad $v_{p}$     & 0.63 & 0.53 & - 0.10 \\
+    \textbf{Tofts model with patient \ac{aif}} & & & \\
+    \quad $K_{trans}$ & 0.66 & 0.65 & - 0.01 \\
+    \quad $v_{e}$     & 0.50 & 0.52 & + 0.02 \\
+    \quad $v_{p}$     & 0.37 & 0.65 & + 0.18 \\
+    \textbf{\ac{pun} model} & & & \\
+    \quad $a_0$       & 0.53 & 0.51 & - 0.02 \\
+    \quad $r$         & 0.59 & 0.55 & - 0.04 \\
+    \quad $\beta$     & 0.56 & 0.44 & - 0.12 \\
+    \textbf{Semi-quantitative analysis} & & & \\
+    \quad wash-in     & 0.64 & 0.51 & - 0.15 \\
+    \quad wash-out    & 0.50 & 0.66 & + 0.16 \\
+    \quad IAUC        & 0.61 & 0.64 & + 0.03 \\
+    \quad $\tau$      & 0.57 & 0.61 & + 0.04 \\
+    \quad $S_M - S_0$ & 0.63 & 0.64 & + 0.01 \\
     \bottomrule
@@
   \label{tab:resfeats}
-\end{table}
+\end{table*}
 
@@
 The results are summarized in Table~\ref{tab:resfeats}.
-In general, data normalization leads to better classification performance while extracting pharmacokinetic related parameters.
+In general, data normalization leads to better classification performance (i.e., + 4\%) while extracting pharmacokinetic related parameters.
 Only the \ac{pun} model does not follow this tendency.
-{\color{red} Find out why!!!}
+{\color{red} Find out why!!! I am computing the R2 coefficient to check the fit of data.}
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \label{fig:normpharmarf}
-\end{figure}
+\end{figure*}
 
@@
 Independently to the quantification model, the data normalization improves the\ac{auc} and classification performance.
+An increase of the \ac{auc} ranging from 1\% to 12\% is noticeable.
 
@@
 The \ac{roc} analysis and \ac{auc} are reported in Fig.\,\ref{fig:rfnormdcesignal}.
-It can be noted that the worst performance are achieved while classifying raw data without normalization.
-However, data normalization in conjunction with the use of the whole \ac{dce}-\ac{mri} signal is the strategy which outperforms all others.
+Classification without normalization lead to the worst performance, with an \ac{auc} of 0.57.
+However, data normalization in conjunction with the use of the whole \ac{dce}-\ac{mri} signal is the strategy which outperforms all others, with an \ac{auc} of 0.67.
 

### 2016-08-24 04_discussions/discussions.tex
Finish the first draft

--- 2016-08-08 01_introduction/introduction.tex
@@
-\section{Introduction}
+\section{Discussions}\label{sec:discussions}
+
+The experiments conducted in the previous section can give rise to several discussions.
+In Tofts quantification, two different approaches have been used to infer the pharmacokinetic parameters: using a population-based or a patient-based \ac{aif}.
+The population-based \ac{aif} approach leads to better classification performance.
+However, there is two shortcomings to take into account while advancing this fact:
+(i) T$_10$ parameter has been fixed and not computed from a T$_1$ map and
+(ii) the population-based \ac{aif} has been estimated from a cohort of only 17 patients.
+These two limitations have to be considered while advancing that population-based \ac{aif} modelling is outperforming patient-based \ac{aif} modelling.
+
+The best classification performance is reached by normalizing the \ac{dce}-\ac{mri} data and use the whole enhanced signal as feature, emphasizing the fact that a loss of information while extracting quantitative parameters.
+However, this strategy suffers from one drawback: the training time of the \ac{rf} classifier increases since that from 3 to 5 features, the feature space become a 40 dimensions space.
 

### 2016-08-24 05_conclusions/conclusions.tex
Finish the first draft

--- 2016-08-08 01_introduction/introduction.tex
@@
-\section{Introduction}
+\section{Conclusions and future works}\label{sec:conclusions}
+
+In this work, we presented a new method for normalizing/standardizing \ac{dce}-\ac{mri} data.
+This method aimed at reducing the inter-patient variations occurring during data acquisition.
+A graph-based approach was used to correct intensity offset in conjunction with a model-based correction to reduce time offset as well as intensity scaling.
+We show the benefit of our normalization method prior to extract quantitative and semi-quantitative features, with a significant improvement of the classification performance.
+Nevertheless, we also show that using the whole normalized \ac{dce}-\ac{mri} signal outperforms all quantitative approach.
+
+As avenues for future research, this normalization has to be part of a \ac{mpmri} \ac{cad} system in which \ac{dce}-\ac{mri} modality needs to be combined with other complementary modalities.
 

### 2016-08-25 02_methods/methods.tex
Finish the first draft
Added the missing figure

@@
 
-\begin{figure}
+\begin{figure*}
   \centering
   \hspace*{\fill}
-  \subfigure[]{\label{subfig:pathist}\includegraphics[width=.35\textwidth]{02_methods/figures/IMG_20160824_122328.jpg}} \hfill
-  \subfigure[]{\label{subfig:heatmaprep}\includegraphics[width=.5\textwidth]{02_methods/figures/pat2.pdf}}
+  \subfigure[]{\label{subfig:pathist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
   \hspace*{\fill}
@@
   \label{fig:heatmap}
-\end{figure}
+\end{figure*}
 
@@
 Indeed, the inter-patient variations are more complex due to the temporal acquisition.
-A better representation to observed these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time (see Fig.\,\ref{subfig:pathist}) using a heatmap representation as shown in Fig.\,\ref{subfig:heatmaprep}.
+A better representation to observed these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
 Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
@@
   \label{fig:curveal}
-\end{figure}
+\end{figure*}
 
@@
   \label{fig:aif}
-\end{figure}
+\end{figure*}
 

### 2016-08-26 01_introduction/introduction.tex
Address robert and fab changes

@@
 In the contrary, Tofts model requires a conversion from \ac{mri} signal intensity to concentration, which become a non-linear relationship using specific equation of \ac{mri} sequences (e.g., FLASH sequence).
-Tofts modelling suffers, however, from an higher complexity~\citep{gliozzi2011phenomenological}.
+Tofts modelling suffers, however, from a higher complexity~\citep{gliozzi2011phenomenological}.
 Indeed, the conversion using the non-linear approach requires to acquire a T$_1$ map which is not always possible during clinical examination.
@@
 
-\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling~\citep{huisman2001accurate,gliozzi2011phenomenological}.
+\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling since that no pharmacokinetic assumption regarding the relation between the \ac{mri} signal and the contrast agent~\citep{huisman2001accurate,gliozzi2011phenomenological}.
 These methods offer the advantages to not require any knowledge about the \ac{mri} sequence nor any conversion from signal intensity to concentration.
-However, the heuristic approach propose by \citeauthor{huisman2001accurate} requires an estimate regarding the noise standard deviation of the signal as well as manual tuning.
+However, the heuristic approach proposed by \citeauthor{huisman2001accurate} requires an initial estimate of the noise standard deviation of the signal as well as manual tuning.
 
@@
 (i) inter-patient variability and (ii) loss of information.
-The inter-patient variability is mainly due to the acquisition process and consequently lead to generalization issue while applying machine learning algorithm.
+The inter-patient variability is mainly due to the acquisition process and consequently leads to generalization issue while applying machine learning algorithm.
 All previous methods extract few discriminative parameters to describe the \ac{dce}-\ac{mri} signal which might lead to a loss of information.
@@
 
-In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduce the inter-patient variability of the data.
-The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
-Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.
+In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
+{\color{red}The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
+Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.}
 
-{\color{red}
 The paper is organized as follows:
@@
 %The dataset, experiments, and results are reported in Section~\ref{sec:experiments} while discussed in Section~\ref{sec:discussions} followed by a concluding section.
-}
 

### 2016-08-26 02_methods/methods.tex
Address robert and fab changes

@@
 
-In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data to reduce intra-patient variations, although it can be applied to any \ac{dce}-\ac{mri} sequences.
+In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data to reduce inter-patient variations, although it can be applied to any \ac{dce}-\ac{mri} sequences.
 In \ac{t2w}-\ac{mri}, these variations are characterized by a shift and a scaling of the intensities as illustrated by the intensity \ac{pdf} in Fig.\,\ref{fig:t2w}.
@@
   \hspace*{\fill}
-  \subfigure[]{\label{subfig:pathist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
+  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
   \hspace*{\fill}
@@
   \hspace*{\fill}
-  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat1.pdf}} \hfill
-  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}} \hfill
-  \subfigure{\includegraphics[width=.2\textwidth]{02_methods/figures/pat2.pdf}}
+  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
+  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}} \hfill
   \hspace*{\fill}
-  \caption{Illustration of the variations of the intensity \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
+  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\sigma_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
   \label{fig:heatmap}
@@
 
-In \ac{dce}-\ac{mri}, the intensity \ac{pdf} does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathist}.
+In \ac{dce}-\ac{mri}, the intensity \ac{pdf} of prostate gland does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathist}.
 Indeed, the inter-patient variations are more complex due to the temporal acquisition.
-A better representation to observed these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
+A better representation to observe these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
 Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
@@
 
-\subsubsection{Graph-based offset correction for each \ac{dce}-\ac{mri} sequence}
+\subsubsection{Graph-based intensity offset correction}
 
@@
 Before to standardize each sequence, the first step of the normalization is to cancel the intensity specific at each patient, occurring due to the media injection.
-As previously mentioned, the intensity \ac{pdf} do not always follow either a Rician or a Gaussian distribution over time, in \ac{dce}-\ac{mri}.
-Therefore, the mean of these distributions cannot be used as a potential estimate for this offset.
-Additionally, this offset should be characterized by a smooth transition between series over time.
-Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{subfig:heatmaprep}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
-Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar of the heatmap as a node and connecting each pair of bars by an edge.
+As previously mentioned, the intensity \ac{pdf} does not always follow either a Rician or a Gaussian distribution over time, in \ac{dce}-\ac{mri}.
+Therefore, the mean of these distributions cannot be used as a potential estimate for these offsets.
+Additionally, these offsets should be characterized by a smooth transition between series over time.
+Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{subfig:heatmaprep}, the offsets correspond to the boundary splitting the heatmap in two partitions such that they are as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
+Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar--- i.e., the probability for a given time and pixel intensity---of the heatmap as a node and connecting each pair of bars by an edge.
 The edge weight $w_{ij}$ between two nodes $i$ and $j$ corresponding to two pixels at position $(x_i, y_i)$ and $(x_j, y_j)$, respectively, is defined as in Eq.\,\eqref{eq:weight}:
@@
 
-Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra's algorithm.
+Therefore, these offsets are estimated by finding the shortest-path to cross the graph using Dijkstra's algorithm.
 The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
-To ensure a robust estimation of the offset, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
-The procedure is stopped once that the offset found do not change.
+To ensure a robust estimation of these offsets, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
+The procedure is stopped once that the offset found does not change.
 In general, this process is not repeated more than 3 iterations.
-An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.
-Finally, for each \ac{dce}-\ac{mri} serie, the intensities are shifted by this offset.
+Figure~\ref{fig:estimator} illustrates the final estimation of the offsets (i.e., red landmark) found for each \ac{dce}-\ac{mri} serie.
+Therefore, each intensity offset is subtracted for each \ac{dce}-\ac{mri}.
 
@@
 The next variations to correct are the time offset and the data dispersion.
-By computing the \ac{rmse} of the intensities for each \ac{dce}-\ac{mri} serie, one can observed these two variations as shown in Fig.\,\ref{fig:rmse}.
+By computing the \ac{rmse} of the intensities for each \ac{dce}-\ac{mri} serie, one can observe these two variations as shown in Fig.\,\ref{fig:rmse}.
 Therefore, to correct these variations, we propose to register each patient \ac{rmse} to a mean model which corresponds to the mean of all patients \ac{rmse}.
@@
 
-\noindent where $\alpha$ and $\tau$ are the two parameters handling the time offset and global scale, respectively, $f(\cdot)$ is the \ac{rmse} function.
+\noindent where $\alpha$ and $\tau$ are the two parameters handling the time offset and global scale, respectively, $f(\cdot)$ is the \ac{rmse} function define as:
+
+\begin{equation}
+  f(t) = \sqrt{ \left( \frac{\sum_{n=0}^{N} x(t)_{n}^2}{N}  \right) },
+  \label{eq:rmsd}
+\end{equation}
+
+\noindent where $x(t)_n$ is the shifted intensity of a sample from a specific \ac{dce}-\ac{mri} serie at time $t$ from a total number of $N$ samples.
 
@@
 Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
-Once all these parameters have been inferred, the data can be shifted as well as scaled.
+Once all these parameters have been inferred, the data can be shifted as well as scale.
 
@@
 
-\noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at time $t$ and the average pre-contrast \ac{mri} signal intensity, respectively; $A$, $k_{el}$, and $k_{ep}$ are a constant proportional to the transfer constant, the diffusion rate constant, and the rate constant, respectively.
+\noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at time $t$ and the average pre-contrast \ac{mri} signal intensity, respectively; $A$, $k_{el}$, and $k_{ep}$ are the constant proportional to the transfer constant, the diffusion rate constant, and the rate constant, respectively.
 Additionally, $t'$ is set such that $0 \leq t \leq \tau$, $t' = t$ and afterwards while $t > \tau$, $t' = \tau$.
 
-\citeauthor{hoffmann1995pharmacokinetic} propose a similar model as expressed in Eq.\,\eqref{eq:hoffmann}, which derive from the Brix model:
+\citeauthor{hoffmann1995pharmacokinetic} proposed a similar model as expressed in Eq.\,\eqref{eq:hoffmann}, which derive from the Brix model:
 
@@
   \small
-  s_n(t) = 1 + \frac{A}{\tau} \left[ \frac{k_{ep} \left( \exp(k_{el} t') - 1 \right)}{k_{el}(k_{ep} - k_{el})} \exp(- k_{el} t) - \frac{\exp(k_{ep} t') - 1}{(k_{ep} - k_{el})} \exp(- k_{ep} t) \right].
+  s_n(t) = 1 + \frac{A}{\tau} \left[ \frac{k_{ep} \left( \exp(k_{el} t') - 1 \right)}{k_{el}(k_{ep} - k_{el})} \exp(- k_{el} t) - \frac{\exp(k_{ep} t') - 1}{(k_{ep} - k_{el})} \exp(- k_{ep} t) \right] ,
   \label{eq:hoffmann}
 \end{equation}
+
+\noindent in which the constant $A$ is redefined by isolating the parameter $\tau$.
 
@@
     Few methods have been proposed to address the automated extraction of \ac{aif} signal.
-    \citeauthor{chen2008automatic} filter successively the possible candidates~\citep{chen2008automatic}:
-    (i) dynamic signals with small peak are rejecting by thresholding,
-    (ii) voxels with a small wash-in are rejected by thresholding,
-    (iii) a blob detector is used and large enough regions are kept, and
-    (iv) circular and cylindricality criteria are used to reject the last false positive.
-    \citeauthor{zhu2011automated} propose an iterative method selecting voxels which best fit a gamma variate function~\citep{zhu2011automated}.
+    \citeauthor{chen2008automatic} filtered successively the possible candidates to be considered as \ac{aif} such that~\citep{chen2008automatic}:
+    (i) dynamic signals with small peak and voxels with a small wash-in are rejected by thresholding,
+    (ii) a blob detector is used and large enough regions are kept, and
+    (iii) circular and cylindricality criteria are used to reject the last false positive.
+    \citeauthor{zhu2011automated} proposed an iterative method selecting voxels which best fit a gamma variate function~\citep{zhu2011automated}.
     However, it requires to compute first and second derivatives as well as maximum curvature points.
-    \citeauthor{shanbhag2012generalized} propose a 4-steps algorithm~\citep{shanbhag2012generalized,fennessy2015quantitative}:
+    \citeauthor{shanbhag2012generalized} proposed a 4-steps algorithm~\citep{shanbhag2012generalized,fennessy2015quantitative}:
     (i) remove slices with artefacts and find the best slices based on intrinsic anatomic landmarks and enhancement characteristics,
     (ii) find the voxel candidates using the maximum enhanced voxels and a multi-label maximum entropy based thresholding algorithm,
-    (iii) excluding region next to the endorectal coil, and
-    (iv) selecting the best 5 candidates which meet enhancement characteristics and that are correlated.
+    (iii) exclude region next to the endorectal coil, and
+    (iv) select the best 5 candidates which meet enhancement characteristics and that are correlated.
 
@@
         We presented in the two previous sections the algorithms which allows to estimate the patient-based \ac{aif} concentration.
-        To compare with the previous approach, we also computed a population-based \ac{aif} which will be also later used to compare the performance of both approaches.
+        To compare with the previous approach, we also computed a population-based \ac{aif} which will be also used later to compare the performance of both approaches.
         In that regard, the population-based \ac{aif} was estimated as in~\citep{meng2010comparison} by fitting the average patient-based \ac{aif}s to the model of~\cite{parker2006experimentally} which is formulated as in Eq.\,\eqref{eq:parker}:
@@
 
-\citeauthor{gliozzi2011phenomenological} show that \ac{pun} approach can be used for \ac{dce}-\ac{mri} analysis~\citep{gliozzi2011phenomenological}.
+\citeauthor{gliozzi2011phenomenological} showed that \ac{pun} approach can be used for \ac{dce}-\ac{mri} analysis~\citep{gliozzi2011phenomenological}.
 The model has been successfully used in a \ac{cad} system proposed by~\cite{giannini2015fully}.
@@
 
-The semi-quantitative analysis of the \ac{dce}-\ac{mri} is equivalent to extract curve characteristics directly from the signal without a strict theoretical pharmacokinetic meaning.
-In this work, we use the model presented by~\cite{huisman2001accurate} which formulate the \ac{mri} signal as in Eq.\,\eqref{eq:huisman}:
+The semi-quantitative analysis of the \ac{dce}-\ac{mri} is equivalent to extracting curve characteristics directly from the signal without a strict theoretical pharmacokinetic meaning.
+In this work, we use the model presented by~\cite{huisman2001accurate} which formulated the \ac{mri} signal as in Eq.\,\eqref{eq:huisman}:
 
@@
 The \ac{aif} signal is computed as in Section~\ref{sec:tofts}.
-$t_0$ is estimated by finding the maximum in the beginning of the first derivative of the \ac{mri} signal.
-Then, the function in Eq.\,\eqref{eq:huisman} is fitted using non-linear least squares with Trust Region Reflective algorithm.
+$t_0$ is estimated by finding the maximum of the first derivative of the \ac{aif} signal, always occurring at the beginning of the signal.
+Then, the function in Eq.\,\eqref{eq:huisman} is fitted using non-linear least squares with Trust Region Reflective algorithm~\citep{sorensen1982newton}.
 Furthermore, the parameters $\tau$ and $S_M$ are bounded during the optimization to ensure robust estimations.
+$\tau$ is bounded between $t_0$ and $t_f$ which is the time of the last sample while $S_M$ is bounded between $S_0$ and $\max(s(t))$.
 

### 2016-08-26 04_discussions/discussions.tex
Address robert and fab changes

@@
 However, there is two shortcomings to take into account while advancing this fact:
-(i) T$_10$ parameter has been fixed and not computed from a T$_1$ map and
+(i) T$_{10}$ parameter has been fixed and not computed from a T$_1$ map and
 (ii) the population-based \ac{aif} has been estimated from a cohort of only 17 patients.

### 2016-08-27 01_introduction/introduction.tex
finished

@@
 In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
+The benefit and simplicity of our approach will be shown by classifying the whole normalized \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
+Additionally, we will show that using this normalization approach in conjunction with the quantitative methods improves the classification performance in for most of the models.
+
 {\color{red}The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.

### 2016-08-27 02_methods/methods.tex
finished

@@
 
-In \ac{dce}-\ac{mri}, the intensity \ac{pdf} of prostate gland does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathist}.
+In \ac{dce}-\ac{mri}, the intensity \ac{pdf} of prostate gland does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathhist}.
 Indeed, the inter-patient variations are more complex due to the temporal acquisition.
@@
 
-\subsubsection{Graph-based intensity offset correction}
+\subsubsection{Graph-based intensity offsets correction}\label{sec:intoffsets}
 
@@
 Additionally, these offsets should be characterized by a smooth transition between series over time.
-Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{subfig:heatmaprep}, the offsets correspond to the boundary splitting the heatmap in two partitions such that they are as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
+Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{subfig:pathhist}, the offsets correspond to the boundary splitting the heatmap in two partitions such that they are as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
 Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar--- i.e., the probability for a given time and pixel intensity---of the heatmap as a node and connecting each pair of bars by an edge.
@@
 Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
-Once all these parameters have been inferred, the data can be shifted as well as scale.
+Once all these parameters have been inferred, the data are shifted as well as scale.
+
+The resulting normalized data can be classified into two fashions: (i) each normalized signal can be classified considering the whole \ac{dce}-\ac{mri} signal or (ii) the normalized data can be fitted using a quantitative method, as presented in the next section.
+However, in the second strategy, this is necessary to apply common intensity offsets such that the data follow a shape as expected by the different quantitative models.
+The set of offsets applied is in fact corresponding to the maximum offsets found in Sect.\,\ref{sec:intoffsets}.
 
@@
 
-As stated in the introduction, one of our main challenge is to demonstrate the benefit of using our normalization method prior to extract parameters using quantitative and semi-quantitative methods.
-In this section, we summarize the different methods which have been used for the quantification of \ac{dce}-\ac{mri} for \ac{cap} detection~\citep{lemaitre2015computer}.
+In this section, we summarize the different methods which have been used for the quantification of \ac{dce}-\ac{mri} for \ac{cap} detection~\citep{lemaitre2015computer} and which will be used for comparison in this work.
 Furthermore, we would like to emphasize the following additional contributions: (i) a novel automatic \ac{aif} estimation algorithm based on clustering and (ii) a simplified semi-quantitative method using constrained optimization.

### 2016-08-27 03_experiments/experiments.tex
finished

--- 2016-08-24 03_experiments/experiments.tex
@@
 
-\subsection{Classification of individual parameter for each model}
+\subsection{Goodness of model fitting}\label{sec:fit}
 
-% \begin{table}
-%   \caption{\acs*{auc} of the individual features for each method.}
-%   \centering
-%   \begin{tabular}{l c c c c}
-%     \toprule
-%     \textbf{Features} & \multicolumn{2}{c}{Un-normalized data} & \multicolumn{2}{c}{Normalized data} \\
-%     & \acs*{rf} & \acs*{nb} & \acs*{rf} & \acs*{nb} \\
-%     \midrule
-%     \textbf{Brix model} & & & & \\
-%     \quad $A$         & 0.54 & 0.62 & 0.58 & 0.67 \\
-%     \quad $k_{el}$    & 0.55 & 0.52 & 0.54 & 0.61 \\
-%     \quad $k_{ep}$    & 0.51 & 0.52 & 0.51 & 0.58 \\
-%     \textbf{Hoffmann model} & & & & \\
-%     \quad $A$         & 0.52 & 0.50 & 0.51 & 0.56 \\
-%     \quad $k_{el}$    & 0.55 & 0.53 & 0.54 & 0.64 \\
-%     \quad $k_{ep}$    & 0.55 & 0.50 & 0.53 & 0.66 \\
-%     \textbf{Tofts model with population \ac{aif}} & & & & \\
-%     \quad $K_{trans}$ & 0.56 & 0.62 & 0.56 & 0.65 \\
-%     \quad $v_{e}$     & 0.51 & 0.50 & 0.50 & 0.52 \\
-%     \quad $v_{p}$     & 0.53 & 0.63 & 0.55 & 0.53 \\
-%     \textbf{Tofts model with patient \ac{aif}} & & & & \\
-%     \quad $K_{trans}$ & 0.57 & 0.66 & 0.56 & 0.65 \\
-%     \quad $v_{e}$     & 0.49 & 0.50 & 0.51 & 0.52 \\
-%     \quad $v_{p}$     & 0.53 & 0.37 & 0.57 & 0.65 \\
-%     \textbf{\ac{pun} model} & & & & \\
-%     \quad $a_0$       & 0.52 & 0.53 & 0.53 & 0.51  \\
-%     \quad $r$         & 0.53 & 0.59 & 0.55 & 0.55 \\
-%     \quad $\beta$     & 0.55 & 0.56 & 0.53 & 0.44 \\
-%     \textbf{Semi-quantitative analysis} & & & & \\
-%     \quad wash-in     & 0.59 & 0.64 & 0.55 & 0.51 \\
-%     \quad wash-out    & 0.52 & 0.50 & 0.56 & 0.66 \\
-%     \quad IAUC        & 0.51 & 0.61 & 0.52 & 0.64 \\
-%     \quad $\tau$      & 0.57 & 0.57 & 0.56 & 0.61 \\
-%     \quad $S_M - S_0$ & 0.56 & 0.63 & 0.53 & 0.64 \\
-%     \bottomrule
-%   \end{tabular}
-%   \label{tab:resfeats}
-% \end{table}
+%{\color{red} In case that we have issue with $R^2$, we need to provide the AIC since that the model are usually non-linear.}
 
-\begin{table}
-  \caption{\acs*{auc} for each individual pharmacokinetic parameter using a \acs*{nb} classifier.}
+\begin{table*}
+  \caption{Coefficient of determination $R^{2}$ (i.e., $\mu \ (\pm \sigma)$), while fitting data with the different quantification models.}
   \centering
+  \resizebox{\columnwidth}{!}{
+  \begin{tabular}{lc c c c c c}
+    \toprule
+    Data type & Brix & Hoffmann & Tofts population \ac{aif} & Tofts patient \ac{aif} & \ac{pun} & Semi-quantitative \\
+    \midrule
+    Un-normalized & $0.85 \ (\pm 0.11)$ & $0.81 \ (\pm 0.17)$ & $0.84 \ (\pm 0.14)$ & $0.88 \ (\pm 0.12)$ & $0.27 \ (\pm 0.18)$ & $0.64 \ (\pm 0.24)$  \\
+    Normalized    & $0.92 \ (\pm 0.05)$ & $0.72 \ (\pm 0.32)$ & $0.92 \ (\pm 0.06)$ & $0.90 \ (\pm 0.10)$ & $0.28 \ (\pm 0.20)$ & $0.75 \ (\pm 0.20)$  \\
+    \bottomrule
+  \end{tabular}
+  }
+  \label{tab:r2}
+\end{table*}
+
+Parameter estimation of the quantification methods are related to fit a specific model to the \ac{dce}-\ac{mri} data.
+Therefore, this section report the goodness of fitting by computing the coefficient of determination $R^2$ such as in Eq.\,\eqref{eq:r2}
+
+\begin{equation}
+  R^2 = 1 - \frac{\sum_{t = 0}^{T} (s_t - \hat{s}_t)^2}{\sum_{t = 0}^{T} (s_t - \bar{s})^2} ,
+  \label{eq:r2}
+\end{equation}
+
+\noindent where $s_t$ and $\hat{s}_t$ are the signal to be fitted and the estimated signal at time $t$, respectively; $\bar{s}$ is the average signal to be fitted.
+
+Mean and standard-deviation of the coefficient of determination $R^{2}$ is reported in Table~\ref{tab:r2} for each quantification model.
+Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.%, implying that they are adequate models for that purpose.
+Additionally, the proposed \ac{pun} model does not seem to fit well the data.
+Normalizing the data improve the coefficient $R^2$ for all the methods apart of the Hoffmann model.
+The large standard deviation for this model might imply that there is some cases, that the fitting fails.
+
+\subsection{Detection of \acs*{cap} using pharmacokinetic parameters}
+
+\begin{table*}
+  \caption{\acs*{auc} for each individual pharmacokinetic parameter using a \acs*{rf} classifier.}
+  \centering
+  \resizebox{\columnwidth}{!}{
   \begin{tabular}{l c c}
@@
     \textbf{Brix model} & & \\
-    \quad $A$         & 0.62 & 0.67 \\
-    \quad $k_{el}$    & 0.52 & 0.61 \\
-    \quad $k_{ep}$    & 0.52 & 0.58 \\
+    \quad $A$         & 0.54 & 0.55 \\
+    \quad $k_{el}$    & 0.51 & 0.50 \\
+    \quad $k_{ep}$    & 0.55 & 0.58 \\
     \textbf{Hoffmann model} & & \\
-    \quad $A$         & 0.50 & 0.56 \\
-    \quad $k_{el}$    & 0.53 & 0.64 \\
-    \quad $k_{ep}$    & 0.50 & 0.66 \\
+    \quad $A$         & 0.52 & 0.51 \\
+    \quad $k_{el}$    & 0.55 & 0.53 \\
+    \quad $k_{ep}$    & 0.55 & 0.54 \\
     \textbf{Tofts model with population \ac{aif}} & & \\
-    \quad $K_{trans}$ & 0.62 & 0.65 \\
-    \quad $v_{e}$     & 0.50 & 0.52 \\
-    \quad $v_{p}$     & 0.63 & 0.53 \\
+    \quad $K_{trans}$ & 0.56 & 0.55 \\
+    \quad $v_{e}$     & 0.49 & 0.49 \\
+    \quad $v_{p}$     & 0.53 & 0.50 \\
     \textbf{Tofts model with patient \ac{aif}} & & \\
-    \quad $K_{trans}$ & 0.66 & 0.65 \\
-    \quad $v_{e}$     & 0.50 & 0.52 \\
-    \quad $v_{p}$     & 0.37 & 0.65 \\
+    \quad $K_{trans}$ & 0.57 & 0.57 \\
+    \quad $v_{e}$     & 0.51 & 0.53 \\
+    \quad $v_{p}$     & 0.53 & 0.55 \\
     \textbf{\ac{pun} model} & & \\
-    \quad $a_0$       & 0.53 & 0.51 \\
-    \quad $r$         & 0.59 & 0.55 \\
-    \quad $\beta$     & 0.56 & 0.44 \\
+    \quad $a_0$       & 0.52 & 0.53 \\
+    \quad $r$         & 0.55 & 0.57 \\
+    \quad $\beta$     & 0.53 & 0.55 \\
     \textbf{Semi-quantitative analysis} & & \\
-    \quad wash-in     & 0.64 & 0.51 \\
-    \quad wash-out    & 0.50 & 0.66 \\
-    \quad IAUC        & 0.61 & 0.64 \\
-    \quad $\tau$      & 0.57 & 0.61 \\
-    \quad $S_M - S_0$ & 0.63 & 0.64 \\
+    \quad wash-in     & 0.57 & 0.53 \\
+    \quad wash-out    & 0.52 & 0.49 \\
+    \quad IAUC        & 0.51 & 0.51 \\
+    \quad $\tau$      & 0.57 & 0.54 \\
+    \quad $S_M - S_0$ & 0.56 & 0.53 \\
     \bottomrule
   \end{tabular}
+  }
   \label{tab:resfeats}
-\end{table}
+\end{table*}
 
-This experiment consists in assessing the benefit of normalizing the \ac{dce}-\ac{mri}, prior to classify each individual parameter for each model.
-Therefore, a Gaussian \ac{nb} classifier is used in conjunction with a \ac{lopo}.
-The results are summarized in Table~\ref{tab:resfeats}.
-In general, data normalization leads to better classification performance while extracting pharmacokinetic related parameters.
-Only the \ac{pun} model does not follow this tendency.
-{\color{red} Find out why!!!}
-
-\subsection{Classification by combining the parameters for each model}
-
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \label{fig:normpharmarf}
-\end{figure}
+\end{figure*}
 
-In previous proposed \ac{cad} systems, the pharmacokinetic of a single model are combined.
-Therefore, for each model, all parameters are combined and classified using a \ac{rf} classifier in a \ac{lopo} fashion.
-The use of \ac{rf} is motivated since that it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer}.
-Results are summarized by performing a \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
-Independently to the quantification model, the data normalization improves the\ac{auc} and classification performance.
-
-% \begin{figure}
-%   \centering
-%   \hspace*{\fill}
-%   \subfigure[Without normalization.]{\label{fig:nbpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/nb.pdf}} \hfill
-%   \subfigure[With normalization.]{\label{fig:nbpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/nb.pdf}}
-%   \hspace*{\fill}
-%   \caption{\acs*{roc} analysis using a \acs*{nb} classifier with and without normalization \ac{dce}-\ac{mri} data for different pharmacokinetic models.}
-%   \label{fig:normpharmanb}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \hspace*{\fill}
-%   \subfigure[\acs*{rf} classifier.]{\label{fig:rfunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/rf.pdf}} \hfill
-%   \subfigure[\acs*{nb} classifier.]{\label{fig:nbunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/nb.pdf}}
-%   \hspace*{\fill}
-%   \caption{\acs*{roc} analysis using the entire \ac{dce}-\ac{mri} signal with and without normalization.}
-%   \label{fig:unormdcesignal}
-% \end{figure}
+To study the potential benefit of our normalization, \ac{cap} are detected using pharmacokinetic parameters estimated from un-normalized and normalized \ac{dce}-\ac{mri} data.
+Each individual pharmacokinetic parameter is classified to evaluate their individual discriminative power to detect \ac{cap}.
+Therefore, a \ac{rf} classifier is used in conjunction with a \ac{lopo}.
+The use of \ac{rf} is motivated since that it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer,lemaitre2015computer}.
+Results are summarized in Table~\ref{tab:resfeats} in terms of \ac{auc}.
+Normalization can improve the detection of \ac{cap}; however, the benefit of normalization is more obvious by combining the pharmacokinetic features of each model, as previously done in traditional \ac{cad} system~\citep{lemaitre2015computer}.
+For the latter configuration, results are summarized by performing a \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
+Quantification using normalized data outperforms quantification using un-normalized data in terms of classification performance apart of Hoffmann and Tofts population-based \ac{aif} models.
+The reasons behind the decrease of the \ac{auc} might be related to: (i) a poor fitting as discussed in Sect.\,\ref{sec:fit} (cf., Hoffmann model) and (ii) a small number of patient while estimating some parameters (cf., Tofts model).
+The best classification performance are obtained using the semi-quantitative approach with an \ac{auc} of 0.655.
 
@@
 As stated in the introduction, the quantification methods are extracting a set of parameters characterizing the enhancement \ac{dce}-\ac{mri} signal.
-However, this extraction could lead to a loss of information.
+However, this extraction might lead to a loss of information.
 This experiment is performed to assess if making use of the whole \ac{dce}-\ac{mri} signal instead of the just the pharmacokinetic parameters can improve the classification performance.
@@
 The \ac{roc} analysis and \ac{auc} are reported in Fig.\,\ref{fig:rfnormdcesignal}.
-It can be noted that the worst performance are achieved while classifying raw data without normalization.
-However, data normalization in conjunction with the use of the whole \ac{dce}-\ac{mri} signal is the strategy which outperforms all others.
+Classification without normalization lead to the worst performance, with an \ac{auc} of 0.568.
+However, data normalization in conjunction with the use of the whole \ac{dce}-\ac{mri} signal is the strategy which outperforms all others, with an \ac{auc} of 0.666.
 

### 2016-08-27 01_introduction/introduction.tex
remove some highlights

@@
 
-{\color{red}The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
-Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.}
+The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
+Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.
 

### 2016-08-27 02_methods/methods.tex
Added the figures missing
symbol

@@
   \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
-  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}} \hfill
+  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
   \hspace*{\fill}
-  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\sigma_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
+  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\alpha_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
   \label{fig:heatmap}
@@
 (ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
-(iii) a change of scale $\sigma_i$ related to the signal enhancement.
+(iii) a change of scale $\alpha_i$ related to the signal enhancement.
 Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.

### 2016-08-29 01_introduction/introduction.tex
Add fab correction

@@
 
-\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling since that no pharmacokinetic assumption regarding the relation between the \ac{mri} signal and the contrast agent~\citep{huisman2001accurate,gliozzi2011phenomenological}.
+\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling since that no pharmacokinetic assumption regarding the relation between the \ac{mri} signal and the contrast agent are made~\citep{huisman2001accurate,gliozzi2011phenomenological}.
 These methods offer the advantages to not require any knowledge about the \ac{mri} sequence nor any conversion from signal intensity to concentration.
-However, the heuristic approach proposed by \citeauthor{huisman2001accurate} requires an initial estimate of the noise standard deviation of the signal as well as manual tuning.
+However, the heuristic approach proposed by \citeauthor{huisman2001accurate} requires an initial estimate of the noise standard deviation of the signal as well as some manual tuning.
 
@@
 The benefit and simplicity of our approach will be shown by classifying the whole normalized \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
-Additionally, we will show that using this normalization approach in conjunction with the quantitative methods improves the classification performance in for most of the models.
+Additionally, we will show that using this normalization approach in conjunction with the quantitative methods improves the classification performance for most of the models.
 

### 2016-08-29 02_methods/methods.tex
Add fab correction

@@
 Indeed, the inter-patient variations are more complex due to the temporal acquisition.
-A better representation to observe these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
+A better representation to observe these variations is to represent the intensity \ac{pdf} of the prostate gland over time--- requiring to segment the prostate ---using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
 Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
@@
 In general, this process is not repeated more than 3 iterations.
+The parameter $\alpha$ is set to $0.9$, empirically.
 Figure~\ref{fig:estimator} illustrates the final estimation of the offsets (i.e., red landmark) found for each \ac{dce}-\ac{mri} serie.
@@
 \begin{equation}
-  f(t) = \sqrt{ \left( \frac{\sum_{n=0}^{N} x(t)_{n}^2}{N}  \right) },
+  f(t) = \sqrt{ \left( \frac{\sum_{n=1}^{N} x(t)_{n}^2}{N}  \right) },
   \label{eq:rmsd}
@@
 \begin{equation}
-  \argmin_{\alpha, \tau} = \sum_{t=0}^{N} \left[ T\left(\alpha, \tau, f(t)\right) - \mu(t) \right]^{2} ,
+  \argmin_{\alpha, \tau} = \sum_{t=1}^{N} \left[ T\left(\alpha, \tau, f(t)\right) - \mu(t) \right]^{2} ,
   \label{eq:cost}
@@
 Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
-Once all these parameters have been inferred, the data are shifted as well as scale.
+Once all these parameters have been inferred, the data are shifted as well as scaled.
 
@@
 
-\noindent where $\Conv$ is the convolution operator; $C_t(t)$ and $C_p(t)$ is the concentration of contrast agent in the tissue and in the plasma, respectively; $K_{trans}$, $k_{ep}$, and $v_p$ are the volume transfer constant, the diffusion rate constant, and the plasma volume fraction, respectively.
+\noindent where $\Conv$ is the convolution operator; $C_t(t)$ and $C_p(t)$ are the concentrations of contrast agent in the tissue and in the plasma, respectively; $K_{trans}$, $k_{ep}$, and $v_p$ are the volume transfer constant, the diffusion rate constant, and the plasma volume fraction, respectively.
 
@@
     (i) all possible \ac{aif} signal candidates should have a similar shape,
-    (ii) an high enhancement, and
+    (ii) a high enhancement, and
     (iii) the arteries should be almost round and within a size range.

### 2016-08-30 03_experiments/experiments.tex
Add fab correction
Correct one parameter for Tofts in the results
Add link to zenodo

@@
 The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
-The data used for this work are also publicly available\footnote{\url{http://kaggle.com}}.
+The data used for this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}.
 
@@
 \begin{equation}
-  R^2 = 1 - \frac{\sum_{t = 0}^{T} (s_t - \hat{s}_t)^2}{\sum_{t = 0}^{T} (s_t - \bar{s})^2} ,
+  R^2 = 1 - \frac{\sum_{t = 1}^{T} (s_t - \hat{s}_t)^2}{\sum_{t = 1}^{T} (s_t - \bar{s})^2} ,
   \label{eq:r2}
@@
 Mean and standard-deviation of the coefficient of determination $R^{2}$ is reported in Table~\ref{tab:r2} for each quantification model.
-Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.%, implying that they are adequate models for that purpose.
+Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.
 Additionally, the proposed \ac{pun} model does not seem to fit well the data.
@@
     \quad $K_{trans}$ & 0.56 & 0.55 \\
-    \quad $v_{e}$     & 0.49 & 0.49 \\
+    \quad $k_{ep}$     & 0.49 & 0.49 \\
     \quad $v_{p}$     & 0.53 & 0.50 \\
@@
     \quad $K_{trans}$ & 0.57 & 0.57 \\
-    \quad $v_{e}$     & 0.51 & 0.53 \\
+    \quad $k_{ep}$     & 0.51 & 0.53 \\
     \quad $v_{p}$     & 0.53 & 0.55 \\

### 2016-08-30 03_experiments/experiments.tex
Add link to zenodo for github repo

@@
 
-The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
-The data used for this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}.
+The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}~\citep{lemaitre2016github}.
+The data used for this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}~\citep{lemaitre2016dce}.
 

### 2016-08-31 01_introduction/introduction.tex
Address the comments of robert

--- 2016-08-27 01_introduction/introduction.tex
@@
 This assumption has shown, however, to lead to inaccurately estimate the pharmacokinetic parameters~\citep{heilmann2006determination}.
-In the contrary, Tofts model requires a conversion from \ac{mri} signal intensity to concentration, which become a non-linear relationship using specific equation of \ac{mri} sequences (e.g., FLASH sequence).
+In the contrary, Tofts model requires a conversion from \ac{mri} signal intensity to concentration, which becomes a non-linear relationship using specific equation of \ac{mri} sequences (e.g., FLASH sequence).
 Tofts modelling suffers, however, from a higher complexity~\citep{gliozzi2011phenomenological}.
 Indeed, the conversion using the non-linear approach requires to acquire a T$_1$ map which is not always possible during clinical examination.
-Additionally, the parameter calculation requires the \ac{aif} which is challenging to measure and can also lead to inaccurate estimation.
+Additionally, the parameter calculation requires the \ac{aif} which is challenging to measure and can also lead to an inaccurate estimation.
 
-\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling since that no pharmacokinetic assumption regarding the relation between the \ac{mri} signal and the contrast agent~\citep{huisman2001accurate,gliozzi2011phenomenological}.
+\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling since no pharmacokinetic assumption regarding the relation between the \ac{mri} signal and the contrast agent are made~\citep{huisman2001accurate,gliozzi2011phenomenological}.
 These methods offer the advantages to not require any knowledge about the \ac{mri} sequence nor any conversion from signal intensity to concentration.
-However, the heuristic approach proposed by \citeauthor{huisman2001accurate} requires an initial estimate of the noise standard deviation of the signal as well as manual tuning.
+However, they present some limitations: the heuristic approach proposed by \citeauthor{huisman2001accurate} requires an initial estimate of the noise standard deviation of the signal as well as some manual tuning.
 
@@
 (i) inter-patient variability and (ii) loss of information.
-The inter-patient variability is mainly due to the acquisition process and consequently leads to generalization issue while applying machine learning algorithm.
+The inter-patient variability is mainly due to the acquisition process and consequently leads to generalization issue while applying a machine learning algorithm.
 All previous methods extract few discriminative parameters to describe the \ac{dce}-\ac{mri} signal which might lead to a loss of information.
@@
 The benefit and simplicity of our approach will be shown by classifying the whole normalized \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
-Additionally, we will show that using this normalization approach in conjunction with the quantitative methods improves the classification performance in for most of the models.
+Additionally, we will show that using this normalization approach in conjunction with the quantitative methods improves the classification performance of most of the models.
+We also propose a new clustering-based method to segment enhanced signals from the arteries, later used to estimate an \ac{aif} as well as an alternative approach to estimate the parameters of the semi-quantitative model proposed by~\cite{huisman2001accurate}.
 
-The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
-Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.
+% The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
+% Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.
 
 The paper is organized as follows:
-Section~\ref{sec:norm} presents into details our normalization strategy for \ac{dce}-\ac{mri} data.
+Section~\ref{sec:norm} details our normalization strategy for \ac{dce}-\ac{mri} data.
 Quantitative and semi-quantitative methods are summarized in Sect.\,\ref{sec:stateart} with insights about their implementations.

### 2016-08-31 02_methods/methods.tex
modified an optimization
Address the comments of robert

@@
 In \ac{t2w}-\ac{mri}, these variations are characterized by a shift and a scaling of the intensities as illustrated by the intensity \ac{pdf} in Fig.\,\ref{fig:t2w}.
-Therefore, these variations can be corrected using a $z$-score approach, assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
+Therefore, these variations can be corrected using a $z$-score approach--- i.e., normalizing the data by subtracting the mean and dividing by the standard deviation ---assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
 
@@
 Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
-(i) an intensity offset $\Delta_i$ of the \ac{pdf} peak at pre-contrast,
+(i) intensity offsets $\Delta_i$ of the \ac{pdf} peak,
 (ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
 (iii) a change of scale $\alpha_i$ related to the signal enhancement.
-Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.
+Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequences rather than for each independent sequence.
 
@@
 
-Therefore, these offsets are estimated by finding the shortest-path to cross the graph using Dijkstra's algorithm.
+Therefore, these offsets related to $\Delta_i$ are estimated by finding the shortest-path to cross the graph using Dijkstra's algorithm.
 The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
 To ensure a robust estimation of these offsets, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
-The procedure is stopped once that the offset found does not change.
+The procedure is stopped once the offset found does not change.
 In general, this process is not repeated more than 3 iterations.
 The parameter $\alpha$ is set to $0.9$, empirically.
-Figure~\ref{fig:estimator} illustrates the final estimation of the offsets (i.e., red landmark) found for each \ac{dce}-\ac{mri} serie.
+Figure~\ref{fig:estimator} illustrates the final estimation of the offsets $\Delta_i$ (i.e., red landmark) found for each \ac{dce}-\ac{mri} serie.
 Therefore, each intensity offset is subtracted for each \ac{dce}-\ac{mri}.
@@
 
-The next variations to correct are the time offset and the data dispersion.
+The next variations to correct are the time offset $\Delta_t$ and the data dispersion $\sigma_i$.
 By computing the \ac{rmse} of the intensities for each \ac{dce}-\ac{mri} serie, one can observe these two variations as shown in Fig.\,\ref{fig:rmse}.
@@
 
-\noindent where $\alpha$ and $\tau$ are the two parameters handling the time offset and global scale, respectively, $f(\cdot)$ is the \ac{rmse} function define as:
+\noindent where $\alpha$ and $\tau$ are the two parameters handling the time offset $\Delta_i$ and global scale $\sigma_i$, respectively, $f(\cdot)$ is the \ac{rmse} function define as:
 
@@
 
-The resulting normalized data can be classified into two fashions: (i) each normalized signal can be classified considering the whole \ac{dce}-\ac{mri} signal or (ii) the normalized data can be fitted using a quantitative method, as presented in the next section.
-However, in the second strategy, this is necessary to apply common intensity offsets such that the data follow a shape as expected by the different quantitative models.
-The set of offsets applied is in fact corresponding to the maximum offsets found in Sect.\,\ref{sec:intoffsets}.
+The resulting normalized data can be used into two fashions: (i) each normalized signal can be used as a whole to determine whether the corresponding voxel is healthy or cancerous or (ii) the normalized data can be fitted using a quantitative method, as presented in the next section.
+%However, for the second strategy, this is necessary to apply common intensity offsets such that the data follow a shape as expected by the different quantitative models.
+%The set of offsets applied is in fact corresponding to the maximum offsets found in Sect.\,\ref{sec:intoffsets}.
 
@@
 In this section, we summarize the different methods which have been used for the quantification of \ac{dce}-\ac{mri} for \ac{cap} detection~\citep{lemaitre2015computer} and which will be used for comparison in this work.
-Furthermore, we would like to emphasize the following additional contributions: (i) a novel automatic \ac{aif} estimation algorithm based on clustering and (ii) a simplified semi-quantitative method using constrained optimization.
+Furthermore, we would like to emphasize the following additional contributions for this section: (i) a novel automatic \ac{aif} estimation algorithm based on clustering and (ii) a simplified semi-quantitative method using constrained optimization.
 
@@
     (ii) a blob detector is used and large enough regions are kept, and
-    (iii) circular and cylindricality criteria are used to reject the last false positive.
+    (iii) circular and cylindricality criteria are used to reject the false positives.
     \citeauthor{zhu2011automated} proposed an iterative method selecting voxels which best fit a gamma variate function~\citep{zhu2011automated}.
@@
 
-    All the above methods are rather complex and thus we propose a method which is based on the following simple assumptions:
+    All the above methods are rather complex and thus we propose a simpler method which is based on the following reasonable assumptions:
     (i) all possible \ac{aif} signal candidates should have a similar shape,
@@
     Therefore, each slice is clustered into regions using K-means clustering with $k=6$.
-    The cluster with the highest enhancement\textemdash i.e.
-corresponding to the 90\textsuperscript{th} percentile of the maximum of each dynamic signal\textemdash contain the arteries and is selected.
+    The cluster made of the most enhanced signals is selected since it contains the artery signals.
+    In this regards, the selection criteria corresponds to the 90\textsuperscript{th} percentile of the maximum \ac{dce}-\ac{mri} signal.
     Finally, regions with an eccentricity smaller than $0.5$ and an area in the range of $[100, 400]$ voxels are kept.
@@
       \end{equation}
-      \noindent where $s(t)$ is the \ac{mri} signal, $S_0$ is the \ac{mri} signal prior to the injection of the contrast media, $\alpha$ is the flip angle, $TR$ is the \acf{tr}, $R_{10}$ is the pre-contrast tissue relaxation time also equal to $\frac{1}{T_{10}}$, $r_1$ is the relaxitivity coefficient of the contrast agent.
+      \noindent where $s(t)$ is the \ac{mri} signal, $S_0$ is the \ac{mri} signal prior to the injection of the contrast media, $\alpha$ is the flip angle, $TR$ is the \acf{tr}, $R_{10}$ is the pre-contrast tissue relaxation time also equal to $\frac{1}{T_{10}}$, and $r_1$ is the relaxitivity coefficient of the contrast agent.
 
@@
 
-The parameters are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
+The parameters are estimated by fitting the model using a constrained non-linear least-squares optimization, solved with the Trust Region Reflective algorithm~\citep{sorensen1982newton} and bounding the parameters to be positive.
 
@@
 $t_0$ is estimated by finding the maximum of the first derivative of the \ac{aif} signal, always occurring at the beginning of the signal.
-Then, the function in Eq.\,\eqref{eq:huisman} is fitted using non-linear least squares with Trust Region Reflective algorithm~\citep{sorensen1982newton}.
+Then, the function in Eq.\,\eqref{eq:huisman} is fitted using non-linear least squares with the Trust Region Reflective algorithm~\citep{sorensen1982newton}.
 Furthermore, the parameters $\tau$ and $S_M$ are bounded during the optimization to ensure robust estimations.

### 2016-08-31 03_experiments/experiments.tex
Address the comments of robert

@@
 The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
-Aside of the \ac{mri} examination, these patients also have underwent a guided-biopsy.
+Aside of the \ac{mri} examination, these patients also have undergone a guided-biopsy.
 The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
@@
 Additionally, the proposed \ac{pun} model does not seem to fit well the data.
-Normalizing the data improve the coefficient $R^2$ for all the methods apart of the Hoffmann model.
-The large standard deviation for this model might imply that there is some cases, that the fitting fails.
+Data normalization improves the coefficient $R^2$ for all the methods apart of the Hoffmann model.
+The large standard deviation for this model might imply that there are some cases where the fitting fails.
 
@@
 
-To study the potential benefit of our normalization, \ac{cap} are detected using pharmacokinetic parameters estimated from un-normalized and normalized \ac{dce}-\ac{mri} data.
+To study the potential benefit of our normalization, \ac{cap} are detected at a voxel level using pharmacokinetic parameters estimated from un-normalized and normalized \ac{dce}-\ac{mri} data.
 Each individual pharmacokinetic parameter is classified to evaluate their individual discriminative power to detect \ac{cap}.
@@
 Results are summarized in Table~\ref{tab:resfeats} in terms of \ac{auc}.
-Normalization can improve the detection of \ac{cap}; however, the benefit of normalization is more obvious by combining the pharmacokinetic features of each model, as previously done in traditional \ac{cad} system~\citep{lemaitre2015computer}.
+Normalization can improve the detection of \ac{cap}; however, the benefit of normalization is more obvious by combining together the pharmacokinetic features of a given model (e.g., $A$, $k_ep$, and $k_el$ for Brix model), as previously done in traditional \ac{cad} system~\citep{lemaitre2015computer}.
 For the latter configuration, results are summarized by performing a \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
 Quantification using normalized data outperforms quantification using un-normalized data in terms of classification performance apart of Hoffmann and Tofts population-based \ac{aif} models.
-The reasons behind the decrease of the \ac{auc} might be related to: (i) a poor fitting as discussed in Sect.\,\ref{sec:fit} (cf., Hoffmann model) and (ii) a small number of patient while estimating some parameters (cf., Tofts model).
+The reasons behind the decrease of the \ac{auc} might be related to: (i) a poor fitting as discussed in Sect.\,\ref{sec:fit} (cf., Hoffmann model) and (ii) a small number of patients while estimating some parameters (cf., Tofts model).
 The best classification performance are obtained using the semi-quantitative approach with an \ac{auc} of 0.655.

### 2016-08-31 04_discussions/discussions.tex
finished
Address the comments of robert

--- 2016-08-24 04_discussions/discussions.tex
@@
 In Tofts quantification, two different approaches have been used to infer the pharmacokinetic parameters: using a population-based or a patient-based \ac{aif}.
-The population-based \ac{aif} approach leads to better classification performance.
-However, there is two shortcomings to take into account while advancing this fact:
-(i) T$_10$ parameter has been fixed and not computed from a T$_1$ map and
+The patient-based \ac{aif} approach leads to better classification performance.
+However, there are two shortcomings to take into account while advancing this fact:
+(i) T$_{10}$ parameter has been fixed and not computed from a T$_1$ map and
 (ii) the population-based \ac{aif} has been estimated from a cohort of only 17 patients.
@@
 The best classification performance is reached by normalizing the \ac{dce}-\ac{mri} data and use the whole enhanced signal as feature, emphasizing the fact that a loss of information while extracting quantitative parameters.
-However, this strategy suffers from one drawback: the training time of the \ac{rf} classifier increases since that from 3 to 5 features, the feature space become a 40 dimensions space.
+Furthermore, this normalization is a less complex process than all quantification methods.
+However, this strategy suffers from one drawback: the training time of the \ac{rf} classifier increases since that from 3 to 5 features, the feature space becomes a 40 dimensions space.
+
+Nevertheless, this study is performed on a small cohort of patients using a single \ac{mri} machine.
+Generalizing the results of this study on a larger dataset acquired from different commercial systems have to be considered to study the robustness of the proposed approach.
 

### 2016-09-01 03_experiments/experiments.tex
Add the standard deviation of the AUC

@@
   \hspace*{\fill}
-  \subfigure[Without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/rf.pdf}} \hfill
-  \subfigure[With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/rf.pdf}}
+  \subfigure[Without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/unormalized_methods_0.pdf}} \hfill
+  \subfigure[With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/normalized_methods_0.pdf}}
   \hspace*{\fill}
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/rf.pdf}
+  \includegraphics[width=0.7\linewidth]{03_experiments/figures/full_signal_0.pdf}
   \caption{\acs*{roc} analysis using the entire \ac{dce}-\ac{mri} signal with and without normalization in conjunction with a \acs*{rf} classifier.}

### 2016-09-01 main.tex
Advance in the methods section
Added the demonstration to make the conversion
Finish to present the sub steps of Tofts
add the first results
start with the normalization
Finish to explain the graph based approach
Finish the draft for the normalization
Finish the first draft
Address robert and fab changes
Add FSU
Add abstract

--- 2016-08-08 main.tex
@@
 \modulolinenumbers[5]
+
+% Package to change into landscape
+\usepackage{pdflscape}
+
+% Package for table
+\usepackage{booktabs}
+
+% For some math expression
+\usepackage{amsmath}
+\usepackage{mathabx}
+\DeclareMathOperator*{\argmin}{arg\,min}
+
+% Package for SI units
+\usepackage{siunitx}
+
+% Package for figures
+\usepackage{epsf,graphicx}
+\usepackage{epstopdf}
+\usepackage{subfigure}
+
+% Package for pseudo algorithm
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\makeatletter
+\def\BState{\State\hskip-\ALG@thistlm}
+\makeatother
+
+% Define the operator of convolution
+\newcommand{\Conv}{\mathop{\scalebox{1.5}{\raisebox{-0.2ex}{$\ast$}}}}%
 
@@
 \author[label3]{Robert~Mart\'i}
+\author[label1]{Mojdeh~Rastgoo}
+\author[label1]{Joan~Massich}
 %\ead{marly@eia.udg.edu}
@@
 %\ead{kvilanova@comg.cat}
-\author[label2]{Paul~M.~Walker}
+%\author[label2]{Paul~M.~Walker}
 %\ead{pwalker@u-bourgogne.fr}
@@
 \address[label1]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, 12 rue de la Fonderie, 71200 Le Creusot, France}
-\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
+%\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
 \address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
@@
 \begin{abstract}
-This template helps you to create a properly formatted \LaTeX\ manuscript.
+\ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used to the design of new \ac{cad} systems.
+\ac{dce}-\ac{mri} is one of the modality regularly used in \ac{mpmri} \ac{cad} system.
+Pharmocokinetric parameters are extracted from the \ac{dce}-\ac{mri} sequences and later used to discriminate cancerous from healthy tissue.
+However, some inter-patients variations occur during the data acquisition leading to estimation errors of the pharmacokinetic parameters.
+Therefore, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
+The benefit and simplicity of our approach is shown by detecting cancerous voxel from healthy voxel using the normalized enhanced \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
+Additionally, we show that using this normalization approach in conjunction with the quantitative methods improves the classification performance of most of the models.
+The best classification performance to detect \ac{cap} is obtained using the whole \ac{dce}-\ac{mri} normalized signal, reaching an \ac{auc} of $0.666\ (\pm 0.154)$ and outperforming the quantitative approaches.
 \end{abstract}
@@
 \input{05_conclusions/conclusions}
+\input{06_appendix/appendix}
 

### 2016-09-01 02_methods/methods.tex
Put the elements into place

@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{02_methods/figures/t2w.pdf}
-  \caption{Illustration of the inter-patient variations in 17 different patients, using the \acs*{pdf} representation.}
-  \label{fig:t2w}
-\end{figure}
-
 In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data to reduce inter-patient variations, although it can be applied to any \ac{dce}-\ac{mri} sequences.
@@
 Therefore, these variations can be corrected using a $z$-score approach--- i.e., normalizing the data by subtracting the mean and dividing by the standard deviation ---assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
-
-\begin{figure*}
-  \centering
-  \hspace*{\fill}
-  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
-  \hspace*{\fill}
-  \\
-  \hspace*{\fill}
-  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
-  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
-  \hspace*{\fill}
-  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\alpha_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
-  \label{fig:heatmap}
-\end{figure*}
 
@@
 \subsubsection{Graph-based intensity offsets correction}\label{sec:intoffsets}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{02_methods/figures/estimator.pdf}
-  \caption{Illustration of the estimator found using the shortest-path through the graph.}
-  \label{fig:estimator}
-\end{figure}
 
@@
 \subsubsection{Time offset and data dispersion correction}
-
-\begin{figure*}
-  \centering
-  \hspace*{\fill}
-  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse.pdf}} \hfill
-  \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
-  \hspace*{\fill}
-  \caption{Illustration of the correction of the time offset and the data dispersion.}
-  \label{fig:curveal}
-\end{figure*}
 
@@
 
-\begin{figure*}
-  \centering
-  \hspace*{\fill}
-  \subfigure[Original image.]{\label{fig:org}\includegraphics[width=.3\textwidth]{02_methods/figures/original.pdf}} \hfill
-  \subfigure[Candidates region after clustering.]{\label{fig:cand}\includegraphics[width=.3\textwidth]{02_methods/figures/candidate.pdf}} \hfill
-  \subfigure[Regions selected after applying the different criteria.]{\label{fig:final}\includegraphics[width=.3\textwidth]{02_methods/figures/aif.pdf}}
-  \hspace*{\fill}
-  \caption{Illustration of the segmentation of the area used to determine the \acs*{aif}.}
-  \label{fig:aif}
-\end{figure*}
-
 \begin{description}
@@
     \item[Conversion of \ac{mri} signal intensity to concentration] To estimate the free parameters of the Tofts model (see Eq.\,\eqref{eq:exttofts}), the concentration $C_t(t)$ and $C_p(t)$ need to be computed from the \ac{mri} signal intensity and the \ac{aif} signal, respectively.
-      This conversion is based on the equation of the FLASH sequence\textemdash see~\ref{app:signaltoconc} for details\textemdash and is formulated as in Eq.\,\eqref{eq:conv}:
+      This conversion is based on the equation of the FLASH sequence\textemdash see Appendix~\ref{app:signaltoconc} for details\textemdash and is formulated as in Eq.\,\eqref{eq:conv}:
       \begin{equation}

### 2016-09-01 03_experiments/experiments.tex
Update the table
Put the elements into place

--- 2016-08-31 03_experiments/experiments.tex
@@
 
-\begin{table*}
-  \caption{Coefficient of determination $R^{2}$ (i.e., $\mu \ (\pm \sigma)$), while fitting data with the different quantification models.}
-  \centering
-  \resizebox{\columnwidth}{!}{
-  \begin{tabular}{lc c c c c c}
-    \toprule
-    Data type & Brix & Hoffmann & Tofts population \ac{aif} & Tofts patient \ac{aif} & \ac{pun} & Semi-quantitative \\
-    \midrule
-    Un-normalized & $0.85 \ (\pm 0.11)$ & $0.81 \ (\pm 0.17)$ & $0.84 \ (\pm 0.14)$ & $0.88 \ (\pm 0.12)$ & $0.27 \ (\pm 0.18)$ & $0.64 \ (\pm 0.24)$  \\
-    Normalized    & $0.92 \ (\pm 0.05)$ & $0.72 \ (\pm 0.32)$ & $0.92 \ (\pm 0.06)$ & $0.90 \ (\pm 0.10)$ & $0.28 \ (\pm 0.20)$ & $0.75 \ (\pm 0.20)$  \\
-    \bottomrule
-  \end{tabular}
-  }
-  \label{tab:r2}
-\end{table*}
-
 Parameter estimation of the quantification methods are related to fit a specific model to the \ac{dce}-\ac{mri} data.
@@
 
-\begin{table*}
-  \caption{\acs*{auc} for each individual pharmacokinetic parameter using a \acs*{rf} classifier.}
-  \centering
-  \resizebox{\columnwidth}{!}{
-  \begin{tabular}{l c c}
-    \toprule
-    \textbf{Features} & Un-normalized data & Normalized data \\
-    \midrule
-    \textbf{Brix model} & & \\
-    \quad $A$         & 0.54 & 0.55 \\
-    \quad $k_{el}$    & 0.51 & 0.50 \\
-    \quad $k_{ep}$    & 0.55 & 0.58 \\
-    \textbf{Hoffmann model} & & \\
-    \quad $A$         & 0.52 & 0.51 \\
-    \quad $k_{el}$    & 0.55 & 0.53 \\
-    \quad $k_{ep}$    & 0.55 & 0.54 \\
-    \textbf{Tofts model with population \ac{aif}} & & \\
-    \quad $K_{trans}$ & 0.56 & 0.55 \\
-    \quad $k_{ep}$     & 0.49 & 0.49 \\
-    \quad $v_{p}$     & 0.53 & 0.50 \\
-    \textbf{Tofts model with patient \ac{aif}} & & \\
-    \quad $K_{trans}$ & 0.57 & 0.57 \\
-    \quad $k_{ep}$     & 0.51 & 0.53 \\
-    \quad $v_{p}$     & 0.53 & 0.55 \\
-    \textbf{\ac{pun} model} & & \\
-    \quad $a_0$       & 0.52 & 0.53 \\
-    \quad $r$         & 0.55 & 0.57 \\
-    \quad $\beta$     & 0.53 & 0.55 \\
-    \textbf{Semi-quantitative analysis} & & \\
-    \quad wash-in     & 0.57 & 0.53 \\
-    \quad wash-out    & 0.52 & 0.49 \\
-    \quad IAUC        & 0.51 & 0.51 \\
-    \quad $\tau$      & 0.57 & 0.54 \\
-    \quad $S_M - S_0$ & 0.56 & 0.53 \\
-    \bottomrule
-  \end{tabular}
-  }
-  \label{tab:resfeats}
-\end{table*}
-
-\begin{figure*}
-  \centering
-  \hspace*{\fill}
-  \subfigure[Without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/rf.pdf}} \hfill
-  \subfigure[With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/rf.pdf}}
-  \hspace*{\fill}
-  \caption{\acs*{roc} analysis using a \acs*{rf} classifier with and without normalization \ac{dce}-\ac{mri} data for different pharmacokinetic models.}
-  \label{fig:normpharmarf}
-\end{figure*}
-
 To study the potential benefit of our normalization, \ac{cap} are detected at a voxel level using pharmacokinetic parameters estimated from un-normalized and normalized \ac{dce}-\ac{mri} data.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{03_experiments/figures/rf.pdf}
-  \caption{\acs*{roc} analysis using the entire \ac{dce}-\ac{mri} signal with and without normalization in conjunction with a \acs*{rf} classifier.}
-  \label{fig:rfnormdcesignal}
-\end{figure}
-
 As stated in the introduction, the quantification methods are extracting a set of parameters characterizing the enhancement \ac{dce}-\ac{mri} signal.

### 2016-09-01 08_figures/figures.tex
Put the elements into place

\newpage

\section{Figures}

\listoffigures

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{02_methods/figures/t2w.pdf}
  \caption{Illustration of the inter-patient variations in 17 different patients, using the \acs*{pdf} representation.}
  \label{fig:t2w}
\end{figure}

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
  \hspace*{\fill}
  \\
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
  \hspace*{\fill}
  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\alpha_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
  \label{fig:heatmap}
\end{figure*}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{02_methods/figures/estimator.pdf}
  \caption{Illustration of the estimator found using the shortest-path through the graph.}
  \label{fig:estimator}
\end{figure}

\begin{figure*}[h]
  \centering
  \hspace*{\fill}
  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse.pdf}} \hfill
  \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the correction of the time offset and the data dispersion.}
  \label{fig:curveal}
\end{figure*}

\begin{figure*}[h]
  \centering
  \hspace*{\fill}
  \subfigure[Original image.]{\label{fig:org}\includegraphics[width=.3\textwidth]{02_methods/figures/original.pdf}} \hfill
  \subfigure[Candidates region after clustering.]{\label{fig:cand}\includegraphics[width=.3\textwidth]{02_methods/figures/candidate.pdf}} \hfill
  \subfigure[Regions selected after applying the different criteria.]{\label{fig:final}\includegraphics[width=.3\textwidth]{02_methods/figures/aif.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the segmentation of the area used to determine the \acs*{aif}.}
  \label{fig:aif}
\end{figure*}

\begin{figure*}[h]
  \centering
  \hspace*{\fill}
  \subfigure[Without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/unormalized_methods_0.pdf}} \hfill
  \subfigure[With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/normalized_methods_0.pdf}}
  \hspace*{\fill}
  \caption{\acs*{roc} analysis using a \acs*{rf} classifier with and without normalization \ac{dce}-\ac{mri} data for different pharmacokinetic models.}
  \label{fig:normpharmarf}
\end{figure*}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{03_experiments/figures/full_signal_0.pdf}
  \caption{\acs*{roc} analysis using the entire \ac{dce}-\ac{mri} signal with and without normalization in conjunction with a \acs*{rf} classifier.}
  \label{fig:rfnormdcesignal}
\end{figure}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2016-09-01 01_introduction/introduction.tex
Add full title page

@@
 The paper is organized as follows:
+Section~\ref{sec:data} gives information about the dataset used and provided source code.
 Section~\ref{sec:norm} details our normalization strategy for \ac{dce}-\ac{mri} data.
 Quantitative and semi-quantitative methods are summarized in Sect.\,\ref{sec:stateart} with insights about their implementations.
-Section~\ref{sec:materials} gives information about the dataset used and provided source code.
 Experiments and results to answer the previous stated challenges are reported in Sect.\,\ref{sec:experiments} while discussed in Sect.\,\ref{sec:discussions}, followed by a concluding section.

### 2016-09-01 02_methods/methods.tex
Add full title page

@@
-\section{Methods}\label{sec:method}
+\section{Material and Methods}\label{sec:method}
+
+\subsection{\ac{mri} data}\label{sec:data}
+
+The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
+The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
+Aside of the \ac{mri} examination, these patients also have undergone a guided-biopsy.
+The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
+Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
+An experienced radiologist has segmented the prostate organ --- on \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
+
+A \SI{3}{\mm} slice fat-suppressed \ac{t2w} fast spin-echo sequence (\ac{tr}/\ac{te}/\ac{etl}: \SI{3400}{\ms}/\SI{85}{\ms}/13) is used to acquire images in sagittal and oblique coronal planes, the latter planes being orientated perpendicular or parallel to the prostate \ac{pz} – rectal wall axis.
+Three-dimensional \ac{t2w} fast spin-echo (\ac{tr}/\ac{te}/\ac{etl}: \SI{3600}{\ms}/\SI{143}{\ms}/109, slice thickness: \SI{1.25}{\mm}) images are then acquired in an oblique axial plane.
+The nominal matrix and \ac{fov} of the 3D \ac{t2w} fast spin-echo images are $320 \times 256$ and $280 \times 240$ mm\textsuperscript{2}, respectively, thereby affording sub-millimetric pixel resolution within the imaging plane.
+
+\ac{dce}-\ac{mri} is performed using a fat suppressed 3D T$_1$ VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
+A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
+
+These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using a linear interpolation.
+The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
+Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
+
+The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
+The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}~\citep{lemaitre2016github}.
+The data used for this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}~\citep{lemaitre2016dce}.
 

### 2016-09-01 03_experiments/experiments.tex
Add full title page

@@
-\section{Materials}\label{sec:materials}
+%\section{Materials}\label{sec:materials}
 
-\subsection{Data}\label{sec:data}
-
-The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
-The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
-Aside of the \ac{mri} examination, these patients also have undergone a guided-biopsy.
-The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
-Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
-An experienced radiologist has segmented the prostate organ --- on \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
-
-A \SI{3}{\mm} slice fat-suppressed \ac{t2w} fast spin-echo sequence (\ac{tr}/\ac{te}/\ac{etl}: \SI{3400}{\ms}/\SI{85}{\ms}/13) is used to acquire images in sagittal and oblique coronal planes, the latter planes being orientated perpendicular or parallel to the prostate \ac{pz} – rectal wall axis.
-Three-dimensional \ac{t2w} fast spin-echo (\ac{tr}/\ac{te}/\ac{etl}: \SI{3600}{\ms}/\SI{143}{\ms}/109, slice thickness: \SI{1.25}{\mm}) images are then acquired in an oblique axial plane.
-The nominal matrix and \ac{fov} of the 3D \ac{t2w} fast spin-echo images are $320 \times 256$ and $280 \times 240$ mm\textsuperscript{2}, respectively, thereby affording sub-millimetric pixel resolution within the imaging plane.
-
-\ac{dce}-\ac{mri} is performed using a fat suppressed 3D T$_1$ VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
-A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
-
-These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using a linear interpolation.
-The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
-Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
-The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
-
-\subsection{Implementation}
-
-The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}~\citep{lemaitre2016github}.
-The data used for this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}~\citep{lemaitre2016dce}.
-
-\section{Experiments and results}\label{sec:experiments}
+\section{Results}\label{sec:experiments}
 

### 2016-09-01 full_title.tex
Add full title page

--- 2016-08-08 main.tex
@@
-\documentclass[review]{elsarticle}
+\documentclass[review, 12pt]{elsarticle}
 
@@
 \modulolinenumbers[5]
+
+% Package to change into landscape
+\usepackage{pdflscape}
+
+% Package for the appendix
+%\usepackage[toc,page]{appendix}
+\usepackage[header,title]{appendix}
+
+% Package for table
+\usepackage{booktabs}
+
+% For some math expression
+\usepackage{amsmath}
+\usepackage{mathabx}
+\DeclareMathOperator*{\argmin}{arg\,min}
+
+% Package for SI units
+\usepackage{siunitx}
+
+% Package for figures
+\usepackage{epsf,graphicx}
+\usepackage{epstopdf}
+\usepackage{subfigure}
+
+% Package for pseudo algorithm
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\makeatletter
+\def\BState{\State\hskip-\ALG@thistlm}
+\makeatother
+
+% Define the operator of convolution
+\newcommand{\Conv}{\mathop{\scalebox{1.5}{\raisebox{-0.2ex}{$\ast$}}}}%
 
@@
 
-\journal{Medical Image Analysis}
+\journal{Journal of Magnetic Resonance Imaging}
 
@@
 %% Numbered
-%\bibliographystyle{00_files_system/model1-num-names}
+\bibliographystyle{00_files_system/model1-num-names}
 
@@
 %% Harvard
-\bibliographystyle{00_files_system/model2-names}\biboptions{authoryear}
+%\bibliographystyle{00_files_system/model2-names}\biboptions{authoryear}
 
 %% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{00_files_system/model3-num-names}
+%\usepackage{00_files_system/numcompress}\bibliographystyle{00_files_system/model3-num-names}
 
@@
 % Add authors and the different addresses
-\author[label1,label3]{Guillaume~Lema\^itre\corref{cor1}}
+\author[label1,label3]{Guillaume~Lema\^itre\corref{cor1}, MS}
 \ead{g.lemaitre58@gmail.com}
-\author[label3]{Robert~Mart\'i}
+\author[label3]{Robert~Mart\'i, PhD}
+\author[label1]{Mojdeh~Rastgoo, PhD}
+\author[label1]{Joan~Massich, PhD}
 %\ead{marly@eia.udg.edu}
-\author[label3]{Jordi~Freixenet}
+\author[label3]{Jordi~Freixenet, PhD}
 %\ead{jordif@eia.udg.edu}
-\author[label5]{Anke Meyer-Baese}
+\author[label5]{Anke Meyer-Baese, PhD}
 %\ead{ameyerbaese@fsu.edu}
-\author[label4]{Joan~C.~Vilanova}
+\author[label4]{Joan~C.~Vilanova, MD}
 %\ead{kvilanova@comg.cat}
-\author[label2]{Paul~M.~Walker}
+%\author[label2]{Paul~M.~Walker}
 %\ead{pwalker@u-bourgogne.fr}
-\author[label1,label6]{Fabrice~Meriaudeau}
+\author[label1,label6]{Fabrice~Meriaudeau, PhD}
 %\ead{fabrice.meriaudeau@u-bourgogne.fr}
 \address[label1]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, 12 rue de la Fonderie, 71200 Le Creusot, France}
-\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
+%\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
 \address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
@@
 \address[label6]{\scriptsize CISIR, Electrical \& Electronic Engineering Department, Universiti Teknologi Petronas, 32610 Seri Iskandar, Perak, Malaysia}
-\cortext[cor1]{Corresponding author.}
+\cortext[cor1]{Corresponding author: Guillaume Lema\^itre, 12 rue de la Fonderie, 71200 Le Creusot, +33761104782}
 
-% Start the abstract
 \begin{abstract}
-This template helps you to create a properly formatted \LaTeX\ manuscript.
+\begin{description}
+  \item[Acknowledgements] None.
+  \item[Grant support] Guillaume Lema\^itre is supported by the Generalitat de Catalunya (grant nb. FI-DGR2012) and partly by the Mediterranean Office for Youth (grant nb. 2011/018/06).
+  \item[Running title] All you need is a good normalization
+\end{description}
 \end{abstract}
-
-% Give the different keywords
-\begin{keyword}
-\acs*{dce}-\acs*{mri}\sep prostate cancer\sep normalization\sep classification\sep quantification
-\end{keyword}
 
@@
 
-% Reset all the acronyms
-\acresetall
-\linenumbers
-% Include now the different files
-\input{01_introduction/introduction}
-\input{02_methods/methods}
-\input{03_experiments/experiments}
-\input{04_discussions/discussions}
-\input{05_conclusions/conclusions}
+\end{document}
 
-% Include the bibliography
-\section*{References}
-
-\bibliography{00_files_system/literature}
-
-\end{document}
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2016-09-07 main.tex
Put the elements into place
Update abstract
Update keywords

@@
 \begin{abstract}
-\ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used to the design of new \ac{cad} systems.
+\Ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used to the design of new \ac{cad} systems.
 \ac{dce}-\ac{mri} is one of the modality regularly used in \ac{mpmri} \ac{cad} system.
@@
 \begin{keyword}
-\acs*{dce}-\acs*{mri}\sep prostate cancer\sep normalization\sep classification\sep quantification
+\acs*{dce}-\acs*{mri}\sep prostate cancer\sep normalization\sep classification
 \end{keyword}

### 2017-01-27 03_experiments/experiments.tex
Advance the correction

--- 2016-09-01 03_experiments/experiments.tex
@@
 
+\begin{table*}
+  \caption{Coefficient of determination $R^{2}$ (i.e., $\mu \ (\pm \sigma)$), while fitting data with the different quantification models.}
+  \centering
+  \resizebox{\columnwidth}{!}{
+  \begin{tabular}{lc c c c c c}
+    \toprule
+    Data type & Brix & Hoffmann & Tofts population \ac{aif} & Tofts patient \ac{aif} & \ac{pun} & Semi-quantitative \\
+    \midrule
+    Un-normalized & $0.85 \ (\pm 0.11)$ & $0.81 \ (\pm 0.17)$ & $0.84 \ (\pm 0.14)$ & $0.88 \ (\pm 0.12)$ & $0.27 \ (\pm 0.18)$ & $0.64 \ (\pm 0.24)$  \\
+    Normalized    & $0.92 \ (\pm 0.05)$ & $0.72 \ (\pm 0.32)$ & $0.92 \ (\pm 0.06)$ & $0.90 \ (\pm 0.10)$ & $0.28 \ (\pm 0.20)$ & $0.75 \ (\pm 0.20)$  \\
+    \bottomrule
+  \end{tabular}
+  }
+  \label{tab:r2}
+\end{table*}
+
 Parameter estimation of the quantification methods are related to fit a specific model to the \ac{dce}-\ac{mri} data.
-Therefore, this section report the goodness of fitting by computing the coefficient of determination $R^2$ such as in Eq.\,\eqref{eq:r2}
+Therefore, this section reports the goodness of fitting by computing the coefficient of determination $R^2$ such as in Eq.\,\eqref{eq:r2}
 
@@
 Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.
-Additionally, the proposed \ac{pun} model does not seem to fit well the data.
+Additionally, the proposed \ac{pun} model does not to fit well the data.
+After introspection of the fitted curves, the original model --- as
+formulated in Eq.\,\eqref{eq:pun} --- does not provide enough degrees
+of freedom to fit well the data. Additional parameters should be
+integrated in this model to control the translation and amplitude of
+the model to be fitted.
 Data normalization improves the coefficient $R^2$ for all the methods apart of the Hoffmann model.
@@
 
-\subsection{Detection of \acs*{cap} using pharmacokinetic parameters}
+% \subsection{Detection of \acs*{cap} using pharmacokinetic parameters}
+
+\subsection{\acs*{cap} detection using pharcokinetic,
+  semi-quantitative, and entire enhanced signal}
+
+\begin{table*}
+  \caption{\acs*{auc} (i.e., $\mu \ (\pm \sigma)$) for each individual pharmacokinetic parameter using a \acs*{rf} classifier.}
+  \centering
+  \resizebox{\columnwidth}{!}{
+  \begin{tabular}{l c c}
+    \toprule
+    \textbf{Features} & Un-normalized data & Normalized data \\
+    \midrule
+    \textbf{Brix model} & & \\
+    \quad $A$         & $0.540\ (\pm 0.069)$ & $0.555\ (\pm 0.080)$ \\
+    \quad $k_{el}$    & $0.549\ (\pm 0.062)$ & $0.577\ (\pm 0.093)$ \\
+    \quad $k_{ep}$    & $0.506\ (\pm 0.032)$ & $0.497\ (\pm 0.019)$ \\
+    \textbf{Hoffmann model} & & \\
+    \quad $A$         & $0.516\ (\pm 0.020)$ & $0.508\ (\pm 0.031)$ \\
+    \quad $k_{el}$    & $0.545\ (\pm 0.066)$ & $0.529\ (\pm 0.065)$ \\
+    \quad $k_{ep}$    & $0.550\ (\pm 0.063)$ & $0.545\ (\pm 0.060)$ \\
+    \textbf{Tofts model with population \ac{aif}} & & \\
+    \quad $K_{trans}$ & $0.556\ (\pm 0.086)$ & $0.565\ (\pm 0.097)$ \\
+    \quad $k_{ep}$    & $0.506\ (\pm 0.026)$ & $0.528\ (\pm 0.038)$ \\
+    \quad $v_{p}$     & $0.533\ (\pm 0.064)$ & $0.548\ (\pm 0.082)$ \\
+    \textbf{Tofts model with patient \ac{aif}} & & \\
+    \quad $K_{trans}$ & $0.563\ (\pm 0.077)$ & $0.548\ (\pm 0.060)$ \\
+    \quad $k_{ep}$    & $0.492\ (\pm 0.025)$ & $0.491\ (\pm 0.020)$ \\
+    \quad $v_{p}$     & $0.530\ (\pm 0.069)$ & $0.495\ (\pm 0.033)$ \\
+    \textbf{\ac{pun} model} & & \\
+    \quad $a_0$       & $0.521\ (\pm 0.040)$ & $0.530\ (\pm 0.045)$ \\
+    \quad $r$         & $0.550\ (\pm 0.085)$ & $0.573\ (\pm 0.097)$ \\
+    \quad $\beta$     & $0.531\ (\pm 0.051)$ & $0.549\ (\pm 0.068)$ \\
+    \textbf{Semi-quantitative analysis} & & \\
+    \quad wash-in     & $0.587\ (\pm 0.107)$ & $0.533\ (\pm 0.032)$ \\
+    \quad wash-out    & $0.516\ (\pm 0.037)$ & $0.486\ (\pm 0.035)$ \\
+    \quad IAUC        & $0.506\ (\pm 0.048)$ & $0.513\ (\pm 0.032)$ \\
+    \quad $\tau$      & $0.565\ (\pm 0.104)$ & $0.537\ (\pm 0.089)$ \\
+    \quad $S_M - S_0$ & $0.560\ (\pm 0.083)$ & $0.532\ (\pm 0.029)$ \\
+    \bottomrule
+  \end{tabular}
+  }
+  \label{tab:resfeats}
+\end{table*}
+
+\begin{figure*}
+  \centering
+  \hspace*{\fill}
+  \subfigure[Quantiative model without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/unormalized_methods_0.pdf}} \hfill
+  \subfigure[Quantitative model With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/normalized_methods_0.pdf}}
+  \hspace*{\fill}
+  \hspace*{\fill}
+  \subfigure[Entire enhanced \acs*{dce} signal classification.]{\label{fig:rfnormdcesignal}\includegraphics[width=.49\textwidth]{03_experiments/figures/full_signal_0.pdf}}
+  \hspace*{\fill}
+  \caption{\acs*{roc} analysis using a \acs*{rf} classifier with and
+    without normalization using different approaches: \protect\subref{fig:rfpharmaunorm} -
+    \protect\subref{fig:rfpharmanorm} pharmacokinetic and
+    semi-quantitative models without and with normalization,
+    respectively; \protect\subref{fig:rfnormdcesignal} entire enhanced
+  \acs*{dce}-\acs*{mri} signal.}
+  \label{fig:normpharmarf}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.\linewidth]{03_experiments/figures/wilcoxon.pdf}
+  \caption{Wilcoxon signed-ranked test to compare each pair of
+    classifiers. The annotation in the matrix corresponds to the
+    p-values ($p$). $p < 0.05$ indicates that a pair of classifiers
+    are significantly different, consequently the classifier with the
+    highest \acs*{auc} significantly outperforms the other
+    one. In the co-occurrence matrix, {\color{blue}blue} cells
+    correspond to lower $p$ while {\color{red} red} cells are
+    representing greater $p$.}
+  \label{fig:wilcoxon}
+\end{figure}
 
@@
 The reasons behind the decrease of the \ac{auc} might be related to: (i) a poor fitting as discussed in Sect.\,\ref{sec:fit} (cf., Hoffmann model) and (ii) a small number of patients while estimating some parameters (cf., Tofts model).
-The best classification performance are obtained using the semi-quantitative approach with an \ac{auc} of 0.655.
+The best classification performance are obtained using the semi-quantitative approach with an \ac{auc} of $0.655$.
 
-\subsection{Classification of the entire enhanced \acs*{dce}-\acs*{mri} signal}
+%\subsection{Classification of the entire enhanced \acs*{dce}-\acs*{mri} signal}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=1.\linewidth]{03_experiments/figures/plot_auc_by_zones.pdf}
+  \caption{Comparison of the distribution of the \acs*{auc} score for
+    each prostate zone, with and without normalization.}
+  \label{fig:boxplot}
+\end{figure*}
 
@@
 The \ac{roc} analysis and \ac{auc} are reported in Fig.\,\ref{fig:rfnormdcesignal}.
-Classification without normalization lead to the worst performance, with an \ac{auc} of 0.568.
-However, data normalization in conjunction with the use of the whole \ac{dce}-\ac{mri} signal is the strategy which outperforms all others, with an \ac{auc} of 0.666.
+Classification without normalization lead to the worst performance, with an \ac{auc} of $0.568$.
+However, data normalization in conjunction with the use of the entire \ac{dce}-\ac{mri} signal is the strategy which outperforms others, with an \ac{auc} of $0.666$.
+Comparable outcomes are visible while analyzing the \ac{auc}
+distributions scores for each prostate zone. The \ac{auc} score
+related to \ac{cap} in \ac{cg} improves using normalized data, for
+most of the models.
 

### 2017-01-27 04_discussions/discussions.tex
Advance the correction

@@
 
-The best classification performance is reached by normalizing the \ac{dce}-\ac{mri} data and use the whole enhanced signal as feature, emphasizing the fact that a loss of information while extracting quantitative parameters.
-Furthermore, this normalization is a less complex process than all quantification methods.
-However, this strategy suffers from one drawback: the training time of the \ac{rf} classifier increases since that from 3 to 5 features, the feature space becomes a 40 dimensions space.
+The best classification performance is reached by normalizing the \ac{dce}-\ac{mri} data and use the entire enhanced signal as feature, emphasizing the fact that a \emph{loss of information} while extracting quantitative parameters.
+Furthermore, this normalization is a less complex process than all
+quantification methods and significantly improves the classification
+performance of the semi-quantitative approach ($p=0.001$) proposed by
+\citeauthor{huisman2001accurate}.
+Additionally, our normalization improves the \ac{auc} score related to
+the detection of \ac{cap} in \ac{cg}, also known to be the most
+challenging cases in the diagnosis of \ac{cap}.
+
+However, using the entire enhanced signal in conjunction with the
+normalization suffers from one drawback: the training time of the
+\ac{rf} classifier increases; instead of using $3$ to $5$ features, the
+feature space becomes a $40$ dimensions space. The extraction of the
+semi-quantitative parameters leads to a comparable classification performance ---
+$0.655$ vs. $0.666$ --- and should be chosen as the alternative method to
+consider if the number of feature in the classification is
+critical. Despite this fact, the benefit of the normalization method
+has been shown for both methods.
 
@@
 Generalizing the results of this study on a larger dataset acquired from different commercial systems have to be considered to study the robustness of the proposed approach.
+Additionally, our method being non-parametric should provide an
+adequate framework to process \ac{dce} data from different
+institutions, scanners with different settings.
 

### 2017-01-27 01_introduction/introduction.tex
make english correction

@@
 
-\Ac{cap} is the second most frequently diagnosed men cancer, accounting for 899,000 cases leading to 258,100 deaths~\citep{ferlay2010estimates}.
+\Ac{cap} is the second most frequently diagnosed cancer in men,
+accounting for 899,000 cases and leading to 258,100 deaths per year~\citep{ferlay2010estimates}.
 As highlighted by the PI-RADS Steering Committee, the two main challenges to be addressed are~\citep{weinreb2016pi}:
-(i) the improvement of detecting clinically significant \ac{cap} and
-(ii) an increase of the confidence in benign or dormant cases, avoiding unnecessary invasive medical exams.
+(i) improving the detection of clinically significant \ac{cap} and
+(ii) increasing confidence in benign or dormant cases and therefore avoiding unnecessary invasive medical exams.
 In this regard, \ac{mpmri} is frequently used to build robust \ac{cad} systems to detect, localize, and grade \ac{cap}.
@@
 In \ac{dce}-\ac{mri}, a contrast media is injected intravenously and a set of images is acquired over time.
-Consequently, each voxel in an image corresponds to a dynamic signal which is related to both contrast agent concentration and the vascular properties of the tissue.
-Therefore, changes of the enhanced signal allows to discriminate healthy from \ac{cap} tissues.
+Consequently, each voxel in an image corresponds to a dynamic signal that is related to both contrast agent concentration and the vascular properties of the tissue.
+Therefore, changes in the enhanced signal allows for the
+discrimination of healthy tissues from \ac{cap} tissues.
 In fact, these properties are automatically extracted using quantitative or semi-quantitative approaches~\citep{lemaitre2015computer}.
@@
 \emph{Quantitative} approaches uses pharmacokinetic modelling based on a bicompartment model, namely Brix~\citep{brix1991pharmacokinetic} and Tofts~\citep{tofts1995quantitative} models.
-The parameters of the Brix model are inferred assuming a linear relationship between the media concentration and the \ac{mri} signal intensity.
-This assumption has shown, however, to lead to inaccurately estimate the pharmacokinetic parameters~\citep{heilmann2006determination}.
-In the contrary, Tofts model requires a conversion from \ac{mri} signal intensity to concentration, which becomes a non-linear relationship using specific equation of \ac{mri} sequences (e.g., FLASH sequence).
-Tofts modelling suffers, however, from a higher complexity~\citep{gliozzi2011phenomenological}.
-Indeed, the conversion using the non-linear approach requires to acquire a T$_1$ map which is not always possible during clinical examination.
+The parameters of the Brix model are inferred by assuming a linear relationship between the media concentration and the \ac{mri} signal intensity.
+However, this assumption has been shown to lead to inaccurate
+estimations of the pharmacokinetic parameters~\citep{heilmann2006determination}.
+In contrast, the Tofts model requires the conversion of \ac{mri}
+signal intensity to concentration, which becomes a non-linear
+relationship using a specific equation of \ac{mri} sequences (e.g., FLASH sequence).
+Tofts modeling, however, is highly complex~\citep{gliozzi2011phenomenological}.
+Achieving the conversion using the non-linear approach requires the
+acquisition of a T$_1$ map which is not always possible during clinical examination.
 Additionally, the parameter calculation requires the \ac{aif} which is challenging to measure and can also lead to an inaccurate estimation.
 
-\emph{Semi-quantitative} approaches are rather mathematical than pharmacokinetic modelling since no pharmacokinetic assumption regarding the relation between the \ac{mri} signal and the contrast agent are made~\citep{huisman2001accurate,gliozzi2011phenomenological}.
-These methods offer the advantages to not require any knowledge about the \ac{mri} sequence nor any conversion from signal intensity to concentration.
-However, they present some limitations: the heuristic approach proposed by \citeauthor{huisman2001accurate} requires an initial estimate of the noise standard deviation of the signal as well as some manual tuning.
+\emph{Semi-quantitative} approaches are mathematical rather than pharmacokinetic because no pharmacokinetic assumptions regarding the relationship between the \ac{mri} signal and the contrast agent are made~\citep{huisman2001accurate,gliozzi2011phenomenological}.
+These methods are advantageous because they do not require any knowledge of the \ac{mri} sequence or any conversion from signal intensity to concentration.
+However, they present some limitations: the heuristic approach
+proposed by \citeauthor{huisman2001accurate} requires an initial
+estimate of the standard deviation of the signal noise and some manual tuning.
 
-Nevertheless, all presented methods suffer from two major drawbacks:
+Nevertheless, all of the presented methods suffer from the following two major drawbacks:
 (i) inter-patient variability and (ii) loss of information.
-The inter-patient variability is mainly due to the acquisition process and consequently leads to generalization issue while applying a machine learning algorithm.
+The inter-patient variability is mainly due to the acquisition process
+and consequently leads to generalization issues in applying a machine learning algorithm.
 All previous methods extract few discriminative parameters to describe the \ac{dce}-\ac{mri} signal which might lead to a loss of information.
@@
 In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
-The benefit and simplicity of our approach will be shown by classifying the whole normalized \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
+The benefit and simplicity of our approach will be demonstrated by
+classifying the whole normalized \ac{dce}-\ac{mri} signal and
+comparing it with state-of-the-art quantitative and semi-quantitative methods.
 Additionally, we will show that using this normalization approach in conjunction with the quantitative methods improves the classification performance of most of the models.
-We also propose a new clustering-based method to segment enhanced signals from the arteries, later used to estimate an \ac{aif} as well as an alternative approach to estimate the parameters of the semi-quantitative model proposed by~\cite{huisman2001accurate}.
+We also propose a new clustering-based method to discern enhanced
+signals from the arteries that can, later be used to estimate an
+\ac{aif} and provide an alternative approach to estimate the parameters of the semi-quantitative model proposed by~\cite{huisman2001accurate}.
 
@@
 The paper is organized as follows:
-Section~\ref{sec:data} gives information about the dataset used and provided source code.
-Section~\ref{sec:norm} details our normalization strategy for \ac{dce}-\ac{mri} data.
+Section~\ref{sec:norm} details our normalization strategy for the \ac{dce}-\ac{mri} data.
 Quantitative and semi-quantitative methods are summarized in Sect.\,\ref{sec:stateart} with insights about their implementations.
-Experiments and results to answer the previous stated challenges are reported in Sect.\,\ref{sec:experiments} while discussed in Sect.\,\ref{sec:discussions}, followed by a concluding section.
+Section~\ref{sec:materials} provides information about the dataset
+used and the provided source code.
+Experiments and results that address the previously stated challenges
+are reported in Sect.\,\ref{sec:experiments} and discussed in Sect.\,\ref{sec:discussions}, followed by a concluding section.
 %Section~\ref{sec:methods} outlines our normalization strategy (Section~\ref{sec:norm}) as well as specificity regarding the state-of-the-art methods used for comparison (Section~\ref{sec:stateart}).

### 2017-01-27 02_methods/methods.tex
Advance the correction
make english correction

--- 2016-08-31 02_methods/methods.tex
@@
   \includegraphics[width=0.7\linewidth]{02_methods/figures/t2w.pdf}
-  \caption{Illustration of the inter-patient variations in 17 different patients, using the \acs*{pdf} representation.}
+  \caption{Illustration of the inter-patient variations in 17
+    different patients in \acs*{t2w}-\acs*{mri}, using the \acs*{pdf} representation.}
   \label{fig:t2w}
@@
 
-In this work, we propose a method to normalize \ac{dce}-\ac{mri} prostate data to reduce inter-patient variations, although it can be applied to any \ac{dce}-\ac{mri} sequences.
+In this work, we propose a method to normalize \ac{dce}-\ac{mri}
+prostate data to reduce inter-patient variations, although this method can be applied to any \ac{dce}-\ac{mri} sequences.
 In \ac{t2w}-\ac{mri}, these variations are characterized by a shift and a scaling of the intensities as illustrated by the intensity \ac{pdf} in Fig.\,\ref{fig:t2w}.
-Therefore, these variations can be corrected using a $z$-score approach--- i.e., normalizing the data by subtracting the mean and dividing by the standard deviation ---assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
+Therefore, these variations can be corrected using a $z$-score approach,--- i.e., normalizing the data by subtracting the mean and dividing by the standard deviation ---assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
 
@@
 
-In \ac{dce}-\ac{mri}, the intensity \ac{pdf} of prostate gland does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathhist}.
+In \ac{dce}-\ac{mri}, the intensity \ac{pdf} of the prostate gland does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathhist}.
 Indeed, the inter-patient variations are more complex due to the temporal acquisition.
-A better representation to observe these variations is to represent the intensity \ac{pdf} of the prostate gland over time--- requiring to segment the prostate ---using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
-Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
-(i) intensity offsets $\Delta_i$ of the \ac{pdf} peak,
-(ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
-(iii) a change of scale $\alpha_i$ related to the signal enhancement.
-Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequences rather than for each independent sequence.
+A better means of observing these variations is to represent the
+intensity \ac{pdf} of the prostate gland over time---, requiring
+segmentation of the prostate ---using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
+By analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
+(i) intensity offsets ($\Delta_i$) of the \ac{pdf} peak,
+(ii) a time offset ($\Delta_t$) depending on the contrast agent arrival, and
+(iii) a change of scale ($\alpha_i$) related to the signal enhancement.
+Therefore, our normalization method should attenuate all of these variations and be performed globally across the different time sequences rather than for each independent sequence.
 
@@
 
-Before to standardize each sequence, the first step of the normalization is to cancel the intensity specific at each patient, occurring due to the media injection.
-As previously mentioned, the intensity \ac{pdf} does not always follow either a Rician or a Gaussian distribution over time, in \ac{dce}-\ac{mri}.
+Before standardizing each sequence, the first step of the
+normalization process is to cancel the intensity specific at each
+patient, which occurs due to the media injection.
+As previously mentioned, the intensity \ac{pdf} does not always follow a Rician or a Gaussian distribution over time, in \ac{dce}-\ac{mri}.
 Therefore, the mean of these distributions cannot be used as a potential estimate for these offsets.
 Additionally, these offsets should be characterized by a smooth transition between series over time.
-Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{subfig:pathhist}, the offsets correspond to the boundary splitting the heatmap in two partitions such that they are as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
-Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar--- i.e., the probability for a given time and pixel intensity---of the heatmap as a node and connecting each pair of bars by an edge.
-The edge weight $w_{ij}$ between two nodes $i$ and $j$ corresponding to two pixels at position $(x_i, y_i)$ and $(x_j, y_j)$, respectively, is defined as in Eq.\,\eqref{eq:weight}:
+Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{subfig:pathhist}, the offsets correspond to the boundary splitting, the heatmap into two partitions such that they are as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
+Given the heatmap, a directed weighted graph
+$\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each
+bar---, i.e., the probability for a given time and pixel intensity---,
+of the heatmap as a node and connecting each pair of bars by an edge.
+The edge weight $w_{ij}$ between two nodes $i$ and $j$ corresponds to
+two pixels at positions $(x_i, y_i)$ and $(x_j, y_j)$, respectively,
+is defined as in Eq.\,\eqref{eq:weight}, as follows:
 
@@
 
-\noindent where $H$ is the heatmap, $\alpha$ is a smoothing parameter controlling the partitioning.
+\noindent where $H$ is the heatmap, and $\alpha$ is a smoothing
+parameter controlling for the partitioning.
 
 Therefore, these offsets related to $\Delta_i$ are estimated by finding the shortest-path to cross the graph using Dijkstra's algorithm.
-The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
-To ensure a robust estimation of these offsets, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
+The entry and exiting nodes are set to be the bin with the maximum
+probability for the first value in the \ac{dce}-\ac{mri} series and
+the bin corresponding to the median value for the last value of the \ac{dce}-\ac{mri} series, respectively.
+To ensure a robust estimation of these offsets, the process of finding the shortest-path is repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
 The procedure is stopped once the offset found does not change.
-In general, this process is not repeated more than 3 iterations.
+In general, this process is not repeated more than 3 times.
 The parameter $\alpha$ is set to $0.9$, empirically.
-Figure~\ref{fig:estimator} illustrates the final estimation of the offsets $\Delta_i$ (i.e., red landmark) found for each \ac{dce}-\ac{mri} serie.
+Figure~\ref{fig:estimator} illustrates the final estimation of the
+offsets, $\Delta_i$ (i.e., red landmark), found for each value of the \ac{dce}-\ac{mri} series.
 Therefore, each intensity offset is subtracted for each \ac{dce}-\ac{mri}.
@@
   \hspace*{\fill}
-  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse.pdf}} \hfill
+  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.44\textwidth]{02_methods/figures/rmse.pdf}} \hfill
   \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
@@
 
-The next variations to correct are the time offset $\Delta_t$ and the data dispersion $\sigma_i$.
-By computing the \ac{rmse} of the intensities for each \ac{dce}-\ac{mri} serie, one can observe these two variations as shown in Fig.\,\ref{fig:rmse}.
-Therefore, to correct these variations, we propose to register each patient \ac{rmse} to a mean model which corresponds to the mean of all patients \ac{rmse}.
-The parametric model to perform the registration is formulated as in Eq.\,\eqref{eq:model}:
+The next variations to correct are the time offset, $\Delta_t$, and the data dispersion, $\sigma_i$.
+By computing the \ac{rmse} of the intensities for each value of the \ac{dce}-\ac{mri} series, one can observe these two variations as shown in Fig.\,\ref{fig:rmse}.
+Therefore, to correct these variations, we propose the registration of
+each patient \ac{rmse} to a mean model that corresponds to the mean of
+all patients' \ac{rmse} values.
+The parametric model required to perform the registration is
+formulated in Eq.\,\eqref{eq:model}, as follows:
 
@@
 
-\noindent where $\alpha$ and $\tau$ are the two parameters handling the time offset $\Delta_i$ and global scale $\sigma_i$, respectively, $f(\cdot)$ is the \ac{rmse} function define as:
+\noindent where $\alpha$ and $\tau$ are the two parameters handling
+the time offset $\Delta_i$ and the global scale $\sigma_i$,
+respectively, $f(\cdot)$ is the \ac{rmse} function defined as follows:
 
@@
 
-\noindent where $x(t)_n$ is the shifted intensity of a sample from a specific \ac{dce}-\ac{mri} serie at time $t$ from a total number of $N$ samples.
+\noindent where $x(t)_n$ is the shifted intensity of a sample from a
+specific \ac{dce}-\ac{mri} series value at time $t$ from a total number of $N$ samples.
 
-Therefore the registration problem is equivalent to:
+Therefore, the registration problem is equivalent to:
 
@@
 
-\noindent where $\mu(\cdot)$ is the mean model, $N$ is the number of \ac{dce}-\ac{mri} serie.
+\noindent where $\mu(\cdot)$ is the mean model and, $N$ is the number
+of values in the \ac{dce}-\ac{mri} series.
 
-Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
-Once all these parameters have been inferred, the data are shifted as well as scaled.
+An illustration of the correction applied to each \ac{rmse} of the patients is shown in Fig.\,\ref{fig:rmseal}.
+Once all of these parameters have been determined, the data are shifted and scaled.
 
-The resulting normalized data can be used into two fashions: (i) each normalized signal can be used as a whole to determine whether the corresponding voxel is healthy or cancerous or (ii) the normalized data can be fitted using a quantitative method, as presented in the next section.
+The resulting normalized data can be used into two ways: (i) each
+normalized signal can be used as a whole to determine if the corresponding voxel is healthy or cancerous or (ii) the normalized data can be fitted using a quantitative method, as presented in the next section.
 %However, for the second strategy, this is necessary to apply common intensity offsets such that the data follow a shape as expected by the different quantitative models.
@@
 
-In this section, we summarize the different methods which have been used for the quantification of \ac{dce}-\ac{mri} for \ac{cap} detection~\citep{lemaitre2015computer} and which will be used for comparison in this work.
+In this section, we summarize the different methods that have been
+used for the quantification of \ac{dce}-\ac{mri} for \ac{cap}
+detection~\citep{lemaitre2015computer} and will be used for comparison in this work.
 Furthermore, we would like to emphasize the following additional contributions for this section: (i) a novel automatic \ac{aif} estimation algorithm based on clustering and (ii) a simplified semi-quantitative method using constrained optimization.
@@
 In the Brix model~\citep{brix1991pharmacokinetic}, the \ac{mri} signal intensity is assumed to be proportional to the media concentration.
-Therefore, the model is expressed as in Eq.\,\eqref{eq:brix}:
+Therefore, the model is expressed as shown in Eq.\,\eqref{eq:brix}, as
+follows:
 
@@
 \noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at time $t$ and the average pre-contrast \ac{mri} signal intensity, respectively; $A$, $k_{el}$, and $k_{ep}$ are the constant proportional to the transfer constant, the diffusion rate constant, and the rate constant, respectively.
-Additionally, $t'$ is set such that $0 \leq t \leq \tau$, $t' = t$ and afterwards while $t > \tau$, $t' = \tau$.
+Additionally, $t'$ is set such that $0 \leq t \leq \tau$, $t' = t$ and
+so forth while $t > \tau$, $t' = \tau$.
 
-\citeauthor{hoffmann1995pharmacokinetic} proposed a similar model as expressed in Eq.\,\eqref{eq:hoffmann}, which derive from the Brix model:
+\citeauthor{hoffmann1995pharmacokinetic} proposed a similar model,
+expressed in Eq.\,\eqref{eq:hoffmann}, which is derived from the Brix model:
 
@@
 
-\noindent in which the constant $A$ is redefined by isolating the parameter $\tau$.
+\noindent where the constant $A$ is redefined by isolating the parameter $\tau$.
 
-The parameters $A$, $k_{el}$, and $k_{ep}$ are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
+The parameters $A$, $k_{el}$, and $k_{ep}$ are estimated by fitting
+the model using non-linear least-squares optimization solved with
+Levenberg-Marquardt algorithm.
 
@@
 
-The extended Tofts model is formulated as in Eq.\,\eqref{eq:exttofts}:
+The extended Tofts model is formulated as shown in
+Eq.\,\eqref{eq:exttofts}, as follows:
 
@@
 
-Therefore, Tofts model requires to:
-(i) detect candidate voxels from the femoral or iliac arteries and estimate a patient-based \ac{aif} signal,
-(ii) convert the \ac{mri} signal intensity (i.e., \ac{aif} and dynamic signal) to a concentration, and
-(iii) in the case of a population-based \ac{aif}, estimate an \ac{aif} signal.
+Therefore, the Tofts model requires:
+(i) detection of the candidate voxels from the femoral or iliac
+arteries and an estimation of a patient-based \ac{aif} signal,
+(ii) conversion of  the \ac{mri} signal intensity (i.e., \ac{aif} and dynamic signal) to a concentration, and
+(iii) in the case of a population-based \ac{aif}, an estimation of an \ac{aif} signal.
 
@@
   \item[Segmentation of artery voxels and patient-based \ac{aif} estimation] The \ac{aif} signal from \ac{dce}-\ac{mri} can be manually estimated by selecting the most-enhanced voxels from the femoral or iliac arteries~\citep{meng2010comparison}.
-    Few methods have been proposed to address the automated extraction of \ac{aif} signal.
-    \citeauthor{chen2008automatic} filtered successively the possible candidates to be considered as \ac{aif} such that~\citep{chen2008automatic}:
-    (i) dynamic signals with small peak and voxels with a small wash-in are rejected by thresholding,
-    (ii) a blob detector is used and large enough regions are kept, and
+    Few methods have been proposed to address the automated extraction
+    of the \ac{aif} signal.
+    \citeauthor{chen2008automatic} successively filtered the possible
+    candidates to be considered as the \ac{aif} such that~\citep{chen2008automatic}:
+    (i) dynamic signals with a small peak and voxels with a small wash-in are rejected by thresholding,
+    (ii) a blob detector is used and large enough regions are maintained, and
     (iii) circular and cylindricality criteria are used to reject the false positives.
-    \citeauthor{zhu2011automated} proposed an iterative method selecting voxels which best fit a gamma variate function~\citep{zhu2011automated}.
-    However, it requires to compute first and second derivatives as well as maximum curvature points.
-    \citeauthor{shanbhag2012generalized} proposed a 4-steps algorithm~\citep{shanbhag2012generalized,fennessy2015quantitative}:
-    (i) remove slices with artefacts and find the best slices based on intrinsic anatomic landmarks and enhancement characteristics,
+    \citeauthor{zhu2011automated} proposed an iterative method that
+    involves the selection of voxels that best fit a gamma variate function~\citep{zhu2011automated}.
+    However, this method requires the computation of the first and
+    second derivatives as well as the maximum curvature points.
+    \citeauthor{shanbhag2012generalized} proposed the following 4-step algorithm~\citep{shanbhag2012generalized,fennessy2015quantitative}:
+    (i) remove the slices with artifacts and find the best slices based on intrinsic anatomic landmarks and enhancement characteristics,
     (ii) find the voxel candidates using the maximum enhanced voxels and a multi-label maximum entropy based thresholding algorithm,
-    (iii) exclude region next to the endorectal coil, and
-    (iv) select the best 5 candidates which meet enhancement characteristics and that are correlated.
+    (iii) exclude the region next to the endorectal coil, and
+    (iv) select the best 5 candidates that meet the enhancement characteristics and are correlated.
 
-    All the above methods are rather complex and thus we propose a simpler method which is based on the following reasonable assumptions:
+    All the above methods are rather complex, therefore,  we propose a simpler method that is based on the following reasonable assumptions:
     (i) all possible \ac{aif} signal candidates should have a similar shape,
-    (ii) a high enhancement, and
+    (ii) they should all have high enhancement, and
     (iii) the arteries should be almost round and within a size range.
@@
     Finally, regions with an eccentricity smaller than $0.5$ and an area in the range of $[100, 400]$ voxels are kept.
-    Additionally, to remove voxels contaminated by partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\citep{schabel2008uncertainty} and the average signal is computed.
+    Additionally, to remove voxels contaminated by the partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\citep{schabel2008uncertainty} and the average signal is computed.
     A summary of the different segmentation steps is presented in Fig.\,\ref{fig:aif}.
-    \item[Conversion of \ac{mri} signal intensity to concentration] To estimate the free parameters of the Tofts model (see Eq.\,\eqref{eq:exttofts}), the concentration $C_t(t)$ and $C_p(t)$ need to be computed from the \ac{mri} signal intensity and the \ac{aif} signal, respectively.
+    \item[Conversion of \ac{mri} signal intensity to concentration] To estimate the free parameters of the Tofts model (see Eq.\,\eqref{eq:exttofts}), the concentrations $C_t(t)$ and $C_p(t)$ need to be computed from the \ac{mri} signal intensity and the \ac{aif} signal, respectively.
       This conversion is based on the equation of the FLASH sequence\textemdash see~\ref{app:signaltoconc} for details\textemdash and is formulated as in Eq.\,\eqref{eq:conv}:
@@
       \end{equation}
-      \noindent where $s(t)$ is the \ac{mri} signal, $S_0$ is the \ac{mri} signal prior to the injection of the contrast media, $\alpha$ is the flip angle, $TR$ is the \acf{tr}, $R_{10}$ is the pre-contrast tissue relaxation time also equal to $\frac{1}{T_{10}}$, and $r_1$ is the relaxitivity coefficient of the contrast agent.
+      \noindent where $s(t)$ is the \ac{mri} signal, $S_0$ is the \ac{mri} signal prior to the injection of the contrast media, $\alpha$ is the flip angle, $TR$ is the \acf{tr}, $R_{10}$ is the pre-contrast tissue relaxation time also equal to $\frac{1}{T_{10}}$, and $r_1$ is the relaxivity coefficient of the contrast agent.
 
@@
       However, this modality is not part of the clinical trial in this research and the value of $T_{10}$ is fixed to \SI{1600}{\ms} for both blood and prostate, in accordance with the values found in the literature~\citep{fennessy2015quantitative,de2004mr,carr2011magnetic}.
-      \item[Estimation of population-based \ac{aif}] While estimating the pharmacokinetic parameters from Tofts model, the \ac{aif} concentration $C_p(t)$ can be computed either from the patient or a population.
-        We presented in the two previous sections the algorithms which allows to estimate the patient-based \ac{aif} concentration.
-        To compare with the previous approach, we also computed a population-based \ac{aif} which will be also used later to compare the performance of both approaches.
-        In that regard, the population-based \ac{aif} was estimated as in~\citep{meng2010comparison} by fitting the average patient-based \ac{aif}s to the model of~\cite{parker2006experimentally} which is formulated as in Eq.\,\eqref{eq:parker}:
+      \item[Estimation of population-based \ac{aif}] While estimating
+        the pharmacokinetic parameters using the Tofts model, the \ac{aif} concentration $C_p(t)$ can be computed either from the patient or a population.
+        In the two previous sections, we presented the algorithms that
+        allow for the estimation of the patient-based \ac{aif} concentration.
+        For a comparison with the previous approach, we also computed a population-based \ac{aif} that will be used later to compare the performance of both approaches.
+        In this regard, the population-based \ac{aif} was estimated in
+        accordance with the method of~\citep{meng2010comparison} by
+        fitting the average patient-based \ac{aif}s to the model
+        of~\cite{parker2006experimentally} which is formulated as
+        shown in Eq.\,\eqref{eq:parker}, as follows:
         \begin{equation}
@@
         \end{equation}
-        \noindent where $A_n$, $T_n$, and $\sigma_n$ are the scaling constants, centers, and widths of the n\textsuperscript{th} Gaussian, $\alpha$ and $\beta$ are the amplitude and decay constant of the exponential; and $s$ and $\tau$ are the width and center of the sigmoid function, respectively.
+        \noindent where $A_n$, $T_n$, and $\sigma_n$ are the scaling
+        constants, centers, and widths of the n\textsuperscript{th}
+        Gaussian, respectively; $\alpha$ and $\beta$ are the amplitude
+        and decay constant of the exponential, respectively; and $s$ and $\tau$ are the width and center of the sigmoid function, respectively.
 \end{description}
 
-The parameters are estimated by fitting the model using a constrained non-linear least-squares optimization, solved with the Trust Region Reflective algorithm~\citep{sorensen1982newton} and bounding the parameters to be positive.
+The parameters are estimated by fitting the model using constrained non-linear least-squares optimization, solved with the Trust Region Reflective algorithm~\citep{sorensen1982newton} and bounding the parameters to be positive.
 
@@
 
-\citeauthor{gliozzi2011phenomenological} showed that \ac{pun} approach can be used for \ac{dce}-\ac{mri} analysis~\citep{gliozzi2011phenomenological}.
+\citeauthor{gliozzi2011phenomenological} showed that the \ac{pun} approach can be used for \ac{dce}-\ac{mri} analysis~\citep{gliozzi2011phenomenological}.
 The model has been successfully used in a \ac{cad} system proposed by~\cite{giannini2015fully}.
@@
 
-\noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at time $t$ and the average pre-contrast \ac{mri} signal intensity, respectively; $r$, $a_0$, and $\beta$ are the free parameters of the model.
+\noindent where $s(t)$ and $S_0$ are the \ac{mri} signal intensity at
+time $t$ and the average pre-contrast \ac{mri} signal intensity,
+respectively; and $r$, $a_0$, and $\beta$ are the free parameters of the model.
 
-The parameters are estimated by fitting the model using non-linear least-squares optimization solved with Levenberg-Marcquardt.
+The parameters are estimated by fitting the model using non-linear
+least-squares optimization solved with Levenberg-Marquardt algorithm.
 
@@
 The semi-quantitative analysis of the \ac{dce}-\ac{mri} is equivalent to extracting curve characteristics directly from the signal without a strict theoretical pharmacokinetic meaning.
-In this work, we use the model presented by~\cite{huisman2001accurate} which formulated the \ac{mri} signal as in Eq.\,\eqref{eq:huisman}:
+In this work, we use the model presented by~\cite{huisman2001accurate}, which formulates the \ac{mri} signal as in Eq.\,\eqref{eq:huisman}:
 
@@
 
-\noindent where $s(t)$ is the \ac{mri} signal intensity, $S_0$ is the pre-contrast signal intensity, $t_0$ is the time corresponding to the start of enhancement, $S_M$ and $\tau$ is the maximum of the signal and the exponential time constant, and $w$ is the slope of the linear part.
+\noindent where $s(t)$ is the \ac{mri} signal intensity, $S_0$ is the
+pre-contrast signal intensity, $t_0$ is the time corresponding to the
+start of enhancement, $S_M$ and $\tau$ are the maximum of the signal
+and the exponential time constant, respectively, and $w$ is the slope of the linear part.
 
-\citeauthor{huisman2001accurate} argue that curve fitting via least-squares minimization using Nelder-Mead algorithm leads to inaccurate estimation of the free parameters: mainly the issue come from an incorrect estimation of the start of enhancement $t_0$ leading to incorrect estimation of the other parameters.
-Therefore, they propose to:
-(i) estimate robustly $t_0$,
-(ii) estimate $S_0$ by averaging the samples between $0$ and $t_0$
-(ii) estimate $w$ depending if the slope is significant or not,
-(iii) estimate $S_M$ which should be the point at the intersection of the most probable slope line and the plateau.
+\citeauthor{huisman2001accurate} argue that curve fitting via
+least-squares minimization using the Nelder-Mead algorithm leads to
+inaccurate estimations of the parameters free parameters.
+Mainly the issue comes from an incorrect estimation of the start of
+enhancement $t_0$, leading to an incorrect estimation of the other parameters.
+Therefore, \citeauthor{huisman2001accurate} to
+(i) robustly estimate $t_0$,
+(ii) estimate $S_0$ by averaging the samples between $0$ and $t_0$,
+(ii) estimate $w$ depending on whether the slope is significant or
+not, and
+(iii) estimate $S_M$, which should be the point of intersection of the most probable slope line and the plateau.
 
-Instead of these successive estimations, we propose a unified optimization in which $t_0$ is fixed since that this is a key parameter.
-Therefore, $t_0$ is robustly estimated from the \ac{aif} signal since that this is the most enhanced signal in which the start of enhancement is easily identifiable.
-The \ac{aif} signal is computed as in Section~\ref{sec:tofts}.
+Instead of these successive estimations, we propose a unified optimization in which $t_0$ is fixed since it is a key parameter.
+Therefore, $t_0$ is robustly estimated from the \ac{aif} signal since this is the most enhanced signal in which the start of enhancement is easily identifiable.
+The \ac{aif} signal is computed as discussed in Section~\ref{sec:tofts}.
 $t_0$ is estimated by finding the maximum of the first derivative of the \ac{aif} signal, always occurring at the beginning of the signal.
@@
 Furthermore, the parameters $\tau$ and $S_M$ are bounded during the optimization to ensure robust estimations.
-$\tau$ is bounded between $t_0$ and $t_f$ which is the time of the last sample while $S_M$ is bounded between $S_0$ and $\max(s(t))$.
+$\tau$ is bounded between $t_0$ and $t_f$, which is the time of the
+last sample, and $S_M$ is bounded between $S_0$ and $\max(s(t))$.
 
-From Eq.\,\eqref{eq:huisman}, the following features are extracted:
+From Eq.\,\eqref{eq:huisman}, the following features can be extracted:
 (i) the wash-in corresponding to the slope between $t_0$ and $t_0 + 2 \tau$,
@@
 (iv) the exponential time constant $\tau$, and
-(v) the relative enhancement $S_M - S_0$.
+(v) the relative enhancement of $S_M - S_0$.
 

### 2017-01-27 03_experiments/experiments.tex
make english correction

@@
 
-The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal level of \ac{psa}.
-The acquisition is performed using a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
-Aside of the \ac{mri} examination, these patients also have undergone a guided-biopsy.
-The dataset is composed of a total of 20 patients of which 18 patients have biopsy proven \ac{cap} and 2 patients are ``healthy'' with negative biopsies.
-Therefore, 13 patients have a \ac{cap} in the \ac{pz}, 3 patients have \ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both \ac{pz} and \ac{cg} and finally 2 patients are considered as ``healthy''.
-An experienced radiologist has segmented the prostate organ --- on \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} --- as well as the prostate zones (i.e., \ac{pz} and \ac{cg}) and \ac{cap} on the \ac{t2w}-\ac{mri}.
+The multi-parametric \ac{mri} data are acquired from a cohort of patients with higher-than-normal levels of \ac{psa}.
+Acquisition is achieved with a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
+In addition to the \ac{mri} examination, these patients also have
+undergone a \ac{trus} guided-biopsy.
+The dataset is composed of a total of 20 patients, 18 of which have
+biopsies that were positive for \ac{cap} and 2 patients are considered
+``healthy'' because they have negative biopsies.
+Therefore, 13 patients have \ac{cap} in the \ac{pz}, 3 patients have
+\ac{cap} in the \ac{cg}, 2 patients have invasive \ac{cap} in both the
+\ac{pz} and the \ac{cg}, and finally 2 patients are considered ``healthy''.
+An experienced radiologist segmented the prostate organ---on
+\ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri}---as well as the prostate
+zones (i.e., \ac{pz} and \ac{cg}) and the \ac{cap} on the \ac{t2w}-\ac{mri}.
 
-A \SI{3}{\mm} slice fat-suppressed \ac{t2w} fast spin-echo sequence (\ac{tr}/\ac{te}/\ac{etl}: \SI{3400}{\ms}/\SI{85}{\ms}/13) is used to acquire images in sagittal and oblique coronal planes, the latter planes being orientated perpendicular or parallel to the prostate \ac{pz} – rectal wall axis.
+A \SI{3}{\mm} slice of fat-suppressed \ac{t2w} fast spin-echo sequence
+(\ac{tr}/\ac{te}/\ac{etl}: \SI{3400}{\ms}/\SI{85}{\ms}/13) is used to
+acquire images in the sagittal and oblique coronal planes, with the latter planes orientated perpendicular or parallel to the prostate \ac{pz} – rectal wall axis.
 Three-dimensional \ac{t2w} fast spin-echo (\ac{tr}/\ac{te}/\ac{etl}: \SI{3600}{\ms}/\SI{143}{\ms}/109, slice thickness: \SI{1.25}{\mm}) images are then acquired in an oblique axial plane.
-The nominal matrix and \ac{fov} of the 3D \ac{t2w} fast spin-echo images are $320 \times 256$ and $280 \times 240$ mm\textsuperscript{2}, respectively, thereby affording sub-millimetric pixel resolution within the imaging plane.
+The nominal matrix and the \ac{fov} of the 3D \ac{t2w} fast spin-echo images are $320 \times 256$ and $280 \times 240$ mm\textsuperscript{2}, respectively, thereby affording sub-millimetric pixel resolution within the imaging plane.
 
-\ac{dce}-\ac{mri} is performed using a fat suppressed 3D T$_1$ VIBE sequence (\ac{tr}/\ac{te}/Flip angle: \SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
+\ac{dce}-\ac{mri} is performed using a fat-suppressed 3D T$_1$ VIBE
+sequence (\ac{tr}/\ac{te}/Flip angle:
+\SI{3.25}{\ms}/\SI{1.12}{\ms}/\SI{10}{\degree}; Matrix: $256 \times
+192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); a slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
 A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
 
-These \ac{dce}-\ac{mri} sequences are resampled using the spatial information of the \ac{t2w}-\ac{mri} and missing data are interpolated using a linear interpolation.
-The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered, to remove any patient motion during the acquisition.
-Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} in order to propagate the prostate zones and \ac{cap} ground-truths.
+These \ac{dce}-\ac{mri} sequences are resampled using the spatial
+information of the \ac{t2w}-\ac{mri} and any missing data are added using linear interpolation.
+The volumes of the \ac{dce}-\ac{mri} dynamic are rigidly registered to remove any patient motion during the acquisition.
+Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} to propagate the prostate zones and \ac{cap} ground-truths.
 The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
@@
 The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}~\citep{lemaitre2016github}.
-The data used for this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}~\citep{lemaitre2016dce}.
+The data used in this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}~\citep{lemaitre2016dce}.
 
@@
     \toprule
-    Data type & Brix & Hoffmann & Tofts population \ac{aif} & Tofts patient \ac{aif} & \ac{pun} & Semi-quantitative \\
+    Data type & Brix & Hoffmann & Tofts population \ac{aif} & Tofts patient \ac{aif} & \ac{pun} & Huisman \\
     \midrule
@@
 
-Parameter estimation of the quantification methods are related to fit a specific model to the \ac{dce}-\ac{mri} data.
-Therefore, this section reports the goodness of fitting by computing the coefficient of determination $R^2$ such as in Eq.\,\eqref{eq:r2}
+The parameter estimations from the quantification methods are related to fit a specific model to the \ac{dce}-\ac{mri} data.
+Therefore, the coefficient of determination $R^2$ reports the goodness
+of fit, as follows:
 
@@
 
-\noindent where $s_t$ and $\hat{s}_t$ are the signal to be fitted and the estimated signal at time $t$, respectively; $\bar{s}$ is the average signal to be fitted.
+\noindent where $s_t$ and $\hat{s}_t$ are the signal to be fitted and
+the estimated signal at time $t$, respectively, and $\bar{s}$ is the average signal to be fitted.
 
-Mean and standard-deviation of the coefficient of determination $R^{2}$ is reported in Table~\ref{tab:r2} for each quantification model.
+The mean and the standard-deviation of the coefficient of determination, $R^{2}$, are reported in Table~\ref{tab:r2} for each quantification model.
 Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.
-Additionally, the proposed \ac{pun} model does not to fit well the data.
+Additionally, the proposed \ac{pun} model does not to fit the data well.
 After introspection of the fitted curves, the original model --- as
@@
 the model to be fitted.
-Data normalization improves the coefficient $R^2$ for all the methods apart of the Hoffmann model.
+Data normalization improves the coefficient $R^2$ for all the methods
+except for the Hoffmann model.
 The large standard deviation for this model might imply that there are some cases where the fitting fails.
@@
 
-To study the potential benefit of our normalization, \ac{cap} are detected at a voxel level using pharmacokinetic parameters estimated from un-normalized and normalized \ac{dce}-\ac{mri} data.
-Each individual pharmacokinetic parameter is classified to evaluate their individual discriminative power to detect \ac{cap}.
+To study the potential benefit of our normalization, \ac{cap} is detected at a voxel level using pharmacokinetic parameters estimated from non-normalized and normalized \ac{dce}-\ac{mri} data.
+Each individual pharmacokinetic parameter is classified to evaluate its individual discriminative power to detect \ac{cap}.
+In addition, p-values ($p$) are computed to identify pairs of classifiers
+which are significantly different, using a Wilcoxon signed-ranked
+test. Those p-values are represented in the color coded co-occurrence
+matrix shown in Fig.\,\ref{fig:wilcoxon}, where blue cells correspond
+to lower p-values while red cells are greater p-values.
 Therefore, a \ac{rf} classifier is used in conjunction with a \ac{lopo}.
-The use of \ac{rf} is motivated since that it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer,lemaitre2015computer}.
-Results are summarized in Table~\ref{tab:resfeats} in terms of \ac{auc}.
-Normalization can improve the detection of \ac{cap}; however, the benefit of normalization is more obvious by combining together the pharmacokinetic features of a given model (e.g., $A$, $k_ep$, and $k_el$ for Brix model), as previously done in traditional \ac{cad} system~\citep{lemaitre2015computer}.
+The use of \ac{rf} is encouraged since it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer,lemaitre2015computer}.
+The results are summarized in Table~\ref{tab:resfeats} in terms of the \ac{auc}.
+Normalization can improve the detection of \ac{cap}, but the benefit
+of normalization is more obvious with the combination of the
+pharmacokinetic features of a given model (e.g., $A$, $k_ep$, and
+$k_el$ for the Brix model) as previously executed in the traditional \ac{cad} system~\citep{lemaitre2015computer}.
 For the latter configuration, results are summarized by performing a \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
-Quantification using normalized data outperforms quantification using un-normalized data in terms of classification performance apart of Hoffmann and Tofts population-based \ac{aif} models.
-The reasons behind the decrease of the \ac{auc} might be related to: (i) a poor fitting as discussed in Sect.\,\ref{sec:fit} (cf., Hoffmann model) and (ii) a small number of patients while estimating some parameters (cf., Tofts model).
-The best classification performance are obtained using the semi-quantitative approach with an \ac{auc} of $0.655$.
+Quantification using normalized data outperforms quantification using
+non-normalized data in terms of the classification performance, except
+for Hoffmann and Tofts population-based \ac{aif} models.
+The reasons behind the decrease of the \ac{auc} might be related to:
+(i) a poor fitting as discussed in Sect.\,\ref{sec:fit} (cf., Hoffmann
+model) and (ii) a small number of patients for the estimation of some parameters (cf., Tofts model).
+The best classification performance is obtained using the
+semi-quantitative approach with an \ac{auc} of $0.655 \pm 0.106$.
 
@@
 
-As stated in the introduction, the quantification methods are extracting a set of parameters characterizing the enhancement \ac{dce}-\ac{mri} signal.
+As stated in the introduction, the quantification methods extract a
+set of parameters that characterize the enhancement of the \ac{dce}-\ac{mri} signal.
 However, this extraction might lead to a loss of information.
-This experiment is performed to assess if making use of the whole \ac{dce}-\ac{mri} signal instead of the just the pharmacokinetic parameters can improve the classification performance.
+This experiment is performed to assess whether using the whole
+\ac{dce}-\ac{mri} signal, rather than just the pharmacokinetic parameters, can improve the classification performance.
 Therefore, each enhanced \ac{dce}-\ac{mri} signal, normalized and un-normalized, is classified using a \ac{rf} classifier in a \ac{lopo} fashion.
 The \ac{roc} analysis and \ac{auc} are reported in Fig.\,\ref{fig:rfnormdcesignal}.
-Classification without normalization lead to the worst performance, with an \ac{auc} of $0.568$.
-However, data normalization in conjunction with the use of the entire \ac{dce}-\ac{mri} signal is the strategy which outperforms others, with an \ac{auc} of $0.666$.
+Classification without normalization leads to the worst performance,
+with an \ac{auc} of $0.568 \pm 0.162$.
+However, data normalization in conjunction with the use of the entire
+\ac{dce}-\ac{mri} signal is the strategy that outperforms others,
+with an \ac{auc} of $0.666 \pm 0.154$.
 Comparable outcomes are visible while analyzing the \ac{auc}
-distributions scores for each prostate zone. The \ac{auc} score
+scores distribution for each prostate zone as shown in
+Fig.\,\ref{fig:boxplot}. The \ac{auc} scores
 related to \ac{cap} in \ac{cg} improves using normalized data, for

### 2017-01-27 04_discussions/discussions.tex
make english correction

--- 2016-08-26 04_discussions/discussions.tex
@@
 
-The experiments conducted in the previous section can give rise to several discussions.
+The experiments conducted in the previous section can incite several discussions.
 In Tofts quantification, two different approaches have been used to infer the pharmacokinetic parameters: using a population-based or a patient-based \ac{aif}.
-The population-based \ac{aif} approach leads to better classification performance.
-However, there is two shortcomings to take into account while advancing this fact:
-(i) T$_{10}$ parameter has been fixed and not computed from a T$_1$ map and
+The patient-based \ac{aif} approach leads to better classification performance.
+However, there are two shortcomings to take into account when considering this fact:
+(i) the T$_{10}$ parameter has been fixed and is not computed from a T$_1$ map and
 (ii) the population-based \ac{aif} has been estimated from a cohort of only 17 patients.
-These two limitations have to be considered while advancing that population-based \ac{aif} modelling is outperforming patient-based \ac{aif} modelling.
+These two limitations have to be considered when asserting that
+population-based \ac{aif} modeling outperforms patient-based \ac{aif} modeling.
 
-The best classification performance is reached by normalizing the \ac{dce}-\ac{mri} data and use the whole enhanced signal as feature, emphasizing the fact that a loss of information while extracting quantitative parameters.
-However, this strategy suffers from one drawback: the training time of the \ac{rf} classifier increases since that from 3 to 5 features, the feature space become a 40 dimensions space.
+The best classification performance is achieved by normalizing the
+\ac{dce}-\ac{mri} data and using the entire enhanced signal as a
+feature, emphasizing the fact that a \emph{loss of information} may occur while extracting quantitative parameters.
+Furthermore, normalization is a less complex process than all
+quantification methods and significantly improves the classification
+performance of the semi-quantitative approach ($p=0.001$) proposed by
+\citeauthor{huisman2001accurate}.
+Additionally, our normalization improves the \ac{auc} score related to
+the detection of \ac{cap} in \ac{cg}, also known to be the most
+challenging cases in the diagnosis of \ac{cap}.
+
+However, using the entire enhanced signal in conjunction with the
+normalization is limited by one drawback: the training time of the
+\ac{rf} classifier increases; instead of using $3$ to $5$ features, so the
+feature space becomes a $40$ dimensional space. The extraction of the
+semi-quantitative parameters leads to a comparable classification performance ---
+$0.655 \pm 0.108$ vs. $0.666 \pm 0.154$ --- and should be chosen as the alternative method to
+consider if the number of feature in the classification is
+critical. Despite this fact, the benefit of our proposed normalization method
+has been shown for both methods.
+
+Nevertheless, this study is performed on a small cohort of patients using a single \ac{mri} machine.
+Generalizing the results of this study onto a larger dataset acquired
+from different commercial systems needs to be considered to study the robustness of the proposed approach.
+Additionally, our method being non-parametric should provide an
+adequate framework to process \ac{dce} data from different
+institutions, scanners with different settings.
 

### 2017-01-27 05_conclusions/conclusions.tex
Address the comments of robert
make english correction

--- 2016-08-08 01_introduction/introduction.tex
@@
-\section{Introduction}
+\section{Conclusions and future works}\label{sec:conclusions}
+
+In this work, we presented a new method for normalizing/standardizing \ac{dce}-\ac{mri} data.
+This method is designed to reduce the inter-patient variations that occur during data acquisition.
+A graph-based approach was used to correct intensity offset along with a model-based correction to reduce time offset and intensity scaling.
+We show the benefit of our normalization method prior to extract quantitative and semi-quantitative features, with a significant improvement of the classification performance.
+Nevertheless, we also show that using the whole normalized \ac{dce}-\ac{mri} signal outperforms all quantitative approaches.
+
+In future research, this normalization needs to be part of an
+\ac{mpmri} \ac{cad} system in which the \ac{dce}-\ac{mri} modality needs to be combined with other complementary modalities.
 

### 2017-01-27 main.tex
Update the acknowledgement
make english correction

@@
 \begin{abstract}
-\Ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used to the design of new \ac{cad} systems.
-\ac{dce}-\ac{mri} is one of the modality regularly used in \ac{mpmri} \ac{cad} system.
-Pharmocokinetric parameters are extracted from the \ac{dce}-\ac{mri} sequences and later used to discriminate cancerous from healthy tissue.
+\Ac{mpmri} plays a major role in the detection of \ac{cap} and is commonly used in the design of new \ac{cad} systems.
+\ac{dce}-\ac{mri} is one of the modalities regularly used in \ac{mpmri} \ac{cad} systems.
+Pharmocokinetic parameters are extracted from the \ac{dce}-\ac{mri}
+sequences and are later used to discriminate cancerous tissue from healthy tissue.
 However, some inter-patients variations occur during the data acquisition leading to estimation errors of the pharmacokinetic parameters.
-Therefore, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patient variability of the data.
-The benefit and simplicity of our approach is shown by detecting cancerous voxel from healthy voxel using the normalized enhanced \ac{dce}-\ac{mri} signal and comparing with the state-of-the-art quantitative and semi-quantitative methods.
+Therefore, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduces the inter-patients variability of the data.
+The benefit and simplicity of our approach is shown by detecting
+cancerous voxels from healthy voxels using a normalized enhanced
+\ac{dce}-\ac{mri} signal and comparing it with state-of-the-art quantitative and semi-quantitative methods.
 Additionally, we show that using this normalization approach in conjunction with the quantitative methods improves the classification performance of most of the models.
-The best classification performance to detect \ac{cap} is obtained using the whole \ac{dce}-\ac{mri} normalized signal, reaching an \ac{auc} of $0.666\ (\pm 0.154)$ and outperforming the quantitative approaches.
+The best classification performance for detecting \ac{cap} is obtained using the whole \ac{dce}-\ac{mri} normalized signal, reaching an \ac{auc} of $0.666\ (\pm 0.154)$ and outperforming the quantitative approaches.
 \end{abstract}
@@
 \input{05_conclusions/conclusions}
+
+\section*{Acknowledgements}
+Guillaume Lema\^itre is supported by the Generalitat de Catalunya (grant nb. FI-DGR2012) and partly by the Mediterranean Office for Youth (grant nb. 2011/018/06).
+
 \input{06_appendix/appendix}

### 2017-01-30 02_methods/methods.tex
Improve figure

@@
   \hspace*{\fill}
-  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
-  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
+  \subfigure[Start of enh.: 6\textsuperscript{th} serie;
+  initial intensity: 117; wider st. dev.]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1.pdf}} \hfill
+  \subfigure[Start of enh.: 4\textsuperscript{th} serie;
+  initial intensity: 103; narrower std. dev.]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}} \hfill
   \hspace*{\fill}
-  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\alpha_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
+  \caption{\subref{subfig:pathhist} Illustration of the heatmap
+    representation: all \ac*{pdf}s of the prostate gland are
+    concatenated together to build an heatmap;
+    \subref{subfig:pat1}-\subref{subfig:pat2} Heatmap of 2 patients
+    revealing  the three types of inter-patient variations: intensity shift
+    ($\Delta_i$), time shift ($\Delta_t$), and intensity scale
+    ($\alpha_i$). The intensity shift is observed by checking the
+    variation of the value of the initial intensity. The time shift
+    is observed by a difference of the start of enhancement. Finally,
+    the intensity scale variation is observed by the difference of
+    dispersion of the intensities.}
   \label{fig:heatmap}

### 2017-01-30 02_methods/methods.tex
Update figure

--- 2017-01-27 02_methods/methods.tex
@@
   \hspace*{\fill}
-  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
-  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
+  \subfigure[$I_0$: 117; $t_0$: 6\textsuperscript{th} serie; wider st. dev.]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
+  \subfigure[$I_0$: 103; $t_0$: 4\textsuperscript{th} serie; narrower std. dev.]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
   \hspace*{\fill}
-  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\alpha_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
+  \caption{\subref{subfig:pathhist} Illustration of the heatmap
+    representation: all \ac*{pdf}s of the prostate gland are
+    concatenated together to build an heatmap;
+    \subref{subfig:pat1}-\subref{subfig:pat2} Heatmap of 2 patients
+    revealing  the three types of inter-patient variations: intensity shift
+    ($\Delta_i$), time shift ($\Delta_t$), and intensity scale
+    ($\alpha_i$).}
   \label{fig:heatmap}

### 2017-01-31 response_to_reviewers.tex
add response to reviewer

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Formal Letter
% LaTeX Template
% Version 1.11 (8/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Letters)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ----------------------------------------------------------------------------------------
% DOCUMENT CONFIGURATIONS
% ----------------------------------------------------------------------------------------

\documentclass{letter}

% Adjust margins for aesthetics
\addtolength{\voffset}{-0.5in}
%\addtolength{\hoffset}{-0.3in}
\addtolength{\textheight}{2cm}

\usepackage[letterpaper, margin=1.5in]{geometry}

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

% ----------------------------------------------------------------------------------------
% YOUR NAME & ADDRESS SECTION
% ----------------------------------------------------------------------------------------

\signature{Guillaume Lema\^itre} % Your name for the signature at the bottom

\address{Parietal team, Inria \\ CEA, Universit\'e Paris-Saclay \\ 1 Rue
  Honor\'e d'Estienne d'Orves \\ 91120 Palaiseau \\ France} % Your address
% and phone number

% ----------------------------------------------------------------------------------------

\begin{document}

% ----------------------------------------------------------------------------------------
% ADDRESSEE SECTION
% ----------------------------------------------------------------------------------------

\begin{letter}{Nicholas Ayache \\ Co-editor in Chief \\ Medical Image Analysis} % Name/title of the addressee

  % ----------------------------------------------------------------------------------------
  % LETTER CONTENT SECTION
  % ----------------------------------------------------------------------------------------

  \opening{
    \textit{Subject: MEDIA-D-16-00507 - Response to reviewers}\\ \\
    \textbf{Dear Sir or Madam,}}

  We would like to thank the reviewers for their pertinent
  remarks that have increased the quality of the manuscript. Whenever
  possible, the comments of the reviewers have been addressed and
  highlighted in the article.

  Please, find below a point-by-point response to each issues raised
  by the reviewers.

  Reviewer \#1:
  \begin{enumerate}
  \item \textbf{In a typical DCE based analysis, the contrast
      enhanced images are rigidly registered to T1w images for
      intensity normalization. Typically for multi-parametric MRI
      based CAD system for prostate cancer detection T1w images
      are present. This is useful in differentiating cancers from
      blood hemorrhage following prostate biopsy. Please discuss
      why a pre or a post contrast T1w image is missing from the
      clinical trial that will be using DCE images.}\\
    The MRI acquisition was performed prior to carry out the
    biopsy. Therefore, the risk of blood hemorrhage is discarded.
    Additionally, pre-contrast T1w images are available since 4 to 6
    volumes are acquired previous to the bolus injection of the
    contrast media. Indeed, this pre-contrast data are used in some
    models (i.e., $S_0$).
  \item \textbf{The other advantage of normalizing to T1w images are
      patient specific information will be preserved. Different
      patients may have different cancer lesions of different grades
      (having different kinetic expression in DCE) and normalizing all
      patients to the same space may result in loss of
      information. Please comment.}\\
    Our normalization is designed to align the \emph{mean kinetic
      expression}. Therefore, it is true that patient-related
    information can be lost. However, lesion with different grades
    should more or less dispersed to the mean kinetic expression. This
    information remains available after applying our normalization.
  \item \textbf{T1w normalization will be probably be more robust to
      change in magnet, machine, reconstruction software and
      acquisition parameters across different institutions as the
      objective is normalization to be patient and institution
      specific. Please comment how the presented model may be affected
      in a multi-institutional study.}\\
    Our method does not rely on any manufacturer/machine-specific settings.
    Subsequently, our approach should work on any type
    of devices, enabling multi-institutional studies. We included
    these remarks in our future work section in p.~23/l.~396.
  \item \textbf{Please discuss how the improvement in prostate cancer
      detection in DCE-MRI impacts the current clinical CAD
      pipeline. According to PIRADS v2 guidelines more emphasis is
      laid upon T1w, T2w and DWI compared to DCE images. Experienced
      radiologists can detect prostate cancers in peripheral zone with
      a high degree of accuracy (higher than 0.6 AUC). The transition
      zone lesions are more difficult to distinguish. Please comment
      how the model performs in detection of transition zone
      lesions. Further please comment how this model adds value to
      already established clinical pipeline of detecting prostate
      cancer (PIRADS).}\\
    A stratified analysis separating PZ and CG showed an increase of
    the classification performance in CG after applying our
    normalization method as depicted in Fig.\,8 p.~22.
    The PIRADS v2 emphasized that DCE-MRI have to be included in
    mp-MRI acquisition to detect small lesion. However, it also warn
    that the benefit is modest. Therefore, the impact of an
    improvement of detection in DCE-MRI can only be evaluated in a
    fully mp-MRI CAD system. Indeed, we recently showed, --- Lemaitre,
    Guillaume. Computer-Aided Diagnosis for Prostate Cancer using
    Multi-Parametric Magnetic Resonance Imaging. Diss. Universit\'e de
    Bourgogne; Universitat de Girona, 2016;
    Chapt.\,6/p.~150/Table~6.10 ---, that DCE-MRI features are
    considered important and the combination with other modalities
    will lead to better classification results.
    However, in our humble opinion, including those additional results
    will clutter the paper.
  \item \textbf{Comparing the results of semi-automatic approach and
      the presented approach of curve fitting using the entire curve
      the results are not significantly different (0.65 AUC vs 0.66
      AUC). The presented model is however automatic which would
      reduce inter-rater variance in a semi-automatic method. Please
      present a discussion comparing these two results.}\\
    It is important to notice that for both approaches, ---
    semi-quantitative and entire enhanced signal ---, the results
    are obtained using our normalization approach, showing the importance of
    this step. We added a discussion in p.~23/l.~388 regarding the
    semi-quantitative approach and entire enhanced signal
    classification. The semi-quantitative approach reduce the number
    of features to analyze, speeding up the classification. However,
    it relies on the curve fitting which is also time consuming and
    might fail.
  \item \textbf{Use of single feature for a random forest classifier
      (Table 2) may be detrimental for the classifier as random
      sub-sampling of the features are not possible. Please present
      the comparison with some linear classifiers like linear SVM.}\\
    A classification using a linear SVM has been added in additional
    material.
    Unlike a linear SVM, RF allows to find multiple thresholds,
    leading to a much complex decision boundary for this
    feature. Bootstrapping the samples for each tree allows to cope
    with the over-fitting of each decision trees. Therefore, we do not
    think that a linear SVM will substantially better insights as are
    showing the results provided in the additional material.
  \end{enumerate}

  Reviewer \#2:
  \begin{enumerate}
  \item \textbf{The title is misleading and not very scientific and I
      would recommend to remove the second part and reword the first
      part to cover the contents of the paper.}\\
    We are not against changing the title but we would like to take
    advantage of this revision to get the opinion of all reviewers
    regarding this matter.
  \item \textbf{The use of the English language needs some attention:
      get it all proof read.}\\
    As suggested, the manuscript has been corrected by an English editing
    service to ensure a good quality writing.
  \item \textbf{What guided biopsy was used: US?}\\
    The guided biopsy was performed with a TRUS. We added this
    statement in p.~15/l.~275.
  \item \textbf{The number of cases seems low. This is mentioned as
      possibly affecting the results and that the limitations might be
      based on the sample size. At the end of section 5 one could draw
      the conclusion that they should do a more extensive study.}\\
    The statement has been added in the discussions p.~23/l.~396.
  \item \textbf{How would this translate to other types of MRI
      systems: it would be good to see experimental results on this or
      at least some discussion.}\\
    Refer to reviewer \#1 / comment 3 since this is a shared remarks.
  \item \textbf{The disappointing performance and large standard
      deviation of the PUN model should be investigated and
      explained.}\\
    A discussion is added in p.~17/l.~320. The original model lacks of
    degrees of freedom. Two additional parameters will
    allow for a better fit. However, we used the original formulation
    in our experiments.
  \item \textbf{There should be a detailed discussion on the results
      to indicate which differences are statistically
      significant. ``Significant'' is mentioned in the conclusions, but
      there is no evidence for this.}\\
    We added a Wilcoxon significance test - see Fig.\,7. Now, the term
    significant is only used for $p<0.05$.
  \item \textbf{The overall results seem poor and this could be
      further discussed.}\\
    It is difficult to compare with the state-of-the-art methods since
    the dataset used are different and the reported results in those
    studies are usually linked to a mp-MRI CAD instead of only
    DCE. Nevertheless, our results are in the same range than Litjens,
    Geert, et al. "Computer-aided detection of prostate cancer in
    MRI." IEEE transactions on medical imaging 33.5 (2014):
    1083-1092 regarding the classification performance of the Tofts
    parameters.
  \item \textbf{Sections 5 and 6 are both disappointingly short.}
    Due to additional analyses, the discussion became longer.
    % However,
    % we believed that there is no need for repeating information
    % already presented in the experiment section or give hypothesis
    % which cannot be verified.
  \item \textbf{Some journals references incomplete. Gliozzi et al. is
      not a single page. Check: Schabel, Shanbhag, Zhu.}\\
    The references have been corrected.
  \end{enumerate}

  Reviewer \#5:
  \begin{enumerate}
  \item \textbf{There are however several issues with the paper In the
      current state. Using quantitative parameters obtained from
      pharmacokinetic models as an end-point comparison indeed may be
      important as the models provide physiological information
      related to capillary permeability, blood fraction and
      interstitial space volume, etc.. However I am not really
      convinced by the detailed results presented in Table 2, as no
      statistical test was performed when the classification
      performances are higher with normalized data, and for some of
      the models the results are worst. For me, the benefits of the
      method are not fully demonstrated in terms of classification
      performance using the models. How these parameters are modified
      with the normalization?}\\
    This is important to emphasize that our goal was to propose a
    normalization method to allow classification of the entire
    enhanced signal which should perform as good as the current
    models. We apply the same normalization on the different
    pharmacokinetic models and, as mentioned by the reviewer ---
    the results are not significantly better.
    Indeed, these experiments were carried out to investigate the
    benefit or not of the normalization with the current models,
    without expecting the results to improve.
  % \item \textbf{Although quantitative parameters obtained from
  %     pharmacokinetic models applied to DCE-MRI series have
  %     demonstrated in general superior performance to differentiate
  %     cancerous from normal tissue prostate in comparison to simpler
  %     enhancement analysis such as semi-quantitative or qualitative
  %     parameters, there are still several differences in results
  %     across the studies in the literature. There are some papers
  %     aimed at defining normal values for some of the pharmacokinetic
  %     parameters. The authors may refer to the paper Sanz-Requena et
  %     al. Dynamic contrast-enhanced case-control analysis in
  %     3T MRI of prostate cancer can help to characterize tumor
  %     aggressiveness, European Journal of Radiology, 85(11), November 2016,
  %     pp. 2119-2126, for a detailed list of typical values and difficulties
  %     of the models}\\
  \item \textbf{Some of the benefits or improvements may be
      demonstrated before any further classification step. The method
      could be useful when performing population analysis with the raw
      data, previous to defining a model.}\\
    We do not really see which analysis can be performed to evaluate
    the benefits of our methods before the classification step. A study of
    the variances with and without normalization could be carried out but
    an evaluation after classification seems equivalent and a good manner to
    evaluate the benefit of the normalization. In fact, this is the
    results reported in Fig.\,6(c).
  \item \textbf{Figure 1 is not pertinent for the goal of this paper.
      It is not clear how is represented the interindividual variation in
      figure 2?  In Fig 2a the PDFs are concatenated in time to obtain a
      heatmap representation, but in 2 b-c  the differences across
      individuals does not appear.}\\
    Figure 1 is used to illustrate inter-patients variation in T2w-MRI
    and to highlight the need of a different normalization approach
    than the one needed in T2w. We improve the Fig.\,2. Figure~2(a)
    presents only the process to build the
    heatmap. In Fig.\,2(b)-2(c), we added parameters which highlight
    more clearly the variations and added their corresponding values
    in caption.
  \item \textbf{It is not clear the rational of equation 1, as the
      parameters are rather empirical.  There are no other ways to
      smooth the heatmap, for example through a diffusion process,
      solving a PDE equation? Or by registering through the series?}\\
    There is probably a confusion. We do not try to smooth the heatmap
    but we search a smooth estimate. Equation 1 represents the weight
    of the graph and is a standard way to formalize graph-based
    problem in image processing.
  \item \textbf{The theoretical foundations of equation 3 are not
      clear. Other registration methods for time signas may have been
      included.}\\
    While other registrations could have been used,
    using a rigid registration directly affect the variations
    $\alpha_i$ and $\Delta_t$. Applying more advanced registration
    such as elastic registration as in Lemaitre, Guillaume, et
    al. "Normalization of T2W-MRI prostate images using Rician a
    priori." SPIE Medical Imaging. International Society for Optics
    and Photonics, 2016. would make it complicated to shift the data
    with only these two parameters. Furthermore, rigid registration
    will not change the variations of the contrast agent over time.
  \item \textbf{Other question that may be raised is the influence of
      the equation parameters (tau, alfa..) in the pharmacokinetic
      models. Do they change with f(t)?}\\
    We think that this question is related to the results presented in
    Sect.\,4.1
  \item \textbf{A thorough review of the structure and in general an
      improvement of the paper in terms of writing may be helpful to
      fully understand the message, the rational and the proposed
      methodology.}\\
    As suggested, the manuscript has been corrected by an English editing
    service to ensure a good quality writing.
  \end{enumerate}

  Thank you for your time and consideration.

  I look forward to your reply.

  \vspace{2\parskip} % Extra whitespace for aesthetics
  \closing{Sincerely,}
  \vspace{2\parskip} % Extra whitespace for aesthetics

  % ----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2017-01-31 02_methods/methods.tex
highlight changes

@@
   \includegraphics[width=0.7\linewidth]{02_methods/figures/t2w.pdf}
-  \caption{Illustration of the inter-patient variations in 17
-    different patients in \acs*{t2w}-\acs*{mri}, using the \acs*{pdf} representation.}
+  \caption{\textbf{Illustration of the inter-patient variations in 17
+    different patients in \acs*{t2w}-\acs*{mri}, using the \acs*{pdf} representation.}}
   \label{fig:t2w}
@@
   \hspace*{\fill}
-  \subfigure[$I_0$: 117; $t_0$: 6\textsuperscript{th} serie; wider st. dev.]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
-  \subfigure[$I_0$: 103; $t_0$: 4\textsuperscript{th} serie; narrower std. dev.]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
+  \subfigure[\textbf{$I_0$: 117; $t_0$: 6\textsuperscript{th} serie; wider st. dev.}]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
+  \subfigure[\textbf{$I_0$: 103; $t_0$: 4\textsuperscript{th} serie; narrower std. dev.}]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
   \hspace*{\fill}

### 2017-01-31 03_experiments/experiments.tex
highlight changes

@@
 Acquisition is achieved with a 3T whole body \ac{mri} scanner (Siemens Magnetom Trio TIM, Erlangen, Germany) using sequences to obtain \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri} and \ac{dw}-\ac{mri}.
-In addition to the \ac{mri} examination, these patients also have
-undergone a \ac{trus} guided-biopsy.
+\textbf{In addition to the \ac{mri} examination, these patients also have
+undergone a \ac{trus} guided-biopsy.}
 The dataset is composed of a total of 20 patients, 18 of which have
@@
 Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.
-Additionally, the proposed \ac{pun} model does not to fit the data well.
+\textbf{Additionally, the proposed \ac{pun} model does not to fit the data well.
 After introspection of the fitted curves, the original model --- as
@@
 integrated in this model to control the translation and amplitude of
-the model to be fitted.
+the model to be fitted.}
 Data normalization improves the coefficient $R^2$ for all the methods
@@
   \includegraphics[width=1.\linewidth]{03_experiments/figures/wilcoxon.pdf}
-  \caption{Wilcoxon signed-ranked test to compare each pair of
+  \caption{\textbf{Wilcoxon signed-ranked test to compare each pair of
     classifiers. The annotation in the matrix corresponds to the
@@
     correspond to lower $p$ while {\color{red} red} cells are
-    representing greater $p$.}
+    representing greater $p$.}}
   \label{fig:wilcoxon}
@@
 Each individual pharmacokinetic parameter is classified to evaluate its individual discriminative power to detect \ac{cap}.
-In addition, p-values ($p$) are computed to identify pairs of classifiers
+\textbf{In addition, p-values ($p$) are computed to identify pairs of classifiers
 which are significantly different, using a Wilcoxon signed-ranked
@@
 Therefore, a \ac{rf} classifier is used in conjunction with a \ac{lopo}.
-The use of \ac{rf} is encouraged since it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer,lemaitre2015computer}.
+The use of \ac{rf} is encouraged since it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer,lemaitre2015computer}.}
 The results are summarized in Table~\ref{tab:resfeats} in terms of the \ac{auc}.
@@
   \includegraphics[width=1.\linewidth]{03_experiments/figures/plot_auc_by_zones.pdf}
-  \caption{Comparison of the distribution of the \acs*{auc} score for
-    each prostate zone, with and without normalization.}
+  \caption{\textbf{Comparison of the distribution of the \acs*{auc} score for
+    each prostate zone, with and without normalization.}}
   \label{fig:boxplot}
@@
 with an \ac{auc} of $0.666 \pm 0.154$.
-Comparable outcomes are visible while analyzing the \ac{auc}
+\textbf{Comparable outcomes are visible while analyzing the \ac{auc}
 scores distribution for each prostate zone as shown in
@@
 related to \ac{cap} in \ac{cg} improves using normalized data, for
-most of the models.
+most of the models.}
 

### 2017-01-31 04_discussions/discussions.tex
highlight changes

@@
 feature, emphasizing the fact that a \emph{loss of information} may occur while extracting quantitative parameters.
-Furthermore, normalization is a less complex process than all
+\textbf{Furthermore, normalization is a less complex process than all
 quantification methods and significantly improves the classification
@@
 the detection of \ac{cap} in \ac{cg}, also known to be the most
-challenging cases in the diagnosis of \ac{cap}.
+challenging cases in the diagnosis of \ac{cap}.}
 
-However, using the entire enhanced signal in conjunction with the
+\textbf{However, using the entire enhanced signal in conjunction with the
 normalization is limited by one drawback: the training time of the
@@
 critical. Despite this fact, the benefit of our proposed normalization method
-has been shown for both methods.
+has been shown for both methods.}
 
 Nevertheless, this study is performed on a small cohort of patients using a single \ac{mri} machine.
-Generalizing the results of this study onto a larger dataset acquired
+\textbf{Generalizing the results of this study onto a larger dataset acquired
 from different commercial systems needs to be considered to study the robustness of the proposed approach.
@@
 adequate framework to process \ac{dce} data from different
-institutions, scanners with different settings.
+institutions, scanners with different settings.}
 

### 2017-02-03 response_to_reviewers.tex
add svm and update response
Update everything

@@
 
-  Please, find below a point-by-point response to each issues raised
+  Please, find below a point-by-point response to each of the issues raised
   by the reviewers.
@@
       clinical trial that will be using DCE images.}\\
-    The MRI acquisition was performed prior to carry out the
-    biopsy. Therefore, the risk of blood hemorrhage is discarded.
-    Additionally, pre-contrast T1w images are available since 4 to 6
-    volumes are acquired previous to the bolus injection of the
-    contrast media. Indeed, this pre-contrast data are used in some
-    models (i.e., $S_0$).
+    Maybe it was not entirely clear from the text but the DCE sequence
+    used in this work is based on T1w. In other words, the
+    pre-contrast acquisition corresponds to the first volumes in the
+    sequence before the contrast injection. To avoid confusion, this
+    has been clarified in the Material section (p.~15/l.~275).
+    Additionally, the risk of blood hemorrhage is discarded since the
+    biopsies are carried out after the MRI acquisition.
   \item \textbf{The other advantage of normalizing to T1w images are
@@
     Our normalization is designed to align the \emph{mean kinetic
-      expression}. Therefore, it is true that patient-related
-    information can be lost. However, lesion with different grades
-    should more or less dispersed to the mean kinetic expression. This
-    information remains available after applying our normalization.
+      expression}. The mean kinetic expression contains cancer and
+    non-cancer kinetic information. Assuming that the amount of cancer
+    information (voxels) is much lower than the normal tissue, the use
+    of this normalization allows to minimize undersired
+    patient-specific (overall-intensity, mean contrast, uptake, ...)
+    without affecting the lesion information.
   \item \textbf{T1w normalization will be probably be more robust to
@@
       in a multi-institutional study.}\\
-    Our method does not rely on any manufacturer/machine-specific settings.
+    In line with the previous comment on the use of T1w, we want to
+    clarify that DCE is based on T1w sequence.
+    Moreover, our method does not rely on any manufacturer/machine-specific settings.
     Subsequently, our approach should work on any type
@@
       cancer (PIRADS).}\\
-    A stratified analysis separating PZ and CG showed an increase of
-    the classification performance in CG after applying our
+    We have included a new stratified analysis, separating PZ and CG,
+    which showed an increase of the classification performance in CG after
+    applying our
     normalization method as depicted in Fig.\,8 p.~22.
-    The PIRADS v2 emphasized that DCE-MRI have to be included in
-    mp-MRI acquisition to detect small lesion. However, it also warn
+    The PIRADS v2 emphasizes that DCE-MRI has to be included in
+    mp-MRI acquisition to detect small lesions. However, it also warns
     that the benefit is modest. Therefore, the impact of an
     improvement of detection in DCE-MRI can only be evaluated in a
-    fully mp-MRI CAD system. Indeed, we recently showed, --- Lemaitre,
+    fully mp-MRI CAD system which is beyond the scope of this paper.
+    Indeed, we recently showed, --- Lemaitre,
     Guillaume. Computer-Aided Diagnosis for Prostate Cancer using
@@
     semi-quantitative approach and entire enhanced signal
-    classification. The semi-quantitative approach reduce the number
+    classification. The semi-quantitative approach reduces the number
     of features to analyze, speeding up the classification. However,
@@
     feature. Bootstrapping the samples for each tree allows to cope
-    with the over-fitting of each decision trees. Therefore, we do not
-    think that a linear SVM will substantially better insights as are
-    showing the results provided in the additional material.
+    with the over-fitting of each decision trees. Results with SVM
+    show no particular improvement in comparison with RF. Therefore,
+    we do not
+    think that including a linear SVM will be beneficial for the paper
+    as are the results provided in the additional material showing.
   \end{enumerate}
 
-  Reviewer \#2:
+  Reviewer \#4:
   \begin{enumerate}
@@
     As suggested, the manuscript has been corrected by an English editing
-    service to ensure a good quality writing.
+    service to ensure a good quality writing. A certificate of the
+    service can be provided upon request.
   \item \textbf{What guided biopsy was used: US?}\\
@@
       the conclusion that they should do a more extensive study.}\\
-    The statement has been added in the discussions p.~23/l.~396.
+    The reviewer is right with the comment, unfortunately due to the
+    difficulty on acquiring and annotating this kind of data, we
+    cannot provide a larger database at this time. However, a
+    statement has been added in the discussions p.~23/l.~396,
+    describing this limitation of the study.
   \item \textbf{How would this translate to other types of MRI
@@
       at least some discussion.}\\
-    Refer to reviewer \#1 / comment 3 since this is a shared remarks.
+    Refer to reviewer \#1 / comment 3 since this is a shared remark.
   \item \textbf{The disappointing performance and large standard
@@
       explained.}\\
-    A discussion is added in p.~17/l.~320. The original model lacks of
+    A discussion is added in p.~17/l.~320. The original published
+    model lacks of
     degrees of freedom. Two additional parameters will
@@
   \item \textbf{Sections 5 and 6 are both disappointingly short.}
-    Due to additional analyses, the discussion became longer.
+    After including the remarks from the reviewers, this section has
+    become much longer.
     % However,
@@
     enhanced signal which should perform as good as the current
-    models. We apply the same normalization on the different
+    models. For the sake of completeness, we apply the same
+    normalization on the different
     pharmacokinetic models and, as mentioned by the reviewer ---
-    the results are not significantly better.
+    the results are not significantly better as the model parameters
+    might have a different interpretation after the normalization is
+    applied.
     Indeed, these experiments were carried out to investigate the
-    benefit or not of the normalization with the current models,
-    without expecting the results to improve.
+    benefit or not of the normalization with the current models.
   % \item \textbf{Although quantitative parameters obtained from
@@
     an evaluation after classification seems equivalent and a good manner to
-    evaluate the benefit of the normalization. In fact, this is the
+    evaluate the benefit of the normalization. In fact, these are the
     results reported in Fig.\,6(c).
@@
     and to highlight the need of a different normalization approach
-    than the one needed in T2w. We improve the Fig.\,2. Figure~2(a)
+    than the one needed in T2w. We have clarified in the caption that
+    Fig.\,1 is related to T2w, and if requested by the reviewers,
+    Figure 1 could be removed. We improve the Fig.\,2. Figure~2(a)
     presents only the process to build the
@@
     of the graph and is a standard way to formalize graph-based
-    problem in image processing.
+    problem in image processing which often includes a data driven
+    term and a smoothing term.
   \item \textbf{The theoretical foundations of equation 3 are not
@@
     using a rigid registration directly affect the variations
-    $\alpha_i$ and $\Delta_t$. Applying more advanced registration
-    such as elastic registration as in Lemaitre, Guillaume, et
-    al. "Normalization of T2W-MRI prostate images using Rician a
-    priori." SPIE Medical Imaging. International Society for Optics
-    and Photonics, 2016. would make it complicated to shift the data
-    with only these two parameters. Furthermore, rigid registration
-    will not change the variations of the contrast agent over time.
+    $\alpha_i$ and $\Delta_t$. Non rigid registration is deemed not
+    necessary as the main parameters that we propose to recover are
+    translations and scaling. Moreover, this kind of registration
+    might induce deformation artifacts which could impact on the
+    overall contrast enhancement over time.
   \item \textbf{Other question that may be raised is the influence of

### 2017-02-03 03_experiments/experiments.tex
Update everything

@@
 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); a slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
-A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
+A power injector (Medrad, Indianola, USA) is used to provide a bolus
+injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of
+\SI{0.2}{\ml} Gd-DTPA/kg of body weight.
+\textbf{The acquisition starts before the bolus injection to obtain
+  pre-contrast volumes.}
 

### 2017-04-29 01_introduction/introduction.tex
Move to IEEE template

@@
 \Ac{cap} is the second most frequently diagnosed cancer in men,
-accounting for 899,000 cases and leading to 258,100 deaths per year~\citep{ferlay2010estimates}.
-As highlighted by the PI-RADS Steering Committee, the two main challenges to be addressed are~\citep{weinreb2016pi}:
+accounting for 899,000 cases and leading to 258,100 deaths per year~\cite{ferlay2010estimates}.
+As highlighted by the PI-RADS Steering Committee, the two main challenges to be addressed are~\cite{weinreb2016pi}:
 (i) improving the detection of clinically significant \ac{cap} and
@@
 In this regard, \ac{mpmri} is frequently used to build robust \ac{cad} systems to detect, localize, and grade \ac{cap}.
-In general, \ac{cad} systems are based on \ac{mpmri} which potentially combines several of the following modalities~\citep{lemaitre2015computer}: \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri}, \ac{adc} maps, and \ac{mrsi}.
+In general, \ac{cad} systems are based on \ac{mpmri} which potentially combines several of the following modalities~\cite{lemaitre2015computer}: \ac{t2w}-\ac{mri}, \ac{dce}-\ac{mri}, \ac{adc} maps, and \ac{mrsi}.
 
@@
 discrimination of healthy tissues from \ac{cap} tissues.
-In fact, these properties are automatically extracted using quantitative or semi-quantitative approaches~\citep{lemaitre2015computer}.
+In fact, these properties are automatically extracted using quantitative or semi-quantitative approaches~\cite{lemaitre2015computer}.
 
-\emph{Quantitative} approaches uses pharmacokinetic modelling based on a bicompartment model, namely Brix~\citep{brix1991pharmacokinetic} and Tofts~\citep{tofts1995quantitative} models.
+\emph{Quantitative} approaches uses pharmacokinetic modelling based on a bicompartment model, namely Brix~\cite{brix1991pharmacokinetic} and Tofts~\cite{tofts1995quantitative} models.
 The parameters of the Brix model are inferred by assuming a linear relationship between the media concentration and the \ac{mri} signal intensity.
 However, this assumption has been shown to lead to inaccurate
-estimations of the pharmacokinetic parameters~\citep{heilmann2006determination}.
+estimations of the pharmacokinetic parameters~\cite{heilmann2006determination}.
 In contrast, the Tofts model requires the conversion of \ac{mri}
@@
 relationship using a specific equation of \ac{mri} sequences (e.g., FLASH sequence).
-Tofts modeling, however, is highly complex~\citep{gliozzi2011phenomenological}.
+Tofts modeling, however, is highly complex~\cite{gliozzi2011phenomenological}.
 Achieving the conversion using the non-linear approach requires the
@@
 
-\emph{Semi-quantitative} approaches are mathematical rather than pharmacokinetic because no pharmacokinetic assumptions regarding the relationship between the \ac{mri} signal and the contrast agent are made~\citep{huisman2001accurate,gliozzi2011phenomenological}.
+\emph{Semi-quantitative} approaches are mathematical rather than pharmacokinetic because no pharmacokinetic assumptions regarding the relationship between the \ac{mri} signal and the contrast agent are made~\cite{huisman2001accurate,gliozzi2011phenomenological}.
 These methods are advantageous because they do not require any knowledge of the \ac{mri} sequence or any conversion from signal intensity to concentration.
@@
 proposed by \citeauthor{huisman2001accurate} requires an initial
-estimate of the standard deviation of the signal noise and some manual tuning.
+estimate of the standard deviation of the signal noise and some manual tuning \cite{huisman2001accurate}.
 

### 2017-04-29 02_methods/methods.tex
Update everything
Move to IEEE template

--- 2017-01-30 02_methods/methods.tex
@@
   \caption{Illustration of the inter-patient variations in 17
-    different patients in \acs*{t2w}-\acs*{mri}, using the \acs*{pdf} representation.}
+    different patients in \acs*{t2w}-\acs*{mri}, using the \acs*{pdf}
+    representation.}
   \label{fig:t2w}
@@
 In \ac{t2w}-\ac{mri}, these variations are characterized by a shift and a scaling of the intensities as illustrated by the intensity \ac{pdf} in Fig.\,\ref{fig:t2w}.
-Therefore, these variations can be corrected using a $z$-score approach,--- i.e., normalizing the data by subtracting the mean and dividing by the standard deviation ---assuming that the data follow a specific distribution~\citep{lemaitre2016normalization}.
+Therefore, these variations can be corrected using a $z$-score approach,--- i.e., normalizing the data by subtracting the mean and dividing by the standard deviation ---assuming that the data follow a specific distribution~\cite{lemaitre2016normalization}.
 
@@
   \hspace*{\fill}
-  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
+  \subfloat[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
   \hspace*{\fill}
@@
   \hspace*{\fill}
-  \subfigure[$I_0$: 117; $t_0$: 6\textsuperscript{th} serie; wider st. dev.]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
-  \subfigure[$I_0$: 103; $t_0$: 4\textsuperscript{th} serie; narrower std. dev.]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
+  \subfloat[$I_0$: 117; $t_0$: 6\textsuperscript{th} serie; wider st. dev.]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
+  \subfloat[$I_0$: 103; $t_0$: 4\textsuperscript{th} serie; narrower std. dev.]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
   \hspace*{\fill}
-  \caption{\subref{subfig:pathhist} Illustration of the heatmap
+  \caption{\protect\subref{subfig:pathhist} Illustration of the heatmap
     representation: all \ac*{pdf}s of the prostate gland are
     concatenated together to build an heatmap;
-    \subref{subfig:pat1}-\subref{subfig:pat2} Heatmap of 2 patients
+    \protect\subref{subfig:pat1}-\protect\subref{subfig:pat2} Heatmap of 2 patients
     revealing  the three types of inter-patient variations: intensity shift
@@
 
-\begin{equation}
+\begin{equation}\small
   w_{ij} = \begin{cases}
@@
   \hspace*{\fill}
-  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.44\textwidth]{02_methods/figures/rmse.pdf}} \hfill
-  \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
+  \subfloat[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.44\textwidth]{02_methods/figures/rmse.pdf}} \hfill
+  \subfloat[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
   \hspace*{\fill}
@@
 used for the quantification of \ac{dce}-\ac{mri} for \ac{cap}
-detection~\citep{lemaitre2015computer} and will be used for comparison in this work.
+detection~\cite{lemaitre2015computer} and will be used for comparison in this work.
 Furthermore, we would like to emphasize the following additional contributions for this section: (i) a novel automatic \ac{aif} estimation algorithm based on clustering and (ii) a simplified semi-quantitative method using constrained optimization.
@@
 
-In the Brix model~\citep{brix1991pharmacokinetic}, the \ac{mri} signal intensity is assumed to be proportional to the media concentration.
+In the Brix model~\cite{brix1991pharmacokinetic}, the \ac{mri} signal intensity is assumed to be proportional to the media concentration.
 Therefore, the model is expressed as shown in Eq.\,\eqref{eq:brix}, as
@@
 
-\begin{equation}
+\begin{dmath}
   s_n(t) = 1 + A \left[ \frac{\exp(k_{el} t') - 1}{k_{ep}(k_{ep} - k_{el})} \exp(- k_{el} t) - \frac{\exp(k_{ep} t') - 1}{k_{el}(k_{ep} - k_{el})} \exp(- k_{ep} t) \right],
   \label{eq:brix}
-\end{equation}
+\end{dmath}
 
@@
 
-\begin{equation}
-  \small
+\begin{dmath}
   s_n(t) = 1 + \frac{A}{\tau} \left[ \frac{k_{ep} \left( \exp(k_{el} t') - 1 \right)}{k_{el}(k_{ep} - k_{el})} \exp(- k_{el} t) - \frac{\exp(k_{ep} t') - 1}{(k_{ep} - k_{el})} \exp(- k_{ep} t) \right] ,
   \label{eq:hoffmann}
-\end{equation}
+\end{dmath}
 
@@
   \hspace*{\fill}
-  \subfigure[Original image.]{\label{fig:org}\includegraphics[width=.3\textwidth]{02_methods/figures/original.pdf}} \hfill
-  \subfigure[Candidates region after clustering.]{\label{fig:cand}\includegraphics[width=.3\textwidth]{02_methods/figures/candidate.pdf}} \hfill
-  \subfigure[Regions selected after applying the different criteria.]{\label{fig:final}\includegraphics[width=.3\textwidth]{02_methods/figures/aif.pdf}}
+  \subfloat[Original image.]{\label{fig:org}\includegraphics[width=.3\textwidth]{02_methods/figures/original.pdf}} \hfill
+  \subfloat[Candidates region after clustering.]{\label{fig:cand}\includegraphics[width=.3\textwidth]{02_methods/figures/candidate.pdf}} \hfill
+  \subfloat[Regions selected after applying the different criteria.]{\label{fig:final}\includegraphics[width=.3\textwidth]{02_methods/figures/aif.pdf}}
   \hspace*{\fill}
@@
 \begin{description}
-  \item[Segmentation of artery voxels and patient-based \ac{aif} estimation] The \ac{aif} signal from \ac{dce}-\ac{mri} can be manually estimated by selecting the most-enhanced voxels from the femoral or iliac arteries~\citep{meng2010comparison}.
+  \item[Segmentation of artery voxels and \ac{aif} estimation] The \ac{aif} signal from \ac{dce}-\ac{mri} can be manually estimated by selecting the most-enhanced voxels from the femoral or iliac arteries~\cite{meng2010comparison}.
     Few methods have been proposed to address the automated extraction
@@
     \citeauthor{chen2008automatic} successively filtered the possible
-    candidates to be considered as the \ac{aif} such that~\citep{chen2008automatic}:
+    candidates to be considered as the \ac{aif} such that~\cite{chen2008automatic}:
     (i) dynamic signals with a small peak and voxels with a small wash-in are rejected by thresholding,
@@
     \citeauthor{zhu2011automated} proposed an iterative method that
-    involves the selection of voxels that best fit a gamma variate function~\citep{zhu2011automated}.
+    involves the selection of voxels that best fit a gamma variate function~\cite{zhu2011automated}.
     However, this method requires the computation of the first and
     second derivatives as well as the maximum curvature points.
-    \citeauthor{shanbhag2012generalized} proposed the following 4-step algorithm~\citep{shanbhag2012generalized,fennessy2015quantitative}:
+    \citeauthor{shanbhag2012generalized} proposed the following 4-step algorithm~\cite{shanbhag2012generalized,fennessy2015quantitative}:
     (i) remove the slices with artifacts and find the best slices based on intrinsic anatomic landmarks and enhancement characteristics,
@@
     Finally, regions with an eccentricity smaller than $0.5$ and an area in the range of $[100, 400]$ voxels are kept.
-    Additionally, to remove voxels contaminated by the partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\citep{schabel2008uncertainty} and the average signal is computed.
+    Additionally, to remove voxels contaminated by the partial volume effect, only the $10\%$ most enhanced voxels of the possible candidates are kept as proposed by~\cite{schabel2008uncertainty} and the average signal is computed.
     A summary of the different segmentation steps is presented in Fig.\,\ref{fig:aif}.
@@
       $T_{10}$ can be estimated from the acquisition of a T$_1$ map.
-      However, this modality is not part of the clinical trial in this research and the value of $T_{10}$ is fixed to \SI{1600}{\ms} for both blood and prostate, in accordance with the values found in the literature~\citep{fennessy2015quantitative,de2004mr,carr2011magnetic}.
+      However, this modality is not part of the clinical trial in this research and the value of $T_{10}$ is fixed to \SI{1600}{\ms} for both blood and prostate, in accordance with the values found in the literature~\cite{fennessy2015quantitative,de2004mr,carr2011magnetic}.
       \item[Estimation of population-based \ac{aif}] While estimating
@@
         In this regard, the population-based \ac{aif} was estimated in
-        accordance with the method of~\citep{meng2010comparison} by
+        accordance with the method of~\cite{meng2010comparison} by
         fitting the average patient-based \ac{aif}s to the model
@@
         shown in Eq.\,\eqref{eq:parker}, as follows:
-        \begin{equation}
+        \begin{equation}\footnotesize
           C_p(t) = \sum_{n=1}^{2} \frac{A_n}{\sigma_n \sqrt{2 \pi}} \exp\left(\frac{- (t- T_n)^2}{2\sigma_{n}^{2}}\right) + \frac{\alpha \exp(-\beta t)}{1 + \exp{-s (t - \tau)}} ,
@@
 
-The parameters are estimated by fitting the model using constrained non-linear least-squares optimization, solved with the Trust Region Reflective algorithm~\citep{sorensen1982newton} and bounding the parameters to be positive.
+The parameters are estimated by fitting the model using constrained non-linear least-squares optimization, solved with the Trust Region Reflective algorithm~\cite{sorensen1982newton} and bounding the parameters to be positive.
 
@@
 
-\citeauthor{gliozzi2011phenomenological} showed that the \ac{pun} approach can be used for \ac{dce}-\ac{mri} analysis~\citep{gliozzi2011phenomenological}.
+\citeauthor{gliozzi2011phenomenological} showed that the \ac{pun} approach can be used for \ac{dce}-\ac{mri} analysis~\cite{gliozzi2011phenomenological}.
 The model has been successfully used in a \ac{cad} system proposed by~\cite{giannini2015fully}.
@@
 
-\begin{equation}
+\begin{equation}\tiny
   s(t) = \begin{cases}
@@
 $t_0$ is estimated by finding the maximum of the first derivative of the \ac{aif} signal, always occurring at the beginning of the signal.
-Then, the function in Eq.\,\eqref{eq:huisman} is fitted using non-linear least squares with the Trust Region Reflective algorithm~\citep{sorensen1982newton}.
+Then, the function in Eq.\,\eqref{eq:huisman} is fitted using non-linear least squares with the Trust Region Reflective algorithm~\cite{sorensen1982newton}.
 Furthermore, the parameters $\tau$ and $S_M$ are bounded during the optimization to ensure robust estimations.

### 2017-04-29 03_experiments/experiments.tex
Move to IEEE template

--- 2017-01-27 03_experiments/experiments.tex
@@
 192$; \ac{fov}: $280 \times 210$ (with 75\% rectangular \ac{fov}); a slab of 16 partitions of \SI{3.5}{\mm} thickness; temporal resolution: \SI{6}{\s}/slab over approximately \SI{5}{\minute}).
-A power injector (Medrad, Indianola, USA) is used to provide a bolus injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of \SI{0.2}{\ml} Gd-DTPA/kg of body weight.
+A power injector (Medrad, Indianola, USA) is used to provide a bolus
+injection of Gd-DTPA (Dotarem, Guerbet, Roissy, France) at a dose of
+\SI{0.2}{\ml} Gd-DTPA/kg of body weight.
+The acquisition starts before the bolus injection to obtain
+  pre-contrast volumes.
 
@@
 Furthermore, a non-rigid registration is performed between the \ac{t2w}-\ac{mri} and \ac{dce}-\ac{mri} to propagate the prostate zones and \ac{cap} ground-truths.
-The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\citep{ibanez2005itk}.
+The resampling is implemented in C++ using the Insight Segmentation and Registration Toolkit~\cite{ibanez2005itk}.
 
@@
 
-The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}~\citep{lemaitre2016github}.
-The data used in this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}~\citep{lemaitre2016dce}.
+The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}~\cite{lemaitre2016github}.
+The data used in this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}~\cite{lemaitre2016dce}.
 
@@
   \centering
-  \resizebox{\columnwidth}{!}{
   \begin{tabular}{lc c c c c c}
@@
   \end{tabular}
-  }
   \label{tab:r2}
@@
   \centering
-  \resizebox{\columnwidth}{!}{
   \begin{tabular}{l c c}
@@
   \end{tabular}
-  }
   \label{tab:resfeats}
@@
   \hspace*{\fill}
-  \subfigure[Quantiative model without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/unormalized/unormalized_methods_0.pdf}} \hfill
-  \subfigure[Quantitative model With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.49\textwidth]{03_experiments/figures/normalized/normalized_methods_0.pdf}}
-  \hspace*{\fill}
-  \hspace*{\fill}
-  \subfigure[Entire enhanced \acs*{dce} signal classification.]{\label{fig:rfnormdcesignal}\includegraphics[width=.49\textwidth]{03_experiments/figures/full_signal_0.pdf}}
+  \subfloat[Quantiative model without normalization.]{\label{fig:rfpharmaunorm}\includegraphics[width=.32\textwidth]{03_experiments/figures/unormalized/unormalized_methods_0.pdf}} \hfill
+  \subfloat[Quantitative model With normalization.]{\label{fig:rfpharmanorm}\includegraphics[width=.32\textwidth]{03_experiments/figures/normalized/normalized_methods_0.pdf}}
+  %\hspace*{\fill}
+  %\hspace*{\fill}
+  \hfill
+  \subfloat[Entire enhanced \acs*{dce} signal classification.]{\label{fig:rfnormdcesignal}\includegraphics[width=.32\textwidth]{03_experiments/figures/full_signal_0.pdf}}
   \hspace*{\fill}
@@
 Therefore, a \ac{rf} classifier is used in conjunction with a \ac{lopo}.
-The use of \ac{rf} is encouraged since it leads to the best performance in the state-of-the-art methods~\citep{litjens2014computer,lemaitre2015computer}.
+The use of \ac{rf} is encouraged since it leads to the best performance in the state-of-the-art methods~\cite{litjens2014computer,lemaitre2015computer}.
 The results are summarized in Table~\ref{tab:resfeats} in terms of the \ac{auc}.
@@
 pharmacokinetic features of a given model (e.g., $A$, $k_ep$, and
-$k_el$ for the Brix model) as previously executed in the traditional \ac{cad} system~\citep{lemaitre2015computer}.
+$k_el$ for the Brix model) as previously executed in the traditional \ac{cad} system~\cite{lemaitre2015computer}.
 For the latter configuration, results are summarized by performing a \ac{roc} analysis and computing the \ac{auc}, as reported in Fig.\,\ref{fig:normpharmarf}.
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
@@
   \label{fig:boxplot}
-\end{figure*}
+\end{figure}
 
